### 2019-03-11 Article/ms.tex
segment grid table

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts

\title{Convolutional Universal Text Information Extractor}
\author{The Author}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\end{document}

### 2019-03-11 data_loader_json.py

@@ -42,15 +42,16 @@ class DataLoader():
         
         self.rows = self.encoding_factor # to be updated 
         self.cols = self.encoding_factor # to be updated 
+        self.segment_grid = params.segment_grid if hasattr(params, 'segment_grid') else False # segment grid into two parts if grid is larger than cols_target
+        self.augment_strategy = params.augment_strategy if hasattr(params, 'augment_strategy') else 1 
+        self.rows_target = params.rows_target if hasattr(params, 'rows_target') else 64 
+        self.cols_target = params.cols_target if hasattr(params, 'cols_target') else 64 
         self.rows_ulimit = params.rows_ulimit if hasattr(params, 'rows_ulimit') else 80 # handle OOM, must be multiple of self.encoding_factor
         self.cols_ulimit = params.cols_ulimit if hasattr(params, 'cols_ulimit') else 80 # handle OOM, must be multiple of self.encoding_factor
-        self.rows_blimit = params.rows_blimit if hasattr(params, 'rows_blimit') else 64 # performance
-        self.cols_blimit = params.cols_blimit if hasattr(params, 'cols_blimit') else 64 # performance
         
         self.fill_bbox = params.fill_bbox if hasattr(params, 'fill_bbox') else False # fill bbox with labels or use one single lable for the entire bbox
         
-        self.data_augmentation = params.data_augmentation if hasattr(params, 'data_augmentation') else False # cal rows/cols for each batch of data
-        self.data_augmentation_dropout = params.data_augmentation_dropout if hasattr(params, 'data_augmentation_dropout') else False # randomly dropout rows/cols
+        self.data_augmentation_dropout = params.data_augmentation_dropout if hasattr(params, 'data_augmentation_dropout') else False # TBD: randomly dropout rows/cols
         self.data_augmentation_extra = params.data_augmentation_extra if hasattr(params, 'data_augmentation_extra') else False # randomly expand rows/cols
         self.da_extra_rows = params.data_augmentation_extra_rows if hasattr(params, 'data_augmentation_extra_rows') else 0 # randomly expand rows/cols
         self.da_extra_cols = params.data_augmentation_extra_cols if hasattr(params, 'data_augmentation_extra_cols') else 0 # randomly expand rows/cols
@@ -151,9 +152,6 @@ class DataLoader():
                         self.dictionary['[UNK]'] += 1
     
     def next_batch(self):
-        #grid_table = np.ones([self.batch_size, self.rows, self.cols, 1])
[…]

### 2019-03-11 main_evaluate_json.py

@@ -9,7 +9,7 @@ import os, csv
 os.environ["CUDA_VISIBLE_DEVICES"] = "1"
 
 from model_cutie import CUTIE
-from model_cutie_res import CUTIERes
+from model_cutie_hr import CUTIERes
 from model_cutie_unet8 import CUTIEUNet
 from model_cutie_sep import CUTIESep
 from data_loader_json import DataLoader
@@ -22,14 +22,14 @@ parser.add_argument('--save_prefix', type=str, default='meals', help='prefix for
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 
 parser.add_argument('--e_ckpt_path', type=str, default='../graph/CUTIE/graph/') # modify this
-parser.add_argument('--ckpt_file', type=str, default='CUTIE_residual_8x_d29939c9(r80c80)_iter_45401.ckpt')
-parser.add_argument('--rows_ulimit', type=int, default=80) 
-parser.add_argument('--cols_ulimit', type=int, default=80) 
-parser.add_argument('--rows_blimit', type=int, default=64) 
-parser.add_argument('--cols_blimit', type=int, default=64) 
+parser.add_argument('--ckpt_file', type=str, default='CUTIE_residual_highresolution_8x_d20000c9(r128c128)_iter_38802.ckpt')
+parser.add_argument('--rows_ulimit', type=int, default=128) 
+parser.add_argument('--cols_ulimit', type=int, default=128) 
+parser.add_argument('--rows_blimit', type=int, default=80) 
+parser.add_argument('--cols_blimit', type=int, default=80) 
 
 parser.add_argument('--load_dict', type=bool, default=True, help='True to work based on an existing dict') 
-parser.add_argument('--load_dict_from_path', type=str, default='dict/40000') # 40000 or 119547 or 20000TC
+parser.add_argument('--load_dict_from_path', type=str, default='dict/20000TC') # 40000 or 119547 or 20000TC
 parser.add_argument('--tokenize', type=bool, default=True) # tokenize input text
 parser.add_argument('--text_case', type=bool, default=True) # case sensitive
 parser.add_argument('--dict_path', type=str, default='dict/---') # not used if load_dict is True
@@ -92,7 +92,7 @@ if __name__ == '__main__':
             recalls += [recall]
             accs_strict += [acc_strict] 
             accs_soft += [acc_soft]
-            #print(res) # show res for current batch  
+            print(res) # show res for current batch  
             
             # visualize result
             shape = data['shape']

### 2019-03-11 main_train_json.py

@@ -7,9 +7,7 @@ import argparse, os
 import timeit
 os.environ["CUDA_VISIBLE_DEVICES"] = "1"
 
-from model_cutie import CUTIE
 from model_cutie_res import CUTIERes
-from model_cutie_unet8 import CUTIEUNet
 from data_loader_json import DataLoader
 from utils import *
 
@@ -35,24 +33,25 @@ parser.add_argument('--update_dict', type=bool, default=False)
 parser.add_argument('--dict_path', type=str, default='dict/---') # not used if load_dict is True
 
 # data manipulation
-parser.add_argument('--rows_ulimit', type=int, default=128) 
-parser.add_argument('--cols_ulimit', type=int, default=128) 
-parser.add_argument('--rows_blimit', type=int, default=64) 
-parser.add_argument('--cols_blimit', type=int, default=64) 
+parser.add_argument('--segment_grid', type=bool, default=True) # segment grid into two parts if grid is larger than cols_target
+parser.add_argument('--rows_target', type=int, default=48) 
+parser.add_argument('--cols_target', type=int, default=48) 
+parser.add_argument('--augment_strategy', type=int, default=2) # 1 for increasing grid shape size, 2 for gaussian around target shape
+parser.add_argument('--rows_ulimit', type=int, default=96) 
+parser.add_argument('--cols_ulimit', type=int, default=96) 
 parser.add_argument('--fill_bbox', type=bool, default=False) # fill bbox with dict_id / label_id
 
-parser.add_argument('--data_augmentation', type=bool, default=True) # augment data row/col in each batch
 parser.add_argument('--data_augmentation_extra', type=bool, default=True) # randomly expand rows/cols
 parser.add_argument('--data_augmentation_dropout', type=bool, default=False) # randomly shrink rows/cols
-parser.add_argument('--data_augmentation_extra_rows', type=int, default=2) 
-parser.add_argument('--data_augmentation_extra_cols', type=int, default=2) 
+parser.add_argument('--data_augmentation_extra_rows', type=int, default=1) 
+parser.add_argument('--data_augmentation_extra_cols', type=int, default=1) 
 
 # training
 parser.add_argument('--batch_size', type=int, default=32) 
 parser.add_argument('--iterations', type=int, default=40000)  
-parser.add_argument('--lr_decay_step', type=int, default=4000) 
-parser.add_argument('--learning_rate', type=float, default=0.001)
-parser.add_argument('--lr_decay_factor', type=float, default=0.5) 
[…]

### 2019-03-11 model_cutie_aspp.py

@@ -1,0 +1,68 @@
+# written by Xiaohui Zhao
+# 2018-12 
+# xiaohui.zhao@accenture.com
+import tensorflow as tf
+from model_cutie import CUTIE    
+    
+class CUTIERes(CUTIE):
+    def __init__(self, num_vocabs, num_classes, params, trainable=True):
+        self.name = "CUTIE_dilate" # 
+        
+        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
+        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
+        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
+        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
+
+        self.num_vocabs = num_vocabs
+        self.num_classes = num_classes     
+        self.trainable = trainable
+        
+        self.embedding_size = params.embedding_size
+        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
+        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
+        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
+        
+        self.layer_inputs = []        
+        self.setup()
+        
+    
+    def setup(self):        
+        # input
+        (self.feed('data')
+             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
+        
+        # encoder
+        (self.feed('embedding')
+             .conv(3, 5, 256, 1, 1, name='encoder1_1')
+             .conv(3, 5, 256, 1, 1, name='encoder1_2')
+             .conv(3, 5, 256, 1, 1, name='encoder1_3')
+             .conv(3, 5, 256, 1, 1, name='encoder1_4')
+             .dilate_conv(3, 5, 256, 1, 1, 2, name='encoder1_5')
[…]

### 2019-03-11 model_cutie_att.py

@@ -6,7 +6,7 @@ from model_cutie import CUTIE
     
 class CUTIERes(CUTIE):
     def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_residual_dilate_8x" # 8x down sampling
+        self.name = "CUTIE_attention" # 
         
         self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
         self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
@@ -35,37 +35,24 @@ class CUTIERes(CUTIE):
         
         # encoder
         (self.feed('embedding')
-             .conv(3, 5, 64, 1, 1, name='encoder1_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_2')
-             .max_pool(2, 2, 2, 2, name='pool1')
-             .conv(3, 5, 128, 1, 1, name='encoder2_1')
-             .conv(3, 5, 256, 1, 1, name='encoder2_2')
-             .max_pool(2, 2, 2, 2, name='pool2')
-             .conv(3, 5, 256, 1, 1, name='encoder3_1')
-             .conv(3, 5, 512, 1, 1, name='encoder3_2')
-             .max_pool(2, 2, 2, 2, name='pool3')
-             .conv(3, 5, 512, 1, 1, name='encoder4_1')
-             .conv(3, 5, 512, 1, 1, name='encoder4_2'))
+             .conv(3, 5, 256, 1, 1, name='encoder1_1')
+             .conv(3, 5, 256, 1, 1, name='encoder1_2')
+             .conv(3, 5, 256, 1, 1, name='encoder1_3')
+             .conv(3, 5, 256, 1, 1, name='encoder1_4'))
         
-        # decoder
-        (self.feed('encoder4_2')
-             .up_conv(3, 5, 512, 1, 1, name='up1'))        
-        (self.feed('up1', 'encoder3_2')
-             .concat(3, name='concat1')
-             .conv(3, 5, 256, 1, 1, name='decoder1_1')
-             .conv(3, 5, 256, 1, 1, name='decoder1_2')
-             .up_conv(3, 5, 256, 1, 1, name='up2'))       
-        (self.feed('up2', 'encoder2_2')
-             .concat(3, name='concat2')
-             .conv(3, 5, 128, 1, 1, name='decoder2_1')
-             .conv(3, 5, 128, 1, 1, name='decoder2_2')
[…]

### 2019-03-11 model_cutie_dilate.py

@@ -1,0 +1,55 @@
+# written by Xiaohui Zhao
+# 2018-12 
+# xiaohui.zhao@accenture.com
+import tensorflow as tf
+from model_cutie import CUTIE    
+    
+class CUTIERes(CUTIE):
+    def __init__(self, num_vocabs, num_classes, params, trainable=True):
+        self.name = "CUTIE_dilate" # 
+        
+        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
+        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
+        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
+        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
+
+        self.num_vocabs = num_vocabs
+        self.num_classes = num_classes     
+        self.trainable = trainable
+        
+        self.embedding_size = params.embedding_size
+        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
+        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
+        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
+        
+        self.layer_inputs = []        
+        self.setup()
+        
+    
+    def setup(self):        
+        # input
+        (self.feed('data')
+             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
+        
+        # encoder
+        (self.feed('embedding')
+             .conv(3, 5, 128, 1, 1, name='encoder1_1')
+             .conv(3, 5, 128, 1, 1, name='encoder1_2')
+             .dilate_conv(3, 5, 256, 1, 1, 2, name='encoder1_3')
+             .dilate_conv(3, 5, 256, 1, 1, 2, name='encoder1_4')
+             .dilate_conv(3, 5, 512, 1, 1, 2, name='encoder1_5')
[…]

### 2019-03-11 model_cutie_hr.py

@@ -1,0 +1,253 @@
+# written by Xiaohui Zhao
+# 2018-12 
+# xiaohui.zhao@accenture.com
+import tensorflow as tf
+from model_cutie import CUTIE    
+    
+class CUTIERes(CUTIE):
+    def __init__(self, num_vocabs, num_classes, params, trainable=True):
+        self.name = "CUTIE_highresolution_8x" # 8x down sampling
+        
+        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
+        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
+        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
+        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
+
+        self.num_vocabs = num_vocabs
+        self.num_classes = num_classes     
+        self.trainable = trainable
+        
+        self.embedding_size = params.embedding_size
+        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
+        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
+        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
+        
+        self.layer_inputs = []        
+        self.setup()
+        
+    
+    def setup(self):        
+        # input
+        (self.feed('data')
+             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
+        
+        # stage 1 block 1
+        (self.feed('embedding')
+             .conv(3, 5, 64, 1, 1, name='encoder1_1_1')
+             .conv(3, 5, 64, 1, 1, name='encoder1_1_2')
[…]

### 2019-03-11 model_framework.py

@@ -166,10 +166,48 @@ class Model(object):
             a = self.convolution(convolve, activate, layer_input, k_h, k_w, c_i, c_o, 
                                  init_weights, init_biases, regularizer, trainable)
             return a  
+     
+     
+    @layer
+    def dilate_conv(self, layer_input, k_h, k_w, c_o, s_h, s_w, rate, name, activation='relu', trainable=True):
+        convolve = lambda input, filter: tf.nn.atrous_conv2d(input, filter, rate, 'SAME', 'DILATE')
+        
+        activate = lambda z: tf.nn.relu(z, 'relu') #if activation == 'relu':
+        if activation == 'sigmoid':
+            activate = lambda z: tf.nn.sigmoid(z, 'sigmoid')
+            
+        with tf.variable_scope(name) as scope:
+            init_weights = tf.truncated_normal_initializer(0.0, 0.01)
+            init_biases = tf.constant_initializer(0.0)
+            regularizer = self.l2_regularizer(self.weight_decay)
+            c_i = layer_input.get_shape()[-1]
+            
+            a = self.convolution(convolve, activate, layer_input, k_h, k_w, c_i, c_o, 
+                                 init_weights, init_biases, regularizer, trainable)
+            return a  
     
     
     @layer
-    def up_conv(self, layer_input, k_h, k_w, c_o, s_h, s_w, name, activation='relu', trainable=True):
+    def dilate_module(self, layer_input, k_h, k_w, c_o, s_h, s_w, rate, name, activation='relu', trainable=True):
+        convolve = lambda input, filter: tf.nn.atrous_conv2d(input, filter, rate, 'SAME', 'DILATE')
+        
+        activate = lambda z: tf.nn.relu(z, 'relu') #if activation == 'relu':
+        if activation == 'sigmoid':
+            activate = lambda z: tf.nn.sigmoid(z, 'sigmoid')
+            
+        with tf.variable_scope(name) as scope:
+            init_weights = tf.truncated_normal_initializer(0.0, 0.01)
+            init_biases = tf.constant_initializer(0.0)
+            regularizer = self.l2_regularizer(self.weight_decay)
+            c_i = layer_input.get_shape()[-1]
+            
+            a = self.convolution(convolve, activate, layer_input, k_h, k_w, c_i, c_o, 
+                                 init_weights, init_biases, regularizer, trainable)
+            return a  
+        
+    
[…]

### 2019-03-13 Article/CVPR/egpaper_final.tex
article updated

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for CVPR Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

By submitting a manuscript to CVPR, the authors guarantee that it has 
not been previously published or accepted for publication in substantially 
similar form in an archival peer-reviewed forum. Furthermore, no paper which 
contains significant overlap with the contributions of this paper is neither 
under review at the moment of submission nor will be submitted during the 
CVPR 2014 review period to {\bf any of the following}: another conference,
a workshop, or a journal. The authors also attest that they did not submit
substantially similar submissions to CVPR 2014. {\bf Violation of any of
these conditions will lead to rejection.} If you are not sure about the
extent of overlap, you may upload a copy of the paper in question as
supplementary material. Note that a Technical Report (departmental, 
arXiv.org, etc.) that is put up without any form of direct peer-review is 
{\bf NOT} considered a publication. Likewise, mention of the work under 
review in a presentation is {\bf NOT} considered a violation.

If there are papers that may appear to the reviewers
to violate this condition, then it is your responsibility to: (1)~cite
these papers (preserving anonymity as described in Section 1.6 below),
(2)~argue in the body of your paper why your CVPR paper is non-trivially
different from these concurrent submissions, and (3)~include anonymized
versions of those papers in the supplemental material.

\subsection{Paper length}
CVPR papers may be between 6 pages and 8 pages, with a \$100 per page added
fee.  Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.  If you submit 8 for review expect to pay the added page
charges for them.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith, it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.

FAQ: Are acknowledgements OK?  No.  Leave them for the final copy.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)  
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Color is valuable, and will be visible to readers of the electronic copy.
However ensure that, when printed on a monochrome printer, no important
information is lost by the conversion to grayscale.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2019-03-13 Article/ms.tex
article updated

@@
-\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
-\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
-\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
-%\geometry{landscape}                		% Activate for rotated page geometry
-%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
-\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
-								% TeX will automatically convert eps --> pdf in pdflatex		
+\documentclass[10pt,twocolumn,letterpaper]{article}
+
+\usepackage{cvpr}
+\usepackage{times}
+\usepackage{epsfig}
+\usepackage{graphicx}
+\usepackage{amsmath}
 \usepackage{amssymb}
 
-%SetFonts
+% Include other packages here, before hyperref.
 
-%SetFonts
+% If you comment hyperref and then uncomment it, you should delete
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
+% run, let it finish, and you should be clear).
+\usepackage[breaklinks=true,bookmarks=false]{hyperref}
 
-\title{Convolutional Universal Text Information Extractor}
-\author{The Author}
-%\date{}							% Activate to display a given date or no date
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
+\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+
+% Pages are numbered in submission mode, and unnumbered in camera-ready
+%\ifcvprfinal\pagestyle{empty}\fi
+\setcounter{page}{4321}
 \begin{document}
+
+%%%%%%%%% TITLE
+\title{CUTIE: Learning to Understand Documents with Convolutional Universal Text Information Extractor}
+
+\author{
+  Xiaohui Zhao, Zhuo Wu, and Xiaoguang Wang \\
+  New IT Accenture \\
+{\tt\small xiaohui.zhao@accenture.com zhuo.wu@accenture.com danny.x.wang@accenture.com}
+% Additional authors and addresses can be added with ``\and'',
+}
+
 \maketitle
-%\section{}
-%\subsection{}
+%\thispagestyle{empty}
+
+%%%%%%%%% ABSTRACT
+\begin{abstract}
+   Extracting key information from documents, such as receipts or invoices, and preserving the interested texts to structured data is crucial in the document-intensive streamline processes of office automation in areas that includes but not limited to accounting, financial, and taxation areas.
+Large proportion of published works attempt to tackle the problem by exploring the semantic context in text sequences based on the named entity recognition method in NLP field.
+In this paper, we propose to combine the effective information from both semantic meaning and spatial distribution of texts in documents.
+Specifically, our proposed model, Convolutional Universal Text Information Extractor (CUTIE), applies convolutional networks on the gridded texts where texts are embedded as features with semantical connotations.
+We further explore the effect of employing different structures of convolutional network and propose a faster and portable structure.
+We demonstrate the effectiveness of the proposed method on a dataset with up to 3000 labelled receipts, without any post-processing, achieving state-of-the-art performance that is higher than BERT but with only 1/10 parameters and much higher than the RNN based methods.
+\end{abstract}
+
+%%%%%%%%% BODY TEXT
+\section{Introduction}
+
+Implementing Scanned receipts OCR and information extraction (SROIE) is of great benefit to services and applications such as efficient archiving, compliance check, and fast indexing in the document-intensive streamline processes of office automation in areas that includes but not limit to accounting, financial, and taxation areas.
+There are two specific tasks involved in SROIE: receipt OCR and key information extraction.
+In this work, we focus on the second task that is rare in published research.
+In fact, key information extraction faces big chanllenges, where different types of document structures and vast number of potential interested key words introduces great difficulties.
+Although the commonly used rule-based method can be implemented with carefully designed expert rules, it can only work on specific type of documents and takes no lesser effort to adapt to new type of documents.
+Therefore, it is desirable to have a learning based key information extraction method with limited requirement of human resources and solely employing the deep learning technique without designing expert rules for any specific type of documents.
+
+History about published learning based methods goes here.
+The majority of the published learning based works are based on the named entity recognition research in the NLP field that is not originally designed to solve the key information extraction problem in SROIE, which align text words in the original document as a long paragraph in line-based rule.
+However, the real world documents, such as receipts and invoices, present with various styles of layouts that were designed for different scenarios or from different enterprise entities, which introduces great difficulties.
+The order or distance of the texts in the line-based aligned long paragraph tend to vary greatly due to layout variations, which is difficult to be handled with the natural language paragraph oriented methods, one typical example is illustrated in Fig.
+\ref{fig:short}.
+
+Attempting to involve the spatial information into the key information extraction process, we propose to tackle this problem by using the CNN based network structure and involve the semantic features in a properly designed fashion.
+In particular, our proposed model, called Convolutional Universal Text Information Extractor (CUTIE), tackles the key information extraction problem by applying convolutional deep learning model on the gridded texts, as illustrated in Fig.
+\ref{fig:onecol}.
+The gridded texts is the formatted input of the entire network, which is arranged in close correspondance with their real spatial relationship of the original scanned document image.
+Furthermore, the rich semantic information is encoded from the gridded texts in the very beginning of the convolutional network.
+
+\section{Related Work}
+
+\section{Method}
+\subsection{Grid Positional Mapping}
+To generate input grid data for the convolutional network, the scanned document image are processed by an OCR engine to acquire the texts and their absolute / relative positions.
+Let the minimum bounding box around an interested text $s$ be $b_s$ that is restricted by four corner coordinates, where the upper-left corner coordinate in the scanned document be $(x_{left}, y_{top})$ and the bottom right of the bounding box be $(x_{right}, y_{bottom})$.
+To avoid the affects from overlapped bounding boxes and reveal the actual relative position among texts, we calculate the center point $(c_x, c_y)$ of the bounding boxes as the reference position.
+It is not hard to find that involving pre-processes that combine texts into meaningful entities here will benefit the following grid positional mapping process.
+However, this is not the major purpose of this paper and we leave it to future researches.
+In this paper, we tokenize the text words with a greedy longest-match-first algorithm using a pre-defined dictionary \cite{bertgit}.
+
+Let the grid positional mapping process be $G$ and the target grid size be $(c_{g_0}, r_{g_0})$.
+To generate the grid data, the goal of $G$ is to map the texts from the original scanned document image to the target grid, such that the mapped grid preserves the original spatial relationship among texts yet more suitable to be used as the input for the convolutional network.
+
+\subsection{Model}
+Through matching the output of CUTIE with the labelled grid data, the model learns to generate the label for each text in the grid input via exploring both the spatial and semantic features.
+For that reason, the task of CUTIE holds resemblance to the semantic segmentation task in the computer vision field.
+Several methods have been proposed to capture multi-scale context in the input data.
+The encoder-decoder structure.
+We propose a convolutional network
+
+\begin{equation}
+\label{cx}
+c_h = x_l + \frac{(x_r - x_l)}{2}
+\end{equation}
+
+\begin{equation}
+\label{cy}
+c_v = y_t + \frac{(y_b - y_t)}{2}
+\end{equation}
+
+For tokenized texts, the bounding box is horizontally divided into multiple boxes and their reference positions are calculated using the same criteria as Equ. \ref{cx} and Equ. \ref{cy}, separately.
+
+\subsection{Grid Augmentation}
+
+\section{Experiments}
+
+\section{Discussion}
+Automatically extracting interested words / information from the scanned document images is of great interest to various services and applications.
+The performance gain is mainly achieved by exploring three key factors: the spatial relationship among texts, the semantic information of texts, and the text gridding mechanism.
+
+\begin{figure}[t]
+\begin{center}
+\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
+   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
+\end{center}
+   \caption{Example of caption.  It is set in Roman so that mathematics
+   (always set in Roman: $B \sin A = A \sin B$) may be included without an
+   ugly clash.}
+\label{fig:long}
+\label{fig:onecol}
+\end{figure}
+
+\subsection{Miscellaneous}
+
+\noindent
+Compare the following:\\
+\begin{tabular}{ll}
+ \verb'$conf_a$' &  $conf_a$ \\
+ \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
+\end{tabular}\\
+See The \TeX book, p165.
+
+The space after \eg, meaning ``for example'', should not be a
+sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
+\verb'\eg' macro takes care of this.
+
+When citing a multi-author paper, you may save space by using ``et alia'',
+shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
+However, use it only when there are three or more authors.  Thus, the
+following is correct: ``
+   Frobnication has been trendy lately.
+   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
+   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
+
+This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
+because reference~\cite{Alpher03} has just two authors.  If you use the
+\verb'\etal' macro provided, then you need not worry about double periods
+when used at the end of a sentence as in Alpher \etal.
+
+\begin{figure*}
+\begin{center}
+\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+\end{center}
+   \caption{Example of a short caption, which should be centered.}
+\label{fig:short}
+\end{figure*}
+
+{\small
+\bibliographystyle{ieee}
+\bibliography{biblio}
+}
 

### 2019-03-13 model_cutie_aspp.py

@@ -1,12 +1,12 @@
 # written by Xiaohui Zhao
-# 2018-12 
+# 2019-03
 # xiaohui.zhao@accenture.com
 import tensorflow as tf
 from model_cutie import CUTIE    
     
 class CUTIERes(CUTIE):
     def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_dilate" # 
+        self.name = "CUTIE_atrousSPP" # 
         
         self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
         self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')

### 2019-03-13 model_cutie_att.py

@@ -1,5 +1,5 @@
 # written by Xiaohui Zhao
-# 2018-12 
+# 2019-03
 # xiaohui.zhao@accenture.com
 import tensorflow as tf
 from model_cutie import CUTIE    

### 2019-03-13 model_cutie_dilate.py

@@ -1,5 +1,5 @@
 # written by Xiaohui Zhao
-# 2018-12 
+# 2019-03 
 # xiaohui.zhao@accenture.com
 import tensorflow as tf
 from model_cutie import CUTIE    

### 2019-03-15 Article/ms.tex
correct segment working version

@@
 
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
 \begin{document}
@@
 
-\section{Related Work}
-
-\section{Method}
-\subsection{Grid Positional Mapping}
-To generate input grid data for the convolutional network, the scanned document image are processed by an OCR engine to acquire the texts and their absolute / relative positions.
-Let the minimum bounding box around an interested text $s$ be $b_s$ that is restricted by four corner coordinates, where the upper-left corner coordinate in the scanned document be $(x_{left}, y_{top})$ and the bottom right of the bounding box be $(x_{right}, y_{bottom})$.
-To avoid the affects from overlapped bounding boxes and reveal the actual relative position among texts, we calculate the center point $(c_x, c_y)$ of the bounding boxes as the reference position.
-It is not hard to find that involving pre-processes that combine texts into meaningful entities here will benefit the following grid positional mapping process.
-However, this is not the major purpose of this paper and we leave it to future researches.
-In this paper, we tokenize the text words with a greedy longest-match-first algorithm using a pre-defined dictionary \cite{bertgit}.
-
-Let the grid positional mapping process be $G$ and the target grid size be $(c_{g_0}, r_{g_0})$.
-To generate the grid data, the goal of $G$ is to map the texts from the original scanned document image to the target grid, such that the mapped grid preserves the original spatial relationship among texts yet more suitable to be used as the input for the convolutional network.
-
-\subsection{Model}
-Through matching the output of CUTIE with the labelled grid data, the model learns to generate the label for each text in the grid input via exploring both the spatial and semantic features.
-For that reason, the task of CUTIE holds resemblance to the semantic segmentation task in the computer vision field.
-Several methods have been proposed to capture multi-scale context in the input data.
-The encoder-decoder structure.
-We propose a convolutional network
-
-\begin{equation}
-\label{cx}
-c_h = x_l + \frac{(x_r - x_l)}{2}
-\end{equation}
-
-\begin{equation}
-\label{cy}
-c_v = y_t + \frac{(y_b - y_t)}{2}
-\end{equation}
-
-For tokenized texts, the bounding box is horizontally divided into multiple boxes and their reference positions are calculated using the same criteria as Equ. \ref{cx} and Equ. \ref{cy}, separately.
-
-\subsection{Grid Augmentation}
-
-\section{Experiments}
-
-\section{Discussion}
-Automatically extracting interested words / information from the scanned document images is of great interest to various services and applications.
-The performance gain is mainly achieved by exploring three key factors: the spatial relationship among texts, the semantic information of texts, and the text gridding mechanism.
-
 \begin{figure}[t]
@@
 
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-\verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'',
-shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-However, use it only when there are three or more authors.  Thus, the
-following is correct: ``
-   Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-because reference~\cite{Alpher03} has just two authors.  If you use the
-\verb'\etal' macro provided, then you need not worry about double periods
-when used at the end of a sentence as in Alpher \etal.
-
 \begin{figure*}
@@
 
+\section{Related Work}
+
+\section{Methods}
+\subsection{Grid Positional Mapping}
+To generate input grid data for the convolutional network, the scanned document image are processed by an OCR engine to acquire the texts and their absolute / relative positions.
+Let the scanned document image is of shape $(w, h)$, the minimum bounding box around the $i$-th interested text $s_i$ be $b_i$ that is restricted by two corner coordinates, where the upper-left corner coordinate in the scanned document be $(x^i_{left}, y^i_{top})$ and the bottom right of the bounding box be $(x^i_{right}, y^i_{bottom})$.
+To avoid the affects from overlapped bounding boxes and reveal the actual relative position among texts, we calculate the center point $(c^i_x, c^i_y)$ of the bounding boxes as the reference position.
+It is not hard to find that involving pre-processes that combine texts into meaningful entities here will benefit the following grid positional mapping process.
+However, this is not the major purpose of this paper and we leave it to future researches.
+In this paper, we tokenize the text words with a greedy longest-match-first algorithm using a pre-defined dictionary \cite{bertgit}.
+
+Let the grid positional mapping process be $G$ and the target grid size be $(c_{g_0}, r_{g_0})$.
+To generate the grid data, the goal of $G$ is to map the texts from the original scanned document image to the target grid, such that the mapped grid preserves the original spatial relationship among texts yet more suitable to be used as the input for the convolutional network.
+
+\begin{equation}
+\label{cx}
+c^i_x = c_{g_0} \frac{x_l + \frac{(x_r - x_l)}{2}}{w}
+\end{equation}
+
+\begin{equation}
+\label{cy}
+r^i_y = r_{g_0} \frac{y_t + \frac{(y_b - y_t)}{2}}{h}
+\end{equation}
+
+For tokenized texts, the bounding box is horizontally divided into multiple boxes and their reference positions are calculated using the same criteria as Equ. \ref{cx} and Equ. \ref{cy}, separately.
+
+\subsection{Model}
+Through matching the output of CUTIE with the labelled grid data, the model learns to generate the label for each text in the grid input via exploring both the spatial and semantic features.
+For that reason, the task of CUTIE bears resemblance to the semantic segmentation task in the computer vision field but with more sparse data distributions.
+Specifically, the mapped grid contains scattered data points (texts) in contrast to the images bespread with pixels.
+The grid positional mapped key texts are either close to or distant to each other due to different types of document layouts.
+
+In fact, several methods have been proposed in the semantic segmentation field to capture multi-scale context in the input data.
+The methods of image pyramid and the encoder-decoder structure both aim at exploiting multi-scale information.
+The interested objects from different scales become prominent in the former networks by using multiple scaled input data to gather multi-scale features.
+The later networks shrink feature maps to enlarge receptive fields and reduce computation burdens, and then capture finer details by gradually recovering the spatial information from lower layer features.
+However, spatial resolution is reduced in the encoding process and the decoding process exploits only high resolution but low level features to recover the spatial resolution, the consecutive striding encoding process decimates detail information which is detrimental to the sparse grid.
+Instead, the field of view of filters can also be effectively enlarged by applying atrous convolution \cite{deeplab, deeplabv1, deeplabv3, deeplabv3p}.
+
+To capture long distance connection and avoid potential loss in the encoding process, we propose to employ the convolutional network with atrous convolution and without the encoder-decoder structure.
+Let the input feature map be $m$, filter be $w$ and output be $n$, for each position $i$, atrous convolution is applied over the input feature map $m$ as
+
+\begin{equation}
+n[i] = \sum_k m[i+r\cdot k]w[k]
+\end{equation}
+where $r$ is the atrous rate that indicates the sampling stride of the input signal, which is implemented as convolving the input feature with upsampled filters by inserting $r-1$ zeros between two consecutive filter values along each spatial dimension.
+Standard convolution is a special case of atrous convolution with $r=1$.
+
+Two types of architectures are developed for CUITE.
+
+\subsection{Grid Augmentation}
+\label{gridaugmentation}
+
+\section{Experiments}
+
+\section{Discussion}
+Automatically extracting interested words / information from the scanned document images is of great interest to various services and applications.
+The performance gain is mainly achieved by exploring three key factors: the spatial relationship among texts, the semantic information of texts, and the text gridding mechanism.
+
 {\small

### 2019-03-15 data_loader_json.py

@@ -375,8 +375,8 @@ class DataLoader():
                         ptr += 1
                     if ptr == cols:
                         print(grid_table[row,:])
-                        print('overlap in {} <{}> row {} r{}c{}!'.
-                              format(file_name, self.index_to_word[dict_id], row, rows, cols))
+                        #print('overlap in {} <{}> row {} r{}c{}!'.
+                        #      format(file_name, self.index_to_word[dict_id], row, rows, cols))
                     else:
                         #print('shift in {} for row {}'.format(file_name, row))
                         grid_table[row, ptr:-1] = grid_table[row, ptr+1:]

### 2019-03-15 main_train_json.py

@@ -33,12 +33,12 @@ parser.add_argument('--update_dict', type=bool, default=False)
 parser.add_argument('--dict_path', type=str, default='dict/---') # not used if load_dict is True
 
 # data manipulation
-parser.add_argument('--segment_grid', type=bool, default=True) # segment grid into two parts if grid is larger than cols_target
-parser.add_argument('--rows_target', type=int, default=48) 
-parser.add_argument('--cols_target', type=int, default=48) 
+parser.add_argument('--segment_grid', type=bool, default=False) # segment grid into two parts if grid is larger than cols_target
+parser.add_argument('--rows_target', type=int, default=72) 
+parser.add_argument('--cols_target', type=int, default=72) 
 parser.add_argument('--augment_strategy', type=int, default=2) # 1 for increasing grid shape size, 2 for gaussian around target shape
-parser.add_argument('--rows_ulimit', type=int, default=96) 
-parser.add_argument('--cols_ulimit', type=int, default=96) 
+parser.add_argument('--rows_ulimit', type=int, default=88) 
+parser.add_argument('--cols_ulimit', type=int, default=88) 
 parser.add_argument('--fill_bbox', type=bool, default=False) # fill bbox with dict_id / label_id
 
 parser.add_argument('--data_augmentation_extra', type=bool, default=True) # randomly expand rows/cols

### 2019-03-15 model_cutie_dilate.py

@@ -46,9 +46,6 @@ class CUTIERes(CUTIE):
              .dilate_conv(3, 5, 128, 1, 1, 2, name='encoder1_9')
              .dilate_conv(3, 5, 128, 1, 1, 2, name='encoder1_10'))
         
-        # Atrous Spatial Pyramid Pooling module
-        
-        
         # classification
         (self.feed('encoder1_10') 
              .conv(1, 1, self.num_classes, 1, 1, activation=self.activation, name='cls_logits') # sigmoid for ghm

### 2019-03-15 data_loader_json.py
correct segment working version

@@ -234,9 +234,9 @@ class DataLoader():
                 res_all[cols] += 1
                 res_row[rows] += 1
                 res_col[cols] += 1
-            res_all = sorted(res_all.items(), key=lambda x:x[1], reverse=True)
-            res_row = sorted(res_row.items(), key=lambda x:x[1], reverse=True)
-            res_col = sorted(res_col.items(), key=lambda x:x[1], reverse=True)
+            res_all = sorted(res_all.items(), key=lambda x:x[0], reverse=True)
+            res_row = sorted(res_row.items(), key=lambda x:x[0], reverse=True)
+            res_col = sorted(res_col.items(), key=lambda x:x[0], reverse=True)
             return res_all, res_row, res_col
     
         tss, tss_r, tss_c = shape_statistic(self.training_docs) # training shape static
@@ -375,8 +375,8 @@ class DataLoader():
                         ptr += 1
                     if ptr == cols:
                         print(grid_table[row,:])
-                        #print('overlap in {} <{}> row {} r{}c{}!'.
-                        #      format(file_name, self.index_to_word[dict_id], row, rows, cols))
+                        print('overlap in {} <{}> row {} r{}c{}!'.
+                              format(file_name, self.index_to_word[dict_id], row, rows, cols))
                     else:
                         #print('shift in {} for row {}'.format(file_name, row))
                         grid_table[row, ptr:-1] = grid_table[row, ptr+1:]
@@ -599,6 +599,8 @@ class DataLoader():
                 else:
                     content_dressed_right.append([file_name, dressed_text, word_id, [x_left, y_top, x_right, y_bottom], \
                                       [left, top, right, bottom], max_rows, self.cols_target])
+            data.append(content_dressed_left)
+            data.append(content_dressed_right)
         else:
             for i, line in enumerate(content_dressed): # append height/width/numofwords to the list
                 file_name, dressed_text, word_id, [x_left, y_top, x_right, y_bottom] = line

### 2019-03-15 main_train_json.py

@@ -5,6 +5,7 @@ import tensorflow as tf
 import numpy as np
 import argparse, os
 import timeit
+from pprint import pprint
 os.environ["CUDA_VISIBLE_DEVICES"] = "1"
 
 from model_cutie_res import CUTIERes
@@ -15,7 +16,7 @@ parser = argparse.ArgumentParser(description='CUTIE parameters')
 # data
 parser.add_argument('--doc_path', type=str, default='data/meals')
 parser.add_argument('--save_prefix', type=str, default='meals', help='prefix for ckpt') # TBD: save log/models with prefix
-parser.add_argument('--test_path', type=str, default='data/meals_1215') # leave empty if no test data provided
+parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
 # ckpt
 parser.add_argument('--restore_ckpt', type=bool, default=False) 
@@ -33,7 +34,7 @@ parser.add_argument('--update_dict', type=bool, default=False)
 parser.add_argument('--dict_path', type=str, default='dict/---') # not used if load_dict is True
 
 # data manipulation
-parser.add_argument('--segment_grid', type=bool, default=False) # segment grid into two parts if grid is larger than cols_target
+parser.add_argument('--segment_grid', type=bool, default=True) # segment grid into two parts if grid is larger than cols_target
 parser.add_argument('--rows_target', type=int, default=72) 
 parser.add_argument('--cols_target', type=int, default=72) 
 parser.add_argument('--augment_strategy', type=int, default=2) # 1 for increasing grid shape size, 2 for gaussian around target shape
@@ -121,7 +122,9 @@ def save_ckpt(sess, path, save_prefix, data_loader, network, num_words, num_clas
     print('\nCheckpoint saved to: {:s}\n'.format(filename))
     
 if __name__ == '__main__':
+    pprint(params)
     # data
+    
     data_loader = DataLoader(params, update_dict=params.update_dict, load_dictionary=params.load_dict, data_split=0.75)
     num_words = max(20000, data_loader.num_words)
     num_classes = data_loader.num_classes
@@ -357,7 +360,6 @@ if __name__ == '__main__':
             if iter>=params.log_save_step and iter%params.log_save_step == 0:
                 summary_writer.add_summary(summary_str, iter+1)    
     
-    from pprint import pprint
     pprint(params)
     pprint('Data rows/cols:{},{}'.format(data_loader.rows, data_loader.cols))
     summary_writer.close()

### 2019-03-15 Article/ms.tex
correct segment working version

@@
 To generate input grid data for the convolutional network, the scanned document image are processed by an OCR engine to acquire the texts and their absolute / relative positions.
-Let the scanned document image is of shape $(w, h)$, the minimum bounding box around the $i$-th interested text $s_i$ be $b_i$ that is restricted by two corner coordinates, where the upper-left corner coordinate in the scanned document be $(x^i_{left}, y^i_{top})$ and the bottom right of the bounding box be $(x^i_{right}, y^i_{bottom})$.
+Let the scanned document image be of shape $(w, h)$, the minimum bounding box around the $i$-th interested text $s_i$ be $b_i$ that is restricted by two corner coordinates, where the upper-left corner coordinate in the scanned document be $(x^i_{left}, y^i_{top})$ and the bottom right of the bounding box be $(x^i_{right}, y^i_{bottom})$.
 To avoid the affects from overlapped bounding boxes and reveal the actual relative position among texts, we calculate the center point $(c^i_x, c^i_y)$ of the bounding boxes as the reference position.
@@
 
-Let the grid positional mapping process be $G$ and the target grid size be $(c_{g_0}, r_{g_0})$.
+Let the grid positional mapping process be $G$ and the target grid size be $(c_{g_m}, r_{g_m})$.
 To generate the grid data, the goal of $G$ is to map the texts from the original scanned document image to the target grid, such that the mapped grid preserves the original spatial relationship among texts yet more suitable to be used as the input for the convolutional network.
@@
 \label{cx}
-c^i_x = c_{g_0} \frac{x_l + \frac{(x_r - x_l)}{2}}{w}
+c^i_x = c_{g_m} \frac{x_{left} + \frac{(x_{right} - x_{left})}{2}}{w}
+\end{equation}
+\begin{equation}
+\label{cy}
+r^i_y = r_{g_m} \frac{y_{top} + \frac{(y_{bottom} - y_{top})}{2}}{h}
 \end{equation}
 
+For tokenized texts, the bounding box is horizontally divided into multiple boxes and their row and col reference positions are calculated using the same criteria as Equ.
+\ref{cx} and Equ.
+\ref{cy}, separately.
+Furthermore, to enhance the capability of CUTIE to better handle documents with different layouts, we augment the grid data to shapes with different rows and columns by random sampling a Gaussian distribution for with probability
+
 \begin{equation}
-\label{cy}
-r^i_y = r_{g_0} \frac{y_t + \frac{(y_b - y_t)}{2}}{h}
+\label{augmentc}
+p_c(k) = \frac{1}{\sqrt{2 \pi \sigma^2}} e^{- \frac{(k - c_{g_t})^2}{2 \sigma^2}}
 \end{equation}
-
-For tokenized texts, the bounding box is horizontally divided into multiple boxes and their reference positions are calculated using the same criteria as Equ. \ref{cx} and Equ. \ref{cy}, separately.
+\begin{equation}
+\label{augmentr}
+p_r(k) = \frac{1}{\sqrt{2 \pi \sigma^2}} e^{- \frac{(k - r_{g_t})^2}{2 \sigma^2}}
+\end{equation}
+where $c_{g_t}$ is the mean center of the target augment gird size, $r_{g_t}$ is the mean center of the target augment grid size, and $\sigma$ is the standard deviation.
 
@@
 However, spatial resolution is reduced in the encoding process and the decoding process exploits only high resolution but low level features to recover the spatial resolution, the consecutive striding encoding process decimates detail information which is detrimental to the sparse grid.
+Moreover, the encoding and decoding process applies shape restricts to the grid shape augment process.
+
 Instead, the field of view of filters can also be effectively enlarged by applying atrous convolution \cite{deeplab, deeplabv1, deeplabv3, deeplabv3p}.
-
-To capture long distance connection and avoid potential loss in the encoding process, we propose to employ the convolutional network with atrous convolution and without the encoder-decoder structure.
+To capture long distance connection and avoid potential information loss in the encoding process, we propose to employ the convolutional network with atrous convolution and without the encoder-decoder structure.
 Let the input feature map be $m$, filter be $w$ and output be $n$, for each position $i$, atrous convolution is applied over the input feature map $m$ as
@@
 
-Two types of architectures are developed for CUITE.
-
-\subsection{Grid Augmentation}
-\label{gridaugmentation}
+The proposed network avoids information loss in the encoding process while taking advantage of encoders by combining encoding results to the maintained high-resolution representations through the entire convolutional process.
+Similar to HRNet proposed in \cite{hrnet}, a high-resolution network without striding is employed as the backbone major network, then several high-to-low resolution sub networks are gradually added and connected to the backbone major network.
+During the connecting process of the major network and sub networks, multi-scale features are fused to generate rich representations.
 

### 2019-03-15 data_loader_json.py

@@ -364,7 +364,7 @@ class DataLoader():
             
             items.sort(key=lambda x: (x[0], x[3], x[5])) # sort according to row > h_c > bbox_id
             for item in items:
-                row, col, v_c, h_c, file_name, dict_id, class_id, bbox_id, box = item                
+                row, col, v_c, h_c, file_name, dict_id, class_id, bbox_id, box = item
                 while col < cols and grid_table[row, col] != 0:
                     col += 1
                     
@@ -374,9 +374,10 @@ class DataLoader():
                     while ptr<cols and grid_table[row, ptr] != 0:
                         ptr += 1
                     if ptr == cols:
-                        print(grid_table[row,:])
-                        print('overlap in {} <{}> row {} r{}c{}!'.
-                              format(file_name, self.index_to_word[dict_id], row, rows, cols))
+                        pass
+                        #print(grid_table[row,:])
+                        #print('overlap in {} <{}> row {} r{}c{}!'.
+                        #      format(file_name, self.index_to_word[dict_id], row, rows, cols))
                     else:
                         #print('shift in {} for row {}'.format(file_name, row))
                         grid_table[row, ptr:-1] = grid_table[row, ptr+1:]
@@ -581,24 +582,32 @@ class DataLoader():
             content_dressed_left = []
             content_dressed_right = []
             cnt = defaultdict(int) # counter for number of words in a specific row
+            #cnt_l, cnt_r = defaultdict(int), defaultdict(int)
             left_boundary = max_cols - self.cols_target
             right_boundary = self.cols_target
             for i, line in enumerate(content_dressed):
                 file_name, dressed_text, word_id, [x_left, y_top, x_right, y_bottom] = line
                 
-                row = y_top + (y_bottom-y_top)/2
+                row = int(max_rows * (y_top + (y_bottom-y_top)/2) / bottom)
                 cnt[row] += 1                
                 if cnt[row] <= left_boundary:
+                    #cnt_l[row] += 1
                     content_dressed_left.append([file_name, dressed_text, word_id, [x_left, y_top, x_right, y_bottom], \
                                       [left, top, right, bottom], max_rows, self.cols_target])
-                elif left_boundary < cnt[row] < right_boundary:
+                elif left_boundary < cnt[row] <= right_boundary:
+                    #cnt_l[row] += 1
+                    #cnt_r[row] += 1
[…]

### 2019-03-15 main_train_json.py

@@ -14,8 +14,8 @@ from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
 # data
-parser.add_argument('--doc_path', type=str, default='data/meals')
-parser.add_argument('--save_prefix', type=str, default='meals', help='prefix for ckpt') # TBD: save log/models with prefix
+parser.add_argument('--doc_path', type=str, default='data/hotel')
+parser.add_argument('--save_prefix', type=str, default='hotel', help='prefix for ckpt') # TBD: save log/models with prefix
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
 # ckpt

### 2019-03-16 Article/ms.tex
updated positional mapping strategy with new strategy 2

@@
 \section{Methods}
+In this section, we introduce the method proposed for creating grid data for training the convolutional network.
+We then present the network architectures that capture long distance information and avoid information loss in the previous works with striding or pooling processes.
+
 \subsection{Grid Positional Mapping}
@@
 
-Instead, the field of view of filters can also be effectively enlarged by applying atrous convolution \cite{deeplab, deeplabv1, deeplabv3, deeplabv3p}.
-To capture long distance connection and avoid potential information loss in the encoding process, we propose to employ the convolutional network with atrous convolution and without the encoder-decoder structure.
-Let the input feature map be $m$, filter be $w$ and output be $n$, for each position $i$, atrous convolution is applied over the input feature map $m$ as
+Instead, the field of view of filters can also be effectively enlarged by combining multi-resolution features \cite{hrnet} or by applying atrous convolution \cite{deeplab, deeplabv1, deeplabv3, deeplabv3p}.
+To capture long distance connection and avoid potential information loss in the encoding process, we propose CUTIE-A to employ convolutional multi-resolution fusion network without losing high-resolution features and CUTIE-B network with atrous convolution.
+
+CUTIE-A avoids information loss in the encoding process while taking advantage of encoders by combining encoding results to the maintained high-resolution representations through the entire convolutional process.
+Similar to HRNet proposed in \cite{hrnet}, a high-resolution network without striding is employed as the backbone major network and several high-to-low resolution sub networks are gradually added and connected to the backbone major network.
+During the connecting process of the major network and sub networks, multi-scale features are fused to generate rich representations.
+
+CUTIE-B is constructed with a single backbone network but employs atrous convolution to capture long distance connections.
+For atrous convolution, let the input feature map be $m$, filter be $w$ and output be $n$, for each position $i$, atrous convolution is applied over the input feature map $m$ as
 
@@
 
-The proposed network avoids information loss in the encoding process while taking advantage of encoders by combining encoding results to the maintained high-resolution representations through the entire convolutional process.
-Similar to HRNet proposed in \cite{hrnet}, a high-resolution network without striding is employed as the backbone major network, then several high-to-low resolution sub networks are gradually added and connected to the backbone major network.
-During the connecting process of the major network and sub networks, multi-scale features are fused to generate rich representations.
+Both CUTIE-A and CUITE-B conducts word embedding in the very beginning stage. The cross entropy loss function is applied to compare the predicted token class grid and the ground truth grid.
 
 \section{Experiments}
+The proposed method is evaluated on a dataset with with 3 types of documents which contain 9 key information classes and 1 don't care class.
+The dataset contains 4000 per-token annotated documents.
+We generate the text and bounding box features with Google's OCR API.
+The performance is measured in terms of per-token accuracy across the 10 classes.
+
+We use a learning rate of 1e-3 for training with Adam optimizer with step decay learning strategy, and the learning rate is dropped to 1e-4 and 1e-5 on the 15000-th and 30000-th steps, respectively.
+The training is terminated within 40000 steps with batch size of 32.
+Our model is trained end-to-end without piecewise pretraining of each component.
+The embedding size is 128, target augmentation shape is 64 for both row and column.
+
+\begin{table}
+	\caption{Performance comparison on 3 types of documents}
+\begin{center}
+\begin{tabular}{l | c | c | c | c}
+	Method & \#Params & Meals & Taxi & hotel \\
+	\hline
+	CloudScan & - & & & \\
+	BERT & 110M & 80.31 & 87.02 & 79.42 \\
+	CUTIE-A & 66M & 82.5 & & \\
+	CUTIE-B & 16M & & \\
+\end{tabular}
+\end{center}
+\end{table}
 

### 2019-03-16 data_loader_json.py

@@ -44,6 +44,7 @@ class DataLoader():
         self.cols = self.encoding_factor # to be updated 
         self.segment_grid = params.segment_grid if hasattr(params, 'segment_grid') else False # segment grid into two parts if grid is larger than cols_target
         self.augment_strategy = params.augment_strategy if hasattr(params, 'augment_strategy') else 1 
+        self.pm_strategy = params.positional_mapping_strategy if hasattr(params, 'positional_mapping_strategy') else 2 
         self.rows_target = params.rows_target if hasattr(params, 'rows_target') else 64 
         self.cols_target = params.cols_target if hasattr(params, 'cols_target') else 64 
         self.rows_ulimit = params.rows_ulimit if hasattr(params, 'rows_ulimit') else 80 # handle OOM, must be multiple of self.encoding_factor
@@ -164,11 +165,16 @@ class DataLoader():
         # data augmentation in each batch if self.data_augmentation==True
         rows, cols, pre_rows, pre_cols = self._cal_rows_cols(training_docs, extra_augmentation=self.data_augmentation_extra, dropout=self.data_augmentation_dropout)
         if self.data_augmentation_extra:
-            print('Training grid table augment size: ({},{}) from ({},{})'\
+            print('Training grid AUGMENT size: ({},{}) from ({},{})'\
                   .format(rows, cols, pre_rows, pre_cols))
         
-        grid_table, gt_classes, bboxes, label_mapids, bbox_mapids, file_name = \
+        grid_table, gt_classes, bboxes, label_mapids, bbox_mapids, file_name, updated_cols = \
             self._positional_mapping(training_docs, self.training_labels, rows, cols)   
+        if updated_cols > cols:
+            print('Training grid EXPAND size: ({},{}) from ({},{})'\
+                  .format(rows, updated_cols, rows, cols))
+            grid_table, gt_classes, bboxes, label_mapids, bbox_mapids, file_name, _ = \
+                self._positional_mapping(training_docs, self.training_labels, rows, updated_cols)  
             
         #grid_table = np.ones([self.batch_size, self.rows, self.cols, 1])
         #gt_classes = np.ones([self.batch_size, self.rows, self.cols])
@@ -193,8 +199,13 @@ class DataLoader():
         rows = max(self.rows_target, real_rows)
         cols = max(self.cols_target, real_cols)
         
-        grid_table, gt_classes, bboxes, label_mapids, bbox_mapids, file_name = \
[…]

### 2019-03-16 main_train_json.py

@@ -14,8 +14,8 @@ from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
 # data
-parser.add_argument('--doc_path', type=str, default='data/hotel')
-parser.add_argument('--save_prefix', type=str, default='hotel', help='prefix for ckpt') # TBD: save log/models with prefix
+parser.add_argument('--doc_path', type=str, default='data/hotel_small')
+parser.add_argument('--save_prefix', type=str, default='hotel_small', help='prefix for ckpt') # TBD: save log/models with prefix
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
 # ckpt
@@ -35,9 +35,10 @@ parser.add_argument('--dict_path', type=str, default='dict/---') # not used if l
 
 # data manipulation
 parser.add_argument('--segment_grid', type=bool, default=True) # segment grid into two parts if grid is larger than cols_target
-parser.add_argument('--rows_target', type=int, default=72) 
-parser.add_argument('--cols_target', type=int, default=72) 
+parser.add_argument('--rows_target', type=int, default=64) 
+parser.add_argument('--cols_target', type=int, default=64) 
 parser.add_argument('--augment_strategy', type=int, default=2) # 1 for increasing grid shape size, 2 for gaussian around target shape
+parser.add_argument('--positional_mapping_strategy', type=int, default=2)
 parser.add_argument('--rows_ulimit', type=int, default=88) 
 parser.add_argument('--cols_ulimit', type=int, default=88) 
 parser.add_argument('--fill_bbox', type=bool, default=False) # fill bbox with dict_id / label_id

### 2019-03-20 Article/ms.tex
article updated

--- 2019-03-15 Article/ms.tex
@@
 \documentclass[10pt,twocolumn,letterpaper]{article}
+
+\usepackage{float}
+\usepackage[caption = false]{subfig}
+\usepackage[final]{graphicx}
 
@@
    Extracting key information from documents, such as receipts or invoices, and preserving the interested texts to structured data is crucial in the document-intensive streamline processes of office automation in areas that includes but not limited to accounting, financial, and taxation areas.
-Large proportion of published works attempt to tackle the problem by exploring the semantic context in text sequences based on the named entity recognition method in NLP field.
+Large proportion of published works attempt to tackle the problem by exploring the semantic context in text sequences based on the Named Entity Recognition (NER) method in the NLP field.
 In this paper, we propose to combine the effective information from both semantic meaning and spatial distribution of texts in documents.
-Specifically, our proposed model, Convolutional Universal Text Information Extractor (CUTIE), applies convolutional networks on the gridded texts where texts are embedded as features with semantical connotations.
-We further explore the effect of employing different structures of convolutional network and propose a faster and portable structure.
-We demonstrate the effectiveness of the proposed method on a dataset with up to 3000 labelled receipts, without any post-processing, achieving state-of-the-art performance that is higher than BERT but with only 1/10 parameters and much higher than the RNN based methods.
+Specifically, our proposed model, Convolutional Universal Text Information Extractor (CUTIE), applies convolutional neural networks on the gridded texts where texts are embedded as features with semantical connotations.
+We further explore the effect of employing different structures of convolutional neural network and propose a faster and portable structure.
+We demonstrate the effectiveness of the proposed method on a dataset with up to $5000$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is higher than BERT but with only 1/10 parameters and much higher than the other RNN based methods.
 \end{abstract}
@@
 History about published learning based methods goes here.
-The majority of the published learning based works are based on the named entity recognition research in the NLP field that is not originally designed to solve the key information extraction problem in SROIE, which align text words in the original document as a long paragraph in line-based rule.
-However, the real world documents, such as receipts and invoices, present with various styles of layouts that were designed for different scenarios or from different enterprise entities, which introduces great difficulties.
-The order or distance of the texts in the line-based aligned long paragraph tend to vary greatly due to layout variations, which is difficult to be handled with the natural language paragraph oriented methods, one typical example is illustrated in Fig.
-\ref{fig:short}.
-
-Attempting to involve the spatial information into the key information extraction process, we propose to tackle this problem by using the CNN based network structure and involve the semantic features in a properly designed fashion.
-In particular, our proposed model, called Convolutional Universal Text Information Extractor (CUTIE), tackles the key information extraction problem by applying convolutional deep learning model on the gridded texts, as illustrated in Fig.
-\ref{fig:onecol}.
-The gridded texts is the formatted input of the entire network, which is arranged in close correspondance with their real spatial relationship of the original scanned document image.
-Furthermore, the rich semantic information is encoded from the gridded texts in the very beginning of the convolutional network.
-
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
+The majority of the published learning based works are based on the Named Entity Recognition (NER) research in the NLP field that is not originally designed to solve the key information extraction problem in SROIE, which align text words in the original document as a long paragraph in line-based rule.
+However, the real world documents, such as receipts and invoices, present with various styles of layouts that were designed for different scenarios or from different enterprise entities.
+The order or word-to-word distance of the texts in the line-based aligned long paragraph tend to vary greatly due to layout variations, which is difficult to be handled with the natural language paragraph oriented methods, one typical example is illustrated in Fig.
+\ref{fig:receipts}.
 
@@
 \begin{center}
-\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
+\includegraphics[width=0.99\linewidth]{Model.png}
 \end{center}
-   \caption{Example of a short caption, which should be centered.}
-\label{fig:short}
+   \caption{Framework of the proposed method, (a) positional map the scanned document image to a grid with text's relative spatial relationship preserved, (b) feed the generated grid into the CNN for extracting key information, (c) reverse map the extracted key information for visual reference.}
+\label{fig:cutie}
 \end{figure*}
+In this work, attempting to involve the spatial information into the key information extraction process, we propose to tackle this problem by using the CNN based network structure and involve the semantic features in a properly designed fashion.
+In particular, our proposed model, called Convolutional Universal Text Information Extractor (CUTIE), tackles the key information extraction problem by applying convolutional deep learning model on the gridded texts, as illustrated in Fig.
+\ref{fig:cutie}.
+The gridded texts is formed with the proposed grid positional mapping method, where the grid is generated with the principle that is preserving text's relative spatial relationship in the original scanned document image.
+The rich semantic information is encoded from the gridded texts at the very beginning stage of the convolutional neural network with a word embedding layer.
+The CUTIE allows for simutaneously looking into both semantical information and spatial information of the texts in the scanned document image and can reach a new state of the art result for key information extraction, which outperforms BERT model but without demanding pretrain on a huge text dataset \cite{bert,transformer}.
 
@@
 \section{Methods}
+In this section, we introduce the method proposed for creating grid data for model training.
+We then present the network architectures that capture long distance information and avoid information loss in the convolutional neural networks that have striding or pooling processes.
+
 \subsection{Grid Positional Mapping}
-To generate input grid data for the convolutional network, the scanned document image are processed by an OCR engine to acquire the texts and their absolute / relative positions.
+\label{pm}
+To generate input grid data for the convolutional neural network, the scanned document image are processed by an OCR engine to acquire the texts and their absolute / relative positions.
 Let the scanned document image be of shape $(w, h)$, the minimum bounding box around the $i$-th interested text $s_i$ be $b_i$ that is restricted by two corner coordinates, where the upper-left corner coordinate in the scanned document be $(x^i_{left}, y^i_{top})$ and the bottom right of the bounding box be $(x^i_{right}, y^i_{bottom})$.
 To avoid the affects from overlapped bounding boxes and reveal the actual relative position among texts, we calculate the center point $(c^i_x, c^i_y)$ of the bounding boxes as the reference position.
-It is not hard to find that involving pre-processes that combine texts into meaningful entities here will benefit the following grid positional mapping process.
+It is not hard to find that involving pre-processes that combine texts into meaningful entities will benefit the grid positional mapping process.
 However, this is not the major purpose of this paper and we leave it to future researches.
@@
 Let the grid positional mapping process be $G$ and the target grid size be $(c_{g_m}, r_{g_m})$.
-To generate the grid data, the goal of $G$ is to map the texts from the original scanned document image to the target grid, such that the mapped grid preserves the original spatial relationship among texts yet more suitable to be used as the input for the convolutional network.
+To generate the grid data, the goal of $G$ is to map the texts from the original scanned document image to the target grid, such that the mapped grid preserves the original spatial relationship among texts yet more suitable to be used as the input for the convolutional neural network.
+The mapping position of texts in the grid is calculated as
 
@@
 
-\subsection{Model}
+\subsection{CUTIE Model}
 Through matching the output of CUTIE with the labelled grid data, the model learns to generate the label for each text in the grid input via exploring both the spatial and semantic features.
 For that reason, the task of CUTIE bears resemblance to the semantic segmentation task in the computer vision field but with more sparse data distributions.
-Specifically, the mapped grid contains scattered data points (texts) in contrast to the images bespread with pixels.
+Specifically, the mapped grid contains scattered data points (text tokens) in contrast to the images bespread with pixels.
 The grid positional mapped key texts are either close to or distant to each other due to different types of document layouts.
+Therefore, incorporating multi-scale context processing ability benefits the network.
 
-In fact, several methods have been proposed in the semantic segmentation field to capture multi-scale context in the input data.
+In fact, several methods have been proposed in the semantic segmentation field to capture multi-scale contexts in the input data.
 The methods of image pyramid and the encoder-decoder structure both aim at exploiting multi-scale information.
@@
 The later networks shrink feature maps to enlarge receptive fields and reduce computation burdens, and then capture finer details by gradually recovering the spatial information from lower layer features.
-However, spatial resolution is reduced in the encoding process and the decoding process exploits only high resolution but low level features to recover the spatial resolution, the consecutive striding encoding process decimates detail information which is detrimental to the sparse grid.
-Moreover, the encoding and decoding process applies shape restricts to the grid shape augment process.
+However, spatial resolution is reduced in the encoding process and the decoding process exploits only high resolution but low level features to recover the spatial resolution, the consecutive striding encoding process decimates detail information \cite{hrnet}.
+Moreover, the encoding and decoding process applies shape restricts to the grid shape augment process as introduced in Section \ref{pm}.
 
-Instead, the field of view of filters can also be effectively enlarged by applying atrous convolution \cite{deeplab, deeplabv1, deeplabv3, deeplabv3p}.
-To capture long distance connection and avoid potential information loss in the encoding process, we propose to employ the convolutional network with atrous convolution and without the encoder-decoder structure.
-Let the input feature map be $m$, filter be $w$ and output be $n$, for each position $i$, atrous convolution is applied over the input feature map $m$ as
+Instead, the field of view of filters can also be effectively enlarged and multi-scale contexts can be captured by combining multi-resolution features \cite{hrnet} or by applying atrous convolution \cite{deeplab, deeplabv1, deeplabv3, deeplabv3p}.
+To capture long distance connection and avoid potential information loss in the encoding process, we propose two different network architectures and compare their performance in Section \ref{experiment}.
+Specifically, proposed CUTIE-A is a high capacity convolutional neural network that fuses multi-resolution features without losing high-resolution features, proposed CUTIE-B is a convolutional network with atrous convolution for enlarging field of view and Atrous Spatial Pyramid Pooling (ASPP) module to capture multi-scale contexts.
+
+Both CUTIE-A and CUITE-B conducts semantical meaning encoding process with a word embedding layer in the very beginning stage.
+The cross entropy loss function is applied to compare the predicted token class grid and the ground truth grid.
+
+\subsubsection{CUTIE-A}
+CUTIE-A avoids information loss in the encoding process while taking advantage of encoders by combining encoding results to the maintained high-resolution representations through the entire convolutional process.
+Similar to HRNet proposed in \cite{hrnet}, a high-resolution network without striding is employed as the backbone network and several high-to-low resolution sub networks are gradually added and connected to the backbone major network.
+During the connecting process of the major network and sub networks, multi-scale features are fused to generate rich representations.
+
+\subsubsection{CUTIE-B}
+CUTIE-B is constructed with a single backbone network but employs atrous convolution to capture long distance connections.
+For atrous convolution, let the input feature map be $m$, filter be $w$ and output be $n$, for each position $i$, atrous convolution is applied over the input feature map $m$ as
 
@@
 where $r$ is the atrous rate that indicates the sampling stride of the input signal, which is implemented as convolving the input feature with upsampled filters by inserting $r-1$ zeros between two consecutive filter values along each spatial dimension.
-Standard convolution is a special case of atrous convolution with $r=1$.
-
-The proposed network avoids information loss in the encoding process while taking advantage of encoders by combining encoding results to the maintained high-resolution representations through the entire convolutional process.
-Similar to HRNet proposed in \cite{hrnet}, a high-resolution network without striding is employed as the backbone major network, then several high-to-low resolution sub networks are gradually added and connected to the backbone major network.
-During the connecting process of the major network and sub networks, multi-scale features are fused to generate rich representations.
+Standard convolution is a special case of atrous convolution with $r=1$ \cite{deeplabv1}.
 
 \section{Experiments}
+\label{experiment}
+The proposed method is evaluated on a dataset with $3$ types of scanned document images, which contain $8$ key information classes and $1$ don't care class.
+For each specific key information class, multiple tokens can be included.
+The overall performance is refered as strict average precision (AP) and measured in terms of per-class accuracy across the $9$ classes, where one class is determined as correct only when every single token in the class is correct.
+To achieve deeper analysis of the performance of the proposed method, we propose to use one more criteria, soft average precision (softAP), where the prediction of a key information class is determined as correct as if positive ground truths are correctly predicted even if some false positive are included in the final prediction.
+SoftAP is important since it indicates model's capability of extracting correct key information with tolerance of incorporating certain false positives.
+In fact, post processings can be employed there to eliminate the false positives.
+Therefore, joint analysis of AP and softAP provides a better understanding of the model performance.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\linewidth]{Receipts.png}
+\end{center}
+   \caption{Example of scanned taxi receipt images.
+We provide two colored rectangles to help readers find the key information about distance of travel and total amount with blue and red, respectively.
+Note the different types of spatial layouts and key information texts in these receipt images.}
+\label{fig:receipts}
+\end{figure}
+
+We compare the performance of the proposed method with two state of the art methods CloudScan \cite{cloudscan} and BERT \cite{bert}.
+For comparison, the Cloud Scan model for SROIE is trained from scratch but with several expert designed features as describded in \cite{cloudscan}.
+The BERT model for SROIE is transform learned with the Google released base model that is pre-trained on a huge dataset with $3,300M$ words \cite{bert,bertgit}.
+
+We use a learning rate of $1e-3$ with Adam optimizer and step decay learning strategy.
+The learning rate is dropped to $1e-4$ and $1e-5$ on the $15000$-th and $30000$-th steps, respectively.
+The training is terminated within $40000$ steps with batch size of $32$.
+Our model is trained end-to-end without piecewise pretraining of any component.
+The embedding size is $128$, target augmentation shape is $64$ for both row and column.
+The dataset is split as training set and test set with ratio of $7:3$.
+
+\subsection{Dataset}
+The dataset contains $4000$ annotated scanned spanish receipt documents, including taxi receipts and meal entertainment (ME) receipts, with $9$ different key information classes, as reported in Table \ref{tab:dataset}.
+We generate the texts and bounding boxes with Google's OCR API.
+Each text and their bounding box is manually labelled as one of the 9 different classes: 'DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', and 'TaxRate'.
+We then employ the tokenizer introduced in Section \ref{pm} to segment texts into minimum token units, where text bounding boxes are also segmented accordingly.
+
+In fact, the dataset is much difficult than the neat scanned document images, since various layouts of receipts were captured in different scenarios using ordinary mobile phone camera.
+Examples of the scanned document images in our dataset are illustrated in Figure \ref{fig:receipts}, note that the colored rectangles is only for visual reference, the actual labelled data is in token-level rather than the line-level that is shown in the figure.
+\begin{table}
+	\caption{Number of labelled receipt document images and key information classes of different types of documents in the labelled dataset.}
+\begin{center}
+\begin{tabular}{l | c | c | c}
+	 & Training Set & Test Set & \#classes \\
+	\hline
+	ME & 1109 & 475 & 9 \\
+	Taxi & 2514 & 1077 & 6 \\
+\end{tabular}
+\end{center}
+	\label{tab:dataset}
+\end{table}
+
+\subsection{Results on Validation Set}
+We report results of our method and compare with other state of the art methods in Table \ref{tab:comparison}.
+Our big network CUTIE-A achieves $100$ score on meals entertainment receipt and $100$ score on taxi receipt, outperforming other methods.
+Compared to CloudScan, our big network CUTIE-A improves AP by $100$ on meals entertainment receipt and $100$ on taxi receipt, our small network CUTIE-B improves AP by $100$ points on meals entertainment receipt and $100$ on taxi receipt.
+Compared to BERT, where model is pre-trained on a dataset with $3,300M$ words and transfer learned on our dataset, our big network CUTIE-B improves AP by $100~100$ while using only $1/2$ parameters, our small network CUTIE-B improves AP by $100~100$ but with much less complexity and smaller model size with only $1/10$ parameters.
+Examples of inference results are illustrated in Figure \ref{fig:result}.
+\begin{figure*}
+\begin{center}
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_0.png}} 
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.4\linewidth]{appendix/Correct_1.png}}
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_2.png}}
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_3.png}} \\ 
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_4.png}}  
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_5.png}}  
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_9.png}}  
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_7.png}}  
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_8.png}} 
+\end{center}
+   \caption{Example of inference results of CUITE.
+Color legend in the top-left corner indicates the key information classes.
+Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
+The result is perfectly correct as if the filled rectangles overlap with the boundary-only rectangles.}
+\label{fig:result}
+\end{figure*}
+
+We also provides softAP results for CUTIE-A and CUTIE-B in Table \ref{tab:comparison}, where both the softAP of CUTIE-A and CUTIE-B exceeds AP by a large margin.
+Typical examples of receipts with low AP but high softAP score is shown in Figure \ref{fig:falsepositive}.
+Most of the false positive cases occor in the 'VenderName' class, where names tend to greatly vary and leads to difficulty in model inference.
+It is not hard to find that, however, these false positives can be easily avoided by appending a dictionary based post processor to the key information extractor.
+One rare false posive case in the $4$-th image is a 'L' letter being mis-recognized as '1' by the employed OCR engine.
+Although the letter shows distinct appearance with the other digits, it is mis-interpreted as one part of the 'BaseAmount' class due to its close spatial location to the digits and it-self being a digit.
+Although this is one and only special case in our test set, it still suggests that incorporating image-level information may further boost the inference accuracy inspite of the already involved semantical and spatial features.
+\begin{table}
+	\caption{Performance comparison on 3 types of documents. (AP/softAP)}
+\begin{center}
+\begin{tabular}{l | c | c | c | c}
+	Method & \#Params & ME & Taxi & Hotel \\
+	\hline
+	CloudScan & - & 82 / - & 64 / - & \\
+	BERT & 110M & 80.3 / - & 87.0 / - & 79.4 / - \\
+	CUTIE-A & 67M & 82.5 / & / & / \\
+	CUTIE-B & 14M & / & / \\
+\end{tabular}
+\end{center}
+	\label{tab:comparison}
+\end{table}
+
+\begin{figure}
+\begin{center}
+\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalsePositive_0.png}} 
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalsePositive_1.png}}\\
+\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalsePositive_2.png}}
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalsePositive_3.png}}
+\end{center}
+   \caption{Example of prediction results of CUITE with false positive inference results.
+Color legend in the top-left corner indicates the key information classes.
+Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
+The false positive are results with the boundary-only rectangles not overlap with the filled rectangles.}
+\label{fig:falsepositive}
+\end{figure}
+
+Furthermore, we find that some cases are determained as not right while the ground truth were wrongly labelled by the human labeller.
+As illustrated in Figure \ref{fig:falselabel}, the 'VendorName' appears twice in the scanned image but only being labelled once while the model correctly interprets both occurance as the 'VendorName'.
+\begin{figure}
+\begin{center}
+\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalseLabel_0.png}} 
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.35\linewidth]{appendix/FalseLabel_1.png}}\\
+\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalseLabel_2.png}}
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalseLabel_3.png}}
+\end{center}
+   \caption{Example of prediction results of CUITE with false positive inference results.
+Color legend in the top-left corner indicates the key information classes.
+Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.}
+\label{fig:falselabel}
+\end{figure}
+
+\subsection{Ablation Studies}
+Although we have demonstrated extremely strong empirical results, the results presented are achieved by combination of each aspect of the CUTIE framework.
+In this section, we perform ablation studies over a number of facets of CUTIE in order to better understand their relative importance.
+
+\subsubsection{Effect of Grid Augmentation on Understanding Spatial Information}
+One of our core claim is that the high performance CUTIE is achieved by jointly analysis of the semantical and spatial information with the proposed framework.
+The highly effective spatial analysis ability is enabled by the CUTIE framework in contrast with the previous NER based methods.
+The grid augmentation process further enhances this ability.
+To give evidence to this claim, we evaluate CUTIE with or without the grid augmentation process.
+Results are presented in Table \ref{tab:augmentation}.
+We can see that adding grid augment process in CUTIE can significantly improve the performance on meal entertainment receipt and taxi receipt.
+These results demonstrate that CUTIE can greatly benefit from enhancing data diversity in spatial distribution.
+For that reason, further analysis about grid augmentation techniques will surely further enhance CUTIE's performance, \eg, randomly moving certain texts upward, downward, leftward, or rightward by several pixels during the grid positional mapping process.
+\begin{table}
+	\caption{Performance evaluation of CUTIE with or without the grid augmentation process. (AP/softAP)}
+\begin{center}
+\begin{tabular}{l | c | c | c}
+	 & MEnter & Taxi & Hotel \\
+	\hline
+	w augmentation & / & / & \\
+	w/o augmentation & / & / & \\
+\end{tabular}
+\end{center}
+	\label{tab:augmentation}
+\end{table}
+
+\subsubsection{Impact of Semantical Information Capacity}
+Next, we evaluate the impact of semantical information of CUTIE by comparing evaluation with different word embedding sizes, although it is intuitively clear that larger embedding size provides more semantic capacity.
+As reported in Table \ref{tab:embedding}, CUTIE performs worse with smaller embedding size.
+The result meets our expection that $details$.
+To further enhance the model performance, it might help to randomly mask out certain texts during the grid positional mapping process, such that the model learns inter-text relationship better with / without all words present in the grid and improves in generality.
+\begin{table}
+	\caption{Performance evaluation of CUTIE with different embedding size. (AP/softAP)}
+\begin{center}
+\begin{tabular}{l | c | c | c}
+	 & 64 & 128 & 256 \\
+	\hline
+	 & / & / & \\
+	 & / & / & \\
+\end{tabular}
+\end{center}
+	\label{tab:embedding}
+\end{table}
 
@@
 Automatically extracting interested words / information from the scanned document images is of great interest to various services and applications.
-The performance gain is mainly achieved by exploring three key factors: the spatial relationship among texts, the semantic information of texts, and the text gridding mechanism.
+The performance gain is mainly achieved by exploring three key factors: the spatial relationship among texts, the semantic information of texts, and the grid positional mapping mechanism.
 
@@
 
+\section{APPENDIX}
+
 \end{document}

### 2019-03-20 data_loader_json.py

@@ -11,7 +11,7 @@ import numpy as np
 import tensorflow as tf
 import tokenization
 
-DEBUG = False
+DEBUG = False # True to show grid as image 
 
 import unicodedata
 def is_number(s):
@@ -34,7 +34,8 @@ class DataLoader():
     """
     def __init__(self, params, update_dict=True, load_dictionary=False, data_split=0.75):
         self.random = False
-        self.encoding_factor = 8 # ensures the size (rows/cols) of grid table compat with the network
+        self.encoding_factor = 1 # ensures the size (rows/cols) of grid table compat with the network
+        self.doc_path = params.doc_path
         self.text_case = params.text_case 
         self.tokenize = params.tokenize
         if self.tokenize:
@@ -45,6 +46,8 @@ class DataLoader():
         self.segment_grid = params.segment_grid if hasattr(params, 'segment_grid') else False # segment grid into two parts if grid is larger than cols_target
         self.augment_strategy = params.augment_strategy if hasattr(params, 'augment_strategy') else 1 
         self.pm_strategy = params.positional_mapping_strategy if hasattr(params, 'positional_mapping_strategy') else 2 
+        self.rows_segment = params.rows_segment if hasattr(params, 'rows_segment') else 72 
+        self.cols_segment = params.cols_segment if hasattr(params, 'cols_segment') else 72
         self.rows_target = params.rows_target if hasattr(params, 'rows_target') else 64 
         self.cols_target = params.cols_target if hasattr(params, 'cols_target') else 64 
         self.rows_ulimit = params.rows_ulimit if hasattr(params, 'rows_ulimit') else 80 # handle OOM, must be multiple of self.encoding_factor
@@ -81,7 +84,7 @@ class DataLoader():
         self.special_dict = {'*', '='} # map texts to specific tokens        
         
         ## 1.1> load words and their location/class as training/validation docs and labels 
-        self.training_doc_files = self._get_filenames(params.doc_path)
+        self.training_doc_files = self._get_filenames(self.doc_path)
         self.training_docs, self.training_labels = self.load_data(self.training_doc_files, update_dict=update_dict) # TBD: optimize the update dict flag
         
         # polish and load dictionary/word_to_index/index_to_word as file
@@ -174,7 +177,7 @@ class DataLoader():
             print('Training grid EXPAND size: ({},{}) from ({},{})'\
                   .format(rows, updated_cols, rows, cols))
             grid_table, gt_classes, bboxes, label_mapids, bbox_mapids, file_name, _ = \
[…]

### 2019-03-20 main_evaluate_json.py

@@ -8,25 +8,23 @@ import argparse
 import os, csv
 os.environ["CUDA_VISIBLE_DEVICES"] = "1"
 
-from model_cutie import CUTIE
 from model_cutie_hr import CUTIERes
-from model_cutie_unet8 import CUTIEUNet
-from model_cutie_sep import CUTIESep
 from data_loader_json import DataLoader
 from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--doc_path', type=str, default='data/meals_1215/') # modify this
+parser.add_argument('--doc_path', type=str, default='data/meals_1108/') # modify this
 parser.add_argument('--save_prefix', type=str, default='meals', help='prefix for ckpt and results') # modify this
 
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 
 parser.add_argument('--e_ckpt_path', type=str, default='../graph/CUTIE/graph/') # modify this
-parser.add_argument('--ckpt_file', type=str, default='CUTIE_residual_highresolution_8x_d20000c9(r128c128)_iter_38802.ckpt')
-parser.add_argument('--rows_ulimit', type=int, default=128) 
-parser.add_argument('--cols_ulimit', type=int, default=128) 
-parser.add_argument('--rows_blimit', type=int, default=80) 
-parser.add_argument('--cols_blimit', type=int, default=80) 
+parser.add_argument('--ckpt_file', type=str, default='CUTIE_highresolution_8x_d20000c9(r80c80)_iter_40000.ckpt')
+parser.add_argument('--positional_mapping_strategy', type=int, default=1)
+parser.add_argument('--rows_target', type=int, default=72) 
+parser.add_argument('--cols_target', type=int, default=72) 
+parser.add_argument('--rows_ulimit', type=int, default=80) 
+parser.add_argument('--cols_ulimit', type=int, default=80) 
 
 parser.add_argument('--load_dict', type=bool, default=True, help='True to work based on an existing dict') 
 parser.add_argument('--load_dict_from_path', type=str, default='dict/20000TC') # 40000 or 119547 or 20000TC
@@ -92,7 +90,7 @@ if __name__ == '__main__':
             recalls += [recall]
             accs_strict += [acc_strict] 
             accs_soft += [acc_soft]
-            print(res) # show res for current batch  
+            print(res.decode()) # show res for current batch  
             
             # visualize result
             shape = data['shape']

### 2019-03-20 main_train_json.py

@@ -8,14 +8,14 @@ import timeit
 from pprint import pprint
 os.environ["CUDA_VISIBLE_DEVICES"] = "1"
 
-from model_cutie_res import CUTIERes
+from model_cutie_aspp import CUTIERes
 from data_loader_json import DataLoader
 from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
 # data
-parser.add_argument('--doc_path', type=str, default='data/hotel_small')
-parser.add_argument('--save_prefix', type=str, default='hotel_small', help='prefix for ckpt') # TBD: save log/models with prefix
+parser.add_argument('--doc_path', type=str, default='data/hotel_1108')
+parser.add_argument('--save_prefix', type=str, default='hotel_1108', help='prefix for ckpt') # TBD: save log/models with prefix
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
 # ckpt
@@ -35,18 +35,20 @@ parser.add_argument('--dict_path', type=str, default='dict/---') # not used if l
 
 # data manipulation
 parser.add_argument('--segment_grid', type=bool, default=True) # segment grid into two parts if grid is larger than cols_target
+parser.add_argument('--rows_segment', type=int, default=72) 
+parser.add_argument('--cols_segment', type=int, default=72) 
+parser.add_argument('--augment_strategy', type=int, default=1) # 1 for increasing grid shape size, 2 for gaussian around target shape
+parser.add_argument('--positional_mapping_strategy', type=int, default=2)
 parser.add_argument('--rows_target', type=int, default=64) 
 parser.add_argument('--cols_target', type=int, default=64) 
-parser.add_argument('--augment_strategy', type=int, default=2) # 1 for increasing grid shape size, 2 for gaussian around target shape
-parser.add_argument('--positional_mapping_strategy', type=int, default=2)
-parser.add_argument('--rows_ulimit', type=int, default=88) 
-parser.add_argument('--cols_ulimit', type=int, default=88) 
+parser.add_argument('--rows_ulimit', type=int, default=80) 
+parser.add_argument('--cols_ulimit', type=int, default=80) 
 parser.add_argument('--fill_bbox', type=bool, default=False) # fill bbox with dict_id / label_id
 
 parser.add_argument('--data_augmentation_extra', type=bool, default=True) # randomly expand rows/cols
 parser.add_argument('--data_augmentation_dropout', type=bool, default=False) # randomly shrink rows/cols
[…]

### 2019-03-20 model_cutie_att.py

@@ -31,26 +31,27 @@ class CUTIERes(CUTIE):
     def setup(self):        
         # input
         (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
+             .embed(self.num_vocabs, self.embedding_size, name='embedding')
+             .conv(3, 5, 128, 1, 1, name='encoder0_1'))  
         
         # encoder
-        (self.feed('embedding')
-             .conv(3, 5, 256, 1, 1, name='encoder1_1')
-             .conv(3, 5, 256, 1, 1, name='encoder1_2')
-             .conv(3, 5, 256, 1, 1, name='encoder1_3')
-             .conv(3, 5, 256, 1, 1, name='encoder1_4'))
+        (self.feed('encoder0_1')
+             .conv(3, 5, 128, 1, 1, name='encoder1_1')
+             .conv(3, 5, 128, 1, 1, name='encoder1_2')
+             .conv(3, 5, 128, 1, 1, name='encoder1_3')
+             .conv(3, 5, 128, 1, 1, name='encoder1_4'))
         
-        (self.feed('embedding', 'encoder1_4')
+        (self.feed('encoder0_1', 'encoder1_4')
              .attention(1, name='attention2')
-             .conv(3, 5, 256, 1, 1, name='encoder1_5')
-             .conv(3, 5, 256, 1, 1, name='encoder1_6')
-             .conv(3, 5, 256, 1, 1, name='encoder1_7')
-             .conv(3, 5, 256, 1, 1, name='encoder1_8')) 
+             .conv(3, 5, 128, 1, 1, name='encoder1_5')
+             .conv(3, 5, 128, 1, 1, name='encoder1_6')
+             .conv(3, 5, 128, 1, 1, name='encoder1_7')
+             .conv(3, 5, 128, 1, 1, name='encoder1_8')) 
         
-        (self.feed('embedding', 'encoder1_8')
+        (self.feed('encoder0_1', 'encoder1_8')
              .attention(1, name='attention5')
-             .conv(3, 5, 256, 1, 1, name='encoder1_9')
-             .conv(3, 5, 256, 1, 1, name='encoder1_10')) 
+             .conv(3, 5, 128, 1, 1, name='encoder1_9')
+             .conv(3, 5, 128, 1, 1, name='encoder1_10')) 
          
         # classification
         (self.feed('encoder1_10') 

### 2019-03-20 utils.py

@@ -46,12 +46,12 @@ def cal_accuracy(data_loader, grid_table, gt_classes, model_output_val, label_ma
             logit_bbox_ids = [bbox_mapid[bbox] for bbox in bbox_id_selected[logits_indexes] if bbox in bbox_mapid]            
             
             #if np.array_equal(labels_indexes, logits_indexes):
-            if set(label_bbox_ids) == set(logit_bbox_ids): 
+            if set(label_bbox_ids) == set(logit_bbox_ids): # decide as correct when all ids match
                 num_correct_strict += 1  
                 num_correct_soft += 1
-            elif set(label_bbox_ids).issubset(set(logit_bbox_ids)):
+            elif set(label_bbox_ids).issubset(set(logit_bbox_ids)): # correct when gt is subset of gt
                 num_correct_soft += 1
-            try:  
+            try: # calculate prevalence with decimal precision
                 num_correct += np.shape(np.intersect1d(labels_indexes, logits_indexes))[0] / np.shape(labels_indexes)[0]
             except ZeroDivisionError:
                 if np.shape(labels_indexes)[0] == 0:
@@ -83,10 +83,10 @@ def cal_accuracy(data_loader, grid_table, gt_classes, model_output_val, label_ma
                         #res += ' "%s"/%.2f%s, '%(w, logits_flat[i], l)
                         
                 #print(res)
-    recall = num_correct / num_all
+    prevalence = num_correct / num_all
     accuracy_strict = num_correct_strict / num_all
     accuracy_soft = num_correct_soft / num_all
-    return recall, accuracy_strict, accuracy_soft, res 
+    return prevalence, accuracy_strict, accuracy_soft, res.encode("utf-8")
 
 
 def cal_save_results(data_loader, save_prefix, docs, grid_table, gt_classes, model_output_val):
@@ -168,21 +168,21 @@ def vis_bbox(data_loader, file_prefix, grid_table, gt_classes, model_output_val,
     logits = model_output_val.reshape([-1, data_loader.num_classes])
     bboxes = bboxes.reshape([-1])
     
+    max_len = 768*2 # upper boundary of image display size 
     img = cv2.imread(join(file_prefix, file_name))
     if img is not None:    
         shape = list(img.shape)
         
         bbox_pad = 1
[…]

### 2019-03-22 Article/ms.tex
paper almost finished

@@
 Specifically, our proposed model, Convolutional Universal Text Information Extractor (CUTIE), applies convolutional neural networks on the gridded texts where texts are embedded as features with semantical connotations.
-We further explore the effect of employing different structures of convolutional neural network and propose a faster and portable structure.
-We demonstrate the effectiveness of the proposed method on a dataset with up to $5000$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is higher than BERT but with only 1/10 parameters and much higher than the other RNN based methods.
+We further explore the effect of employing different structures of convolutional neural network and propose a fast and portable structure.
+We demonstrate the effectiveness of the proposed method on a dataset with up to $6,980$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than BERT but with only $1/9$ parameters and without requiring the $3,300$M word dataset for pre-training.
 \end{abstract}
@@
 In this work, we focus on the second task that is rare in published research.
-In fact, key information extraction faces big chanllenges, where different types of document structures and vast number of potential interested key words introduces great difficulties.
+In fact, key information extraction faces big challenges, where different types of document structures and vast number of potential interested key words introduces great difficulties.
 Although the commonly used rule-based method can be implemented with carefully designed expert rules, it can only work on specific type of documents and takes no lesser effort to adapt to new type of documents.
-Therefore, it is desirable to have a learning based key information extraction method with limited requirement of human resources and solely employing the deep learning technique without designing expert rules for any specific type of documents.
+Therefore, it is desirable to have a learning-based key information extraction method with limited requirement of human resources and solely employing the deep learning technique without designing expert rules for any specific type of documents.
 
-History about published learning based methods goes here.
-The majority of the published learning based works are based on the Named Entity Recognition (NER) research in the NLP field that is not originally designed to solve the key information extraction problem in SROIE, which align text words in the original document as a long paragraph in line-based rule.
-However, the real world documents, such as receipts and invoices, present with various styles of layouts that were designed for different scenarios or from different enterprise entities.
+History about published learning-based methods goes here.
+The majority of the published learning-based works are based on the Named Entity Recognition (NER) research in the NLP field that is not originally designed to solve the key information extraction problem in SROIE, which align text words in the original document as a long paragraph in line-based rule.
+However, the real-world documents, such as receipts and invoices, present with various styles of layouts that were designed for different scenarios or from different enterprise entities.
 The order or word-to-word distance of the texts in the line-based aligned long paragraph tend to vary greatly due to layout variations, which is difficult to be handled with the natural language paragraph oriented methods, one typical example is illustrated in Fig.
@@
 \end{center}
-   \caption{Framework of the proposed method, (a) positional map the scanned document image to a grid with text's relative spatial relationship preserved, (b) feed the generated grid into the CNN for extracting key information, (c) reverse map the extracted key information for visual reference.}
+   \caption{Framework of the proposed method, (a) positional map the scanned document image to a grid with text's relative spatial relation preserved, (b) feed the generated grid into the CNN for extracting key information, (c) reverse map the extracted key information for visual reference.}
 \label{fig:cutie}
@@
 The rich semantic information is encoded from the gridded texts at the very beginning stage of the convolutional neural network with a word embedding layer.
-The CUTIE allows for simutaneously looking into both semantical information and spatial information of the texts in the scanned document image and can reach a new state of the art result for key information extraction, which outperforms BERT model but without demanding pretrain on a huge text dataset \cite{bert,transformer}.
+The CUTIE allows for simultaneously looking into both semantical information and spatial information of the texts in the scanned document image and can reach a new state of the art result for key information extraction, which outperforms BERT model but without demand pretraining on a huge text dataset \cite{bert,transformer}.
 
@@
 The later networks shrink feature maps to enlarge receptive fields and reduce computation burdens, and then capture finer details by gradually recovering the spatial information from lower layer features.
-However, spatial resolution is reduced in the encoding process and the decoding process exploits only high resolution but low level features to recover the spatial resolution, the consecutive striding encoding process decimates detail information \cite{hrnet}.
+However, spatial resolution is reduced in the encoding process and the decoding process exploits only high resolution but low-level features to recover the spatial resolution, the consecutive striding encoding process decimates detail information \cite{hrnet}.
 Moreover, the encoding and decoding process applies shape restricts to the grid shape augment process as introduced in Section \ref{pm}.
@@
 To capture long distance connection and avoid potential information loss in the encoding process, we propose two different network architectures and compare their performance in Section \ref{experiment}.
+We had experimented with various types of model structures and only detail two of them here to avoid being a tedious paper.
 Specifically, proposed CUTIE-A is a high capacity convolutional neural network that fuses multi-resolution features without losing high-resolution features, proposed CUTIE-B is a convolutional network with atrous convolution for enlarging field of view and Atrous Spatial Pyramid Pooling (ASPP) module to capture multi-scale contexts.
@@
 \end{equation}
-where $r$ is the atrous rate that indicates the sampling stride of the input signal, which is implemented as convolving the input feature with upsampled filters by inserting $r-1$ zeros between two consecutive filter values along each spatial dimension.
+where $r$ is the atrous rate that indicates the sampling stride of the input signal, which is implemented as convolving the input feature with up sampled filters by inserting $r-1$ zeros between two consecutive filter values along each spatial dimension.
 Standard convolution is a special case of atrous convolution with $r=1$ \cite{deeplabv1}.
@@
 For each specific key information class, multiple tokens can be included.
-The overall performance is refered as strict average precision (AP) and measured in terms of per-class accuracy across the $9$ classes, where one class is determined as correct only when every single token in the class is correct.
+The overall performance is referred as strict average precision (AP) and measured in terms of per-class accuracy across the $9$ classes, where one class is determined as correct only when every single token in the class is correct.
 To achieve deeper analysis of the performance of the proposed method, we propose to use one more criteria, soft average precision (softAP), where the prediction of a key information class is determined as correct as if positive ground truths are correctly predicted even if some false positive are included in the final prediction.
 SoftAP is important since it indicates model's capability of extracting correct key information with tolerance of incorporating certain false positives.
-In fact, post processings can be employed there to eliminate the false positives.
+In fact, post processing can be employed to eliminate the false positives.
 Therefore, joint analysis of AP and softAP provides a better understanding of the model performance.
@@
 We compare the performance of the proposed method with two state of the art methods CloudScan \cite{cloudscan} and BERT \cite{bert}.
-For comparison, the Cloud Scan model for SROIE is trained from scratch but with several expert designed features as describded in \cite{cloudscan}.
-The BERT model for SROIE is transform learned with the Google released base model that is pre-trained on a huge dataset with $3,300M$ words \cite{bert,bertgit}.
+For comparison, the Cloud Scan model for SROIE is trained from scratch but with several expert designed features as described in \cite{cloudscan}.
+The BERT model for SROIE is transform learned with the Google released base model that is pre-trained on a huge dataset with $3,300$M words \cite{bert,bertgit}.
 
 We use a learning rate of $1e-3$ with Adam optimizer and step decay learning strategy.
-The learning rate is dropped to $1e-4$ and $1e-5$ on the $15000$-th and $30000$-th steps, respectively.
-The training is terminated within $40000$ steps with batch size of $32$.
+The learning rate is dropped to $1e-4$ and $1e-5$ on the $15,000$-th and $30,000$-th steps, respectively.
+The training is terminated within $40,000$ steps with batch size of $32$.
+Instance normalization is involved to facilate training.
 Our model is trained end-to-end without piecewise pretraining of any component.
 The embedding size is $128$, target augmentation shape is $64$ for both row and column.
-The dataset is split as training set and test set with ratio of $7:3$.
+The dataset is split as training set and test set with ratio of $75:25$.
 
 \subsection{Dataset}
-The dataset contains $4000$ annotated scanned spanish receipt documents, including taxi receipts and meal entertainment (ME) receipts, with $9$ different key information classes, as reported in Table \ref{tab:dataset}.
-We generate the texts and bounding boxes with Google's OCR API.
-Each text and their bounding box is manually labelled as one of the 9 different classes: 'DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', and 'TaxRate'.
+The dataset contains $6,980$ annotated scanned Spanish receipt documents, including taxi receipts, meals entertainment (ME) receipts, and hotel receipts, with $9$ different key information classes, as reported in Table \ref{tab:dataset}.
+We generate the texts and corresponding bounding boxes with Google's OCR API.
+Each text and their bounding box is manually labelled as one of the $9$ different classes: 'DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', and 'TaxRate'.
 We then employ the tokenizer introduced in Section \ref{pm} to segment texts into minimum token units, where text bounding boxes are also segmented accordingly.
 
-In fact, the dataset is much difficult than the neat scanned document images, since various layouts of receipts were captured in different scenarios using ordinary mobile phone camera.
-Examples of the scanned document images in our dataset are illustrated in Figure \ref{fig:receipts}, note that the colored rectangles is only for visual reference, the actual labelled data is in token-level rather than the line-level that is shown in the figure.
+The dataset in this work is much more difficult than the neat scanned document images, since various layouts of receipts were captured in different scenarios using ordinary mobile phone camera.
+Examples of the scanned document images in our dataset are illustrated in Figure \ref{fig:receipts}, note that the colored rectangles is only for visual reference and the actual labelled data is in token-level rather than the line-level that is shown in the figure.
 \begin{table}
-	\caption{Number of labelled receipt document images and key information classes of different types of documents in the labelled dataset.}
+	\caption{Statistic of the numbers of labelled receipt document images and key information classes in the dataset.}
 \begin{center}
@@
 	Taxi & 2514 & 1077 & 6 \\
+	Hotel & 1353 & 452 & 9 \\
 \end{tabular}
@@
 \end{table}
+\begin{table*}
+	\caption{Performance comparison on different types of documents. (AP / softAP)}
+\begin{center}
+\begin{tabular}{l | c | c | c | c}
+	Method & \#Params & Taxi & ME & Hotel \\
+	\hline
+	CloudScan\cite{cloudscan} & - & 82 / - & 64 / - & 60 / - \\
+	BERT\cite{bert} & 110M & 87.0 / - & 80.3 / - & \textbf{79.4} / - \\
+	CUTIE-A & 67M & / & \textbf{84.8} / \textbf{93.5} & / \\
+	CUTIE-B & \textbf{14M} & \textbf{92.8} / \textbf{98.0} & 84.3 / 91.5 & 70.8 / \textbf{83.8} \\
+\end{tabular}
+\end{center}
+	\label{tab:comparison}
+\end{table*}
 
 \subsection{Results on Validation Set}
-We report results of our method and compare with other state of the art methods in Table \ref{tab:comparison}.
-Our big network CUTIE-A achieves $100$ score on meals entertainment receipt and $100$ score on taxi receipt, outperforming other methods.
-Compared to CloudScan, our big network CUTIE-A improves AP by $100$ on meals entertainment receipt and $100$ on taxi receipt, our small network CUTIE-B improves AP by $100$ points on meals entertainment receipt and $100$ on taxi receipt.
-Compared to BERT, where model is pre-trained on a dataset with $3,300M$ words and transfer learned on our dataset, our big network CUTIE-B improves AP by $100~100$ while using only $1/2$ parameters, our small network CUTIE-B improves AP by $100~100$ but with much less complexity and smaller model size with only $1/10$ parameters.
+We report results of our method in terms of AP and compare with other state of the art methods in Table \ref{tab:comparison}.
+We also provides softAP results for CUTIE-A and CUTIE-B in Table \ref{tab:comparison}, where both the softAP of CUTIE-A and CUTIE-B exceeds their AP by a large margin.
 Examples of inference results are illustrated in Figure \ref{fig:result}.
+Our big network CUTIE-A achieves $100\%$ AP and $100\%$ softAP on meals entertainment receipts, $100\%$ AP and $100\%$ softAP on taxi receipts, and $100\%$ AP and $100\%$ softAP on hotel receipts, outperforming other methods in almost all of the test cases.
+Compared to CloudScan, our big network CUTIE-A improves AP by $100\%$ on meals entertainment receipts, $100\%$ on taxi receipt, and $100\%$ on hotel receipts; our small network CUTIE-B improves AP by $100\%$ points on meals entertainment receipts, $100$ on taxi receipts, and $100\%$ on hotel receipts.
+Furthermore, compared to BERT, where model is pre-trained on a dataset with $3,300M$ words and transfer learned on our dataset, our big network CUTIE-B improves AP by $100\%~100\%$ in meals entertainment and taxi receipts while using only $1/2$ parameters, our small network CUTIE-B improves AP by $100\%~100\%$ in meals entertainment and taxi receipts but with much less complexity and smaller model size with only $1/9$ parameters without requiring a huge dataset for model pretraining.
+
+It is worth noting that the difference of AP in the hotel receipt column actually leads to interesting findings.
+One of the finding is that if we neglect the 'VendorName' class in the evaluation criteria, the AP is increased to from $70.8\%$ to $76.9\%$ and the softAP drops to $83.8\%$, indicating that CUTIE is capable of extracting the interested 'VendorName' texts but sometimes involves texts that are not in the ground truth label.
+Another finding is that the hotel receipts are quite different from the meals entertainment receipts and the taxi receipts, where key information appear multi times in different areas of the receipt, whereas the human labelers tend to label only one of their appearances.
+We look deeper into this in the following part of this section by analyzing some error cases.
 \begin{figure*}
 \begin{center}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_0.png}} 
+\subfloat{\includegraphics[width=0.17\linewidth]{appendix/meals/Correct_0.png}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.4\linewidth]{appendix/Correct_1.png}}
+\subfloat{\includegraphics[width=0.39\linewidth]{appendix/meals/Correct_1.png}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_2.png}}
+\subfloat{\includegraphics[width=0.17\linewidth]{appendix/meals/Correct_2.png}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_3.png}} \\ 
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_4.png}}  
+\subfloat{\includegraphics[width=0.17\linewidth]{appendix/meals/Correct_3.png}} \\ 
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_4.png}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_5.png}}  
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_5.png}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_9.png}}  
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_9.png}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_7.png}}  
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_7.png}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/Correct_8.png}} 
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_8.png}} \\
+\subfloat{\includegraphics[width=0.35\linewidth]{appendix/hotel/Correct_0.png}}  
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.19\linewidth]{appendix/hotel/Correct_1.png}}  
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.21\linewidth]{appendix/hotel/Correct_2.png}}  
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.21\linewidth]{appendix/hotel/Correct_3.png}}  
 \end{center}
-   \caption{Example of inference results of CUITE.
+   \caption{Example of CUITE inference results.
 Color legend in the top-left corner indicates the key information classes.
@@
 
-We also provides softAP results for CUTIE-A and CUTIE-B in Table \ref{tab:comparison}, where both the softAP of CUTIE-A and CUTIE-B exceeds AP by a large margin.
-Typical examples of receipts with low AP but high softAP score is shown in Figure \ref{fig:falsepositive}.
-Most of the false positive cases occor in the 'VenderName' class, where names tend to greatly vary and leads to difficulty in model inference.
-It is not hard to find that, however, these false positives can be easily avoided by appending a dictionary based post processor to the key information extractor.
-One rare false posive case in the $4$-th image is a 'L' letter being mis-recognized as '1' by the employed OCR engine.
-Although the letter shows distinct appearance with the other digits, it is mis-interpreted as one part of the 'BaseAmount' class due to its close spatial location to the digits and it-self being a digit.
-Although this is one and only special case in our test set, it still suggests that incorporating image-level information may further boost the inference accuracy inspite of the already involved semantical and spatial features.
-\begin{table}
-	\caption{Performance comparison on 3 types of documents. (AP/softAP)}
-\begin{center}
-\begin{tabular}{l | c | c | c | c}
-	Method & \#Params & ME & Taxi & Hotel \\
-	\hline
-	CloudScan & - & 82 / - & 64 / - & \\
-	BERT & 110M & 80.3 / - & 87.0 / - & 79.4 / - \\
-	CUTIE-A & 67M & 82.5 / & / & / \\
-	CUTIE-B & 14M & / & / \\
-\end{tabular}
-\end{center}
-	\label{tab:comparison}
-\end{table}
+Typical examples of receipts with low AP but high softAP score are shown in Figure \ref{fig:falsepositive}.
+Most of the false positive cases occur in the 'VenderName' class, where names tend to greatly vary and leads to difficulty in model inference.
+However, it is not hard to find that these false positives can be easily avoided by appending a dictionary based post processor to the key information extractor.
+One rare false positive case, the third receipt in the first row, is a 'L' letter being mis-recognized as '1' by the employed OCR engine.
+Although the letter shows distinct appearance from the other digits in the scanned receipt image, it is mis-interpreted as one part of the 'BaseAmount' class due to its close spatial location to the digits and it-self being a digit.
+It is also can be seen in the first receipt in the second row that several spatial distant digits were wrongly predicted as in the 'BaseAmount' class.
+Although these are rare cases in our test set, it still suggests that incorporating image-level information may further boost the inference accuracy inspite of the already involved semantical and spatial features.
 
@@
 \begin{center}
-\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalsePositive_0.png}} 
+\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalsePositive_0.png}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalsePositive_1.png}}\\
-\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalsePositive_2.png}}
+\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalsePositive_1.png}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalsePositive_3.png}}
+\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalsePositive_3.png}}\\
+\subfloat{\includegraphics[width=0.29\linewidth]{appendix/hotel/FalsePositive_0.png}}
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.35\linewidth]{appendix/taxi/FalsePositive_0.png}}
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.29\linewidth]{appendix/hotel/FalsePositive_1.png}}
+\subfloat{\fcolorbox{white}{white}{}}
 \end{center}
-   \caption{Example of prediction results of CUITE with false positive inference results.
+   \caption{False positive examples of CUITE prediction results.
 Color legend in the top-left corner indicates the key information classes.
 Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
-The false positive are results with the boundary-only rectangles not overlap with the filled rectangles.}
+The false positives are results with the boundary-only rectangles being not overlapped with the filled rectangles.}
 \label{fig:falsepositive}
@@
 
-Furthermore, we find that some cases are determained as not right while the ground truth were wrongly labelled by the human labeller.
-As illustrated in Figure \ref{fig:falselabel}, the 'VendorName' appears twice in the scanned image but only being labelled once while the model correctly interprets both occurance as the 'VendorName'.
+Furthermore, we find that some wrong cases are actually correct since the ground truth were wrongly labelled by the human labelers.
+As illustrated in Figure \ref{fig:falselabel}, the 'VendorName' appears twice in the scanned image but only being labelled once in both the first and second receipt in the first row, while the model correctly interprets both occurance as the 'VendorName' in the first receipt and correctly interprets the second occurance in the second receipt.
+Furthermore, 'TaxRate' is neglected to be labeled in the third receipt in the first row and 'VendorName' is wrongly labelled in the first receipt in the second row.
+The third receipt in the second row and the first and second receipt in the third row are all neglected with labelling 'TaxRate', and the third receipt in the third row is neglected with labelling 'BaseAmount' while the trained model correctly inferred the right class.
+It is not hard to find that the trained model produces even better results than human labeler on these receipts, which further proves the effectiveness of the proposed method.
 \begin{figure}
 \begin{center}
-\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalseLabel_0.png}} 
+\subfloat{\includegraphics[width=0.28\linewidth]{appendix/meals/FalseLabel_0.png}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.35\linewidth]{appendix/FalseLabel_1.png}}\\
-\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalseLabel_2.png}}
+\subfloat{\includegraphics[width=0.34\linewidth]{appendix/meals/FalseLabel_1.png}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.4\linewidth]{appendix/FalseLabel_3.png}}
+\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalseLabel_2.png}}\\
+\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalseLabel_3.png}} 
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.31\linewidth]{appendix/hotel/FalseLabel_0.png}}
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.31\linewidth]{appendix/taxi/FalseLabel_4.png}}\\
+\subfloat{\includegraphics[width=0.36\linewidth]{appendix/taxi/FalseLabel_0.png}} 
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.22\linewidth]{appendix/taxi/FalseLabel_5.png}}
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.36\linewidth]{appendix/hotel/FalseLabel_1.png}}\\
 \end{center}
-   \caption{Example of prediction results of CUITE with false positive inference results.
+   \caption{False positive examples of CUITE prediction results, where the error is actually caused by the wrong labelling of human labeler.
 Color legend in the top-left corner indicates the key information classes.
@@
 Results are presented in Table \ref{tab:augmentation}.
-We can see that adding grid augment process in CUTIE can significantly improve the performance on meal entertainment receipt and taxi receipt.
+We can see that adding grid augment process in CUTIE can significantly improve the performance on all of these receipts.
 These results demonstrate that CUTIE can greatly benefit from enhancing data diversity in spatial distribution.
@@
 \begin{table}
-	\caption{Performance evaluation of CUTIE with or without the grid augmentation process. (AP/softAP)}
+	\caption{Performance evaluation of CUTIE with or without the grid augmentation process. (AP / softAP)}
 \begin{center}
 \begin{tabular}{l | c | c | c}
-	 & MEnter & Taxi & Hotel \\
+	 & Taxi & ME & Hotel \\
 	\hline
@@
 As reported in Table \ref{tab:embedding}, CUTIE performs worse with smaller embedding size.
-The result meets our expection that $details$.
-To further enhance the model performance, it might help to randomly mask out certain texts during the grid positional mapping process, such that the model learns inter-text relationship better with / without all words present in the grid and improves in generality.
+The result meets our expectation that $details$.
+To further enhance the model performance, it might help to randomly mask out certain texts during the grid positional mapping process, such that the model learns inter-text relationship better with / without certain words present in the grid and further improves in generality.
 \begin{table}
-	\caption{Performance evaluation of CUTIE with different embedding size. (AP/softAP)}
+	\caption{Performance evaluation of CUTIE with different embedding size. (AP / softAP)}
 \begin{center}
 \begin{tabular}{l | c | c | c}
-	 & 64 & 128 & 256 \\
+	 & Taxi & ME & Hotel \\
 	\hline
-	 & / & / & \\
-	 & / & / & \\
+	64 & / & / & \\
+	128 & / & / & \\
+	256 & / & / & \\
 \end{tabular}
@@
 
+\subsubsection{Impact of Number of Training Samples}
+To evaluate the impact of different number of training samples on model performance, we train CUTIE with $30\%$, $39\%$, $48\%$, $57\%$, $66\%$, and $75\%$ of our dataset, and report the results in Table \ref{tab:samples}.
+\begin{table}
+	\caption{Performance evaluation of CUTIE with different number of training samples. (AP / softAP)}
+\begin{center}
+\begin{tabular}{l | c | c | c}
+	 & Taxi & ME & Hotel \\
+	\hline
+	30\% & / & / & \\
+	39\% & / & / & \\
+	48\% & / & / & \\
+	57\% & / & / & \\
+	66\% & / & / & \\
+	75\% & 84.3 / 91.5 & \textbf{92.8} / \textbf{98.0} & 70.8 / \textbf{83.8} \\
+\end{tabular}
+\end{center}
+	\label{tab:samples}
+\end{table}
+
 \section{Discussion}
 Automatically extracting interested words / information from the scanned document images is of great interest to various services and applications.
+This paper proposes CUTIE to tackle this problem without requirement of any pre-training of post processing.
+Experimental results verifies the effectiveness of the proposed method.
+In contrast to the previous methods, the proposed method is easy to train and requires much smaller amount of training data while achieving state of the art performance.
 The performance gain is mainly achieved by exploring three key factors: the spatial relationship among texts, the semantic information of texts, and the grid positional mapping mechanism.
+One interesting finding is that the trained CUTIE model correctly predicts certain key information that is neglected to be labelled by the human labeler, which further proves the effectiveness of the proposed method.
+It is also worth mention that incorporating better semantical feature processing module or involving image-level features may further boost the model performance and we leave it to future research.
 
@@
 \section{APPENDIX}
+\subsection{Model Structure}
+We report the best performed CUTIE-B model in Table \ref{tab:cutie}.
+Tokens are firstly embedd into $128$ dimensional features.
+Then, $4$ consecutive convolution operations are conducted in the conv block and $4$ consecutive atrous convolution are conducted in the atrous conv block with stride $1$ and rate $2$.
+Following the atrous conv block, an ASPP module is employed to combine multi-resolution features.
+The low level but high resolution feature from the $1$st output of the convolution block is also added to the model in the shortcut layer with a concatenation operation and a $1\times1$ convolution.
+Finally, inference result is achieved through a $1\times1$ convolution.
+\begin{table}
+	\caption{Structure of the proposed CUTIE-B model. }
+\begin{center}
+\begin{tabular}{l | c | c | c | c}
+	layer name & operations & input dimension & output diemnsion & comments \\
+	\hline
+	embedding layer & - & 20000 & 128 & \\
+	conv block & [$3\times5$]$\times$4 & 256 & 256 & stride=1 \\
+	atrous conv block & [$3\times5$]$\times$4 & 256 & 256 & stride=1, rate=2 \\
+	ASPP module & [$3\times5$]$\times$3, global pooling, concat, $1\times1$ & 256 & 256 & stride=1, rate=\{4,8,16\} \\
+	shorcut layer & concat, $1\times1$ & 256 & 64 & \\
+	output layer & $1\times1$ & 64 & 9 & \\ 
+\end{tabular}
+\end{center}
+	\label{tab:cutie}
+\end{table}
 

### 2019-03-22 deprecated/data_loader.py

@@ -1,324 +1,0 @@
-# -*- coding: utf-8 -*-
-# 2019-01 
-# written by Xiaohui Zhao
-# xiaohui.zhao@accenture.com
-from os import walk
-from os.path import isfile, join
-import csv, re, random
-
-import numpy as np
-import tensorflow as tf
-
-DEBUG = False
-
-import unicodedata
-def is_number(s):
-    try:
-        float(s)
-        return True
-    except ValueError:
-        pass
- 
-    try:
-        unicodedata.numeric(s)
-        return True
-    except (TypeError, ValueError):
-        pass 
-    return False
-
-class DataLoader():
-    """
-    training_grid_tables
-    """
-    def __init__(self, params):
-        ## 0> parameters to be tuned
-        self.dictionary = {'<dontcare>':0, '<unknown>':1, '<name>':2} # to be updated in self.load_data()
-        self.classes = ['DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount']
-        self.combinekv = True # False to consider key and value as two different class, otherwise the same class
-        self.num_classes = len(self.classes) 
-        
-        self.rows = 32 # to be updated in self._update_training_rows_cols()
-        self.cols = 32 # to be updated in self._update_training_rows_cols()
-        self.encoding_factor = 8 # ensures the size (rows/cols) of grid table compat with the network
-        
-        self.batch_size = params.batch_size        
-        
-        # TBD: build a special cared dictionary
-        self.special_dict = {'some_word': '<dontcare>'} # map texts to specific tokens        
-        
-        ## 1> load words and their location/class as docs and labels 
-        self.training_doc_files = self._get_filenames(params.training_doc_path)
-        self.training_label_files = self._get_filenames(params.training_label_path)
-        self.training_docs, self.training_labels = self.load_data(self.training_doc_files, self.training_label_files, True)  
-        
-        self.validation_doc_files = self._get_filenames(params.validation_doc_path)
-        self.validation_label_files = self._get_filenames(params.validation_label_path)
-        self.validation_docs, self.validation_labels = self.load_data(self.validation_doc_files, self.validation_label_files)  
-        
-        self.num_words = len(self.dictionary) # TBD: check correctness of dictionary
-        sorted(self.dictionary.items(), key=lambda x:x[1], reverse=True)
-        self.word_to_index = dict(list(zip(self.dictionary.keys(), list(range(self.num_words))))) 
[…]

### 2019-03-22 deprecated/main_train.py

@@ -1,222 +1,0 @@
-# written by Xiaohui Zhao
-# 2018-12 
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-import numpy as np
-import argparse
-import os
-os.environ["CUDA_VISIBLE_DEVICES"] = "1"
-
-from model_cutie import CUTIE
-from model_cutie_res import CUTIERes
-from model_cutie_sep import CUTIESep
-from data_loader import DataLoader
-
-parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--training_doc_path', type=str, default='data/training_data') 
-parser.add_argument('--training_label_path', type=str, default='data/label') 
-parser.add_argument('--validation_doc_path', type=str, default='data/validation_data') 
-parser.add_argument('--validation_label_path', type=str, default='data/label') 
-
-parser.add_argument('--restore_ckpt', type=bool, default=False) 
-parser.add_argument('--ckpt_path', type=str, default='../graph/CUTIE/graph/')
-parser.add_argument('--ckpt_file', type=str, default='CUTIE_residual_iter_9000.ckpt')  
-parser.add_argument('--ckpt_save_prefix', type=str, default='CUTIE') # TBD: save log/models with prefix
-
-parser.add_argument('--log_path', type=str, default='../graph/CUTIE/log/') 
-parser.add_argument('--log_disp_step', type=int, default=50) 
-parser.add_argument('--log_save_step', type=int, default=10) 
-parser.add_argument('--validation_step', type=int, default=50) 
-parser.add_argument('--ckpt_save_step', type=int, default=1000)
-
-parser.add_argument('--hard_negative_ratio', type=int, help='the ratio between negative and positive losses', default=3) 
-parser.add_argument('--embedding_size', type=int, default=120) 
-
-parser.add_argument('--batch_size', type=int, default=32) 
-parser.add_argument('--iterations', type=int, default=10000)  
-parser.add_argument('--lr_decay_step', type=int, default=2000) 
-parser.add_argument('--lr_decay_factor', type=float, default=0.5) 
-parser.add_argument('--learning_rate', type=float, default=0.001)
-parser.add_argument('--weight_decay', type=float, default=0.0005) 
-parser.add_argument('--eps', type=float, default=1e-14) 
-
-parser.add_argument('--c_threshold', type=float, default=0.5) 
-params = parser.parse_args()
-
[…]

### 2019-03-22 main_evaluate_json.py

@@ -8,18 +8,18 @@ import argparse
 import os, csv
 os.environ["CUDA_VISIBLE_DEVICES"] = "1"
 
-from model_cutie_hr import CUTIERes
+from model_cutie_aspp import CUTIERes
 from data_loader_json import DataLoader
 from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--doc_path', type=str, default='data/meals_1108/') # modify this
-parser.add_argument('--save_prefix', type=str, default='meals', help='prefix for ckpt and results') # modify this
+parser.add_argument('--doc_path', type=str, default='data/hotel/') # modify this
+parser.add_argument('--save_prefix', type=str, default='hotel', help='prefix for load ckpt model') # modify this
 
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 
 parser.add_argument('--e_ckpt_path', type=str, default='../graph/CUTIE/graph/') # modify this
-parser.add_argument('--ckpt_file', type=str, default='CUTIE_highresolution_8x_d20000c9(r80c80)_iter_40000.ckpt')
+parser.add_argument('--ckpt_file', type=str, default='CUTIE_atrousSPP_d20000c9(r80c80)_iter_40000.ckpt')
 parser.add_argument('--positional_mapping_strategy', type=int, default=1)
 parser.add_argument('--rows_target', type=int, default=72) 
 parser.add_argument('--cols_target', type=int, default=72) 
@@ -42,7 +42,7 @@ params = parser.parse_args()
 if __name__ == '__main__':
     # data
     #data_loader = DataLoader(params, True, True) # True to use 25% training data
-    data_loader = DataLoader(params, update_dict=False, load_dictionary=True, data_split=0) # False to provide a path with only test data
+    data_loader = DataLoader(params, update_dict=False, load_dictionary=True, data_split=0.75) # False to provide a path with only test data
     num_words = max(20000, data_loader.num_words)
     num_classes = data_loader.num_classes
 

### 2019-03-22 main_train_json.py

@@ -14,16 +14,16 @@ from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
 # data
-parser.add_argument('--doc_path', type=str, default='data/hotel_1108')
-parser.add_argument('--save_prefix', type=str, default='hotel_1108', help='prefix for ckpt') # TBD: save log/models with prefix
+parser.add_argument('--doc_path', type=str, default='data/taxi')
+parser.add_argument('--save_prefix', type=str, default='taxi', help='prefix for ckpt') # TBD: save log/models with prefix
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
 # ckpt
 parser.add_argument('--restore_ckpt', type=bool, default=False) 
-parser.add_argument('--restore_bertembedding_only', type=bool, default=True) # effective when restore_ckpt is True
+parser.add_argument('--restore_bertembedding_only', type=bool, default=False) # effective when restore_ckpt is True
 parser.add_argument('--embedding_file', type=str, default='../graph/bert/multi_cased_L-12_H-768_A-12/bert_model.ckpt') 
 parser.add_argument('--ckpt_path', type=str, default='../graph/CUTIE/graph/')
-parser.add_argument('--ckpt_file', type=str, default='*.ckpt')  
+parser.add_argument('--ckpt_file', type=str, default='meals/CUTIE_highresolution_8x_d20000c9(r80c80)_iter_40000.ckpt')  
 
 # dict
 parser.add_argument('--load_dict', type=bool, default=True, help='True to work based on an existing dict') 
@@ -72,7 +72,7 @@ parser.add_argument('--test_step', type=int, default=400)
 parser.add_argument('--ckpt_save_step', type=int, default=1000)
 
 # model
-parser.add_argument('--embedding_size', type=int, default=128) # not used for bert embedding which has 768 as default
+parser.add_argument('--embedding_size', type=int, default=64) # not used for bert embedding which has 768 as default
 parser.add_argument('--weight_decay', type=float, default=0.0005) 
 parser.add_argument('--eps', type=float, default=1e-6) 
 
@@ -205,7 +205,7 @@ if __name__ == '__main__':
                     ckpt_saver.restore(sess, ckpt_path)
                     print('Restored from {}'.format(ckpt_path))
                     stem = os.path.splitext(os.path.basename(ckpt_path))[0]
-                    iter_start = int(stem.split('_')[-1]) - 1
[…]

### 2019-03-22 model_cutie_aspp.py

@@ -46,6 +46,8 @@ class CUTIERes(CUTIE):
         
         # Atrous Spatial Pyramid Pooling module
         (self.feed('encoder1_8')
+             .conv(1, 1, 256, 1, 1, name='aspp_0'))
+        (self.feed('encoder1_8')
              .dilate_conv(3, 5, 256, 1, 1, 4, name='aspp_1'))
         (self.feed('encoder1_8')
              .dilate_conv(3, 5, 256, 1, 1, 8, name='aspp_2'))
@@ -53,7 +55,7 @@ class CUTIERes(CUTIE):
              .dilate_conv(3, 5, 256, 1, 1, 16, name='aspp_3'))
         (self.feed('encoder1_8')
              .global_pool(name='aspp_4'))
-        (self.feed('aspp_1', 'aspp_2', 'aspp_3', 'aspp_4')
+        (self.feed('aspp_0', 'aspp_1', 'aspp_2', 'aspp_3', 'aspp_4')
              .concat(3, name='aspp_concat')
              .conv(1, 1, 256, 1, 1, name='aspp_1x1'))
         

### 2019-03-22 utils.py

@@ -35,6 +35,7 @@ def cal_accuracy(data_loader, grid_table, gt_classes, model_output_val, label_ma
         bbox_id_selected = bbox_id[indexes]
         
         # calculate accuracy
+        #test_classes = [1,2,3,4,5,6,7,8,9]
         for c in range(1, data_loader.num_classes):
             labels_indexes = np.where(labels_selected == c)[0]
             logits_indexes = np.where(logits_array_selected[:,c] > c_threshold)[0]

### 2019-03-27 Article/ms.tex
article almost final version

@@
   New IT Accenture \\
-{\tt\small xiaohui.zhao@accenture.com zhuo.wu@accenture.com danny.x.wang@accenture.com}
+{\tt\small xh.zhao@outlook.com zhuo.wu@accenture.com danny.x.wang@accenture.com}
 % Additional authors and addresses can be added with ``\and'',
@@
 We further explore the effect of employing different structures of convolutional neural network and propose a fast and portable structure.
-We demonstrate the effectiveness of the proposed method on a dataset with up to $6,980$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than BERT but with only $1/9$ parameters and without requiring the $3,300$M word dataset for pre-training.
+We demonstrate the effectiveness of the proposed method on a dataset with up to $6,980$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than BERT but with only $1/10$ parameters and without requiring the $3,300$M word dataset for pre-training.
+Experimental results also demonstrate that the CUTIE being able to achieve state of the art performance with much smaller amount of training data.
 \end{abstract}
@@
 
-History about published learning-based methods goes here.
-The majority of the published learning-based works are based on the Named Entity Recognition (NER) research in the NLP field that is not originally designed to solve the key information extraction problem in SROIE, which align text words in the original document as a long paragraph in line-based rule.
+\cite{cloudscan} proposed a learning based invoice analysis system named CloudScan, aiming to not rely on invoice layout templates, CloudScan trains a model that could be generalized to unseen invoice layouts, where a model is trained either using Long Short Term Memory (LSTM) or Logistic Regression (LR) with expert designed rules.
+This turns out to be extremely similar with a Named Entity Recognition (NER) model or a slot filling model.
+The Bi-directional Encoder Representations from Transformers (BERT) model proposed in \cite{bert} is a recently proposed state of the art method and has achieved great success in a wide of range of NLP tasks including NER.
+However, the methods based on the Named Entity Recognition (NER) research in the NLP field that is not originally designed to solve the key information extraction problem in SROIE, which align text words in the original document as a long paragraph in line-based rule.
 However, the real-world documents, such as receipts and invoices, present with various styles of layouts that were designed for different scenarios or from different enterprise entities.
@@
 \ref{fig:cutie}.
-The gridded texts is formed with the proposed grid positional mapping method, where the grid is generated with the principle that is preserving text's relative spatial relationship in the original scanned document image.
+The gridded texts is formed with the proposed grid positional mapping method, where the grid is generated with the principle that is preserving texts’ relative spatial relationship in the original scanned document image.
 The rich semantic information is encoded from the gridded texts at the very beginning stage of the convolutional neural network with a word embedding layer.
@@
 \section{Related Work}
+Several rule-based invoice analysis systems were proposed in \cite{3,5,7}.
+Intellix by DocuWare requires the a template being annotated with relevant fields \cite{3}.
+For that reason, a collection of templates have to be constructed.
+SmartFix employs specifically designed configuration rules for each template \cite{5}.
+Esser et al.
+uses a dataset of fixed key information positions for each template \cite{7}.
+It is not hard to find that the rule-based methods rely heavily on the pre-defined template rules to extract information from specific invoice layouts.
+
+CloudScan is a work attempting to extracting key information with learning based models \cite{cloudscan}.
+Firstly, N-grams features are formed by connecting expert designed rules calculated results on texts of each document line.
+Then, the features are feed to train a RNN-based or a logistic regression based classifier for key information extraction.
+Certain post-processing are added to further enhance extraction results.
+However, the line-based feature extraction method can not achieve its best performance if document texts are not perfectly aligned in line.
+Moreover, the RNN-based classifier, bi-directional LSTM model in CloudScan, has limited ability to learn relationship among distant words.
+
+Bidirectional Encoder Representations from Transformers (BERT) is a recently proposed model that is pre-trained on a huge dataset and can be fine-tuned for a specific task, including Named Entity Recognition (NER), which outperforms most of the state of the art results in several NLP tasks \cite{bert}.
+Since the previous learning based methods treats the key information extraction problem as a NER problem, applying BERT can achieve better result than bi-LSTM in CloudScan.
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.99\linewidth]{Receipts.png}
+\end{center}
+   \caption{Example of scanned taxi receipt images.
+We provide two colored rectangles to help readers find the key information about distance of travel and total amount with blue and red, respectively.
+Note the different types of spatial layouts and key information texts in these receipt images.}
+\label{fig:receipts}
+\end{figure}
+
 \subsection{CUTIE Model}
@@
 
-\section{Experiments}
-\label{experiment}
-The proposed method is evaluated on a dataset with $3$ types of scanned document images, which contain $8$ key information classes and $1$ don't care class.
-For each specific key information class, multiple tokens can be included.
-The overall performance is referred as strict average precision (AP) and measured in terms of per-class accuracy across the $9$ classes, where one class is determined as correct only when every single token in the class is correct.
-To achieve deeper analysis of the performance of the proposed method, we propose to use one more criteria, soft average precision (softAP), where the prediction of a key information class is determined as correct as if positive ground truths are correctly predicted even if some false positive are included in the final prediction.
-SoftAP is important since it indicates model's capability of extracting correct key information with tolerance of incorporating certain false positives.
-In fact, post processing can be employed to eliminate the false positives.
-Therefore, joint analysis of AP and softAP provides a better understanding of the model performance.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.99\linewidth]{Receipts.png}
-\end{center}
-   \caption{Example of scanned taxi receipt images.
-We provide two colored rectangles to help readers find the key information about distance of travel and total amount with blue and red, respectively.
-Note the different types of spatial layouts and key information texts in these receipt images.}
-\label{fig:receipts}
-\end{figure}
-
-We compare the performance of the proposed method with two state of the art methods CloudScan \cite{cloudscan} and BERT \cite{bert}.
-For comparison, the Cloud Scan model for SROIE is trained from scratch but with several expert designed features as described in \cite{cloudscan}.
-The BERT model for SROIE is transform learned with the Google released base model that is pre-trained on a huge dataset with $3,300$M words \cite{bert,bertgit}.
-
-We use a learning rate of $1e-3$ with Adam optimizer and step decay learning strategy.
-The learning rate is dropped to $1e-4$ and $1e-5$ on the $15,000$-th and $30,000$-th steps, respectively.
-The training is terminated within $40,000$ steps with batch size of $32$.
-Instance normalization is involved to facilate training.
-Our model is trained end-to-end without piecewise pretraining of any component.
-The embedding size is $128$, target augmentation shape is $64$ for both row and column.
-The dataset is split as training set and test set with ratio of $75:25$.
-
-\subsection{Dataset}
-The dataset contains $6,980$ annotated scanned Spanish receipt documents, including taxi receipts, meals entertainment (ME) receipts, and hotel receipts, with $9$ different key information classes, as reported in Table \ref{tab:dataset}.
-We generate the texts and corresponding bounding boxes with Google's OCR API.
-Each text and their bounding box is manually labelled as one of the $9$ different classes: 'DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', and 'TaxRate'.
-We then employ the tokenizer introduced in Section \ref{pm} to segment texts into minimum token units, where text bounding boxes are also segmented accordingly.
-
-The dataset in this work is much more difficult than the neat scanned document images, since various layouts of receipts were captured in different scenarios using ordinary mobile phone camera.
-Examples of the scanned document images in our dataset are illustrated in Figure \ref{fig:receipts}, note that the colored rectangles is only for visual reference and the actual labelled data is in token-level rather than the line-level that is shown in the figure.
 \begin{table}
@@
 \end{table}
+
 \begin{table*}
-	\caption{Performance comparison on different types of documents. (AP / softAP)}
+	\caption{Performance comparison on different types of documents. Post-processing is abbreviated as pp.}
 \begin{center}
@@
 	CloudScan\cite{cloudscan} & - & 82 / - & 64 / - & 60 / - \\
-	BERT\cite{bert} & 110M & 87.0 / - & 80.3 / - & \textbf{79.4} / - \\
-	CUTIE-A & 67M & / & \textbf{84.8} / \textbf{93.5} & / \\
-	CUTIE-B & \textbf{14M} & \textbf{92.8} / \textbf{98.0} & 84.3 / 91.5 & 70.8 / \textbf{83.8} \\
+	BERT\cite{bert}+pp & 110M & 87.0 / - & 80.3 / - & \textbf{79.4} / - \\
+	CUTIE-A & 67M & 91.2 / 98.1 & \textbf{84.8} / \textbf{93.5} & 62.7 / 88.9 \\
+	CUTIE-B & \textbf{14M} & \textbf{95.2} / \textbf{97.6} & 84.3 / 92.4 & 70.8 / \textbf{89.4} \\
 \end{tabular}
@@
 
-\subsection{Results on Validation Set}
-We report results of our method in terms of AP and compare with other state of the art methods in Table \ref{tab:comparison}.
-We also provides softAP results for CUTIE-A and CUTIE-B in Table \ref{tab:comparison}, where both the softAP of CUTIE-A and CUTIE-B exceeds their AP by a large margin.
-Examples of inference results are illustrated in Figure \ref{fig:result}.
-Our big network CUTIE-A achieves $100\%$ AP and $100\%$ softAP on meals entertainment receipts, $100\%$ AP and $100\%$ softAP on taxi receipts, and $100\%$ AP and $100\%$ softAP on hotel receipts, outperforming other methods in almost all of the test cases.
-Compared to CloudScan, our big network CUTIE-A improves AP by $100\%$ on meals entertainment receipts, $100\%$ on taxi receipt, and $100\%$ on hotel receipts; our small network CUTIE-B improves AP by $100\%$ points on meals entertainment receipts, $100$ on taxi receipts, and $100\%$ on hotel receipts.
-Furthermore, compared to BERT, where model is pre-trained on a dataset with $3,300M$ words and transfer learned on our dataset, our big network CUTIE-B improves AP by $100\%~100\%$ in meals entertainment and taxi receipts while using only $1/2$ parameters, our small network CUTIE-B improves AP by $100\%~100\%$ in meals entertainment and taxi receipts but with much less complexity and smaller model size with only $1/9$ parameters without requiring a huge dataset for model pretraining.
+\section{Experiments}
+\label{experiment}
+The proposed method is evaluated on a dataset with $3$ types of scanned document images, which contain $8$ key information classes and $1$ don't care class.
+For each specific key information class, multiple tokens can be included.
+The overall performance is referred as strict average precision (AP) and measured in terms of per-class accuracy across the $9$ classes, where one class is determined as correct only when every single token in the class is correct.
+To achieve deeper analysis of the performance of the proposed method, we propose to use one more criteria, soft average precision (softAP), where the prediction of a key information class is determined as correct as if positive ground truths are correctly predicted even if some false positives are included in the final prediction.
+SoftAP is important since it indicates model's capability of extracting correct key information with tolerance of incorporating certain false positives.
+In fact, post processing can be employed to eliminate the false positives.
+Therefore, joint analysis of AP and softAP provides a better understanding of the model performance.
 
-It is worth noting that the difference of AP in the hotel receipt column actually leads to interesting findings.
-One of the finding is that if we neglect the 'VendorName' class in the evaluation criteria, the AP is increased to from $70.8\%$ to $76.9\%$ and the softAP drops to $83.8\%$, indicating that CUTIE is capable of extracting the interested 'VendorName' texts but sometimes involves texts that are not in the ground truth label.
-Another finding is that the hotel receipts are quite different from the meals entertainment receipts and the taxi receipts, where key information appear multi times in different areas of the receipt, whereas the human labelers tend to label only one of their appearances.
-We look deeper into this in the following part of this section by analyzing some error cases.
+We compare the performance of the proposed method with two state of the art methods CloudScan \cite{cloudscan} and BERT \cite{bert}.
+For comparison, the Cloud Scan model for SROIE is trained from scratch but with several expert designed features as described in \cite{cloudscan}.
+The BERT model for SROIE is transform learned with the Google released base model that is pre-trained on a huge dataset with $3,300$M words \cite{bert,bertgit}.
+Furthermore, post-processing is applied to the BERT results to eliminate certain errors and enhance accuracy.
+It is worth noting that the CloudScan based method and BERT based method were implemented by other teams.
+For that reason, there is minor difference in numbers of training / test data.
+To provide a fair comparison, we also provide ablation study to evaluate the influence of number of training images in CUTIE.
+We will also provide results generated using the same dataset in the next version of this paper.
+
+We use a learning rate of $1e-3$ with Adam optimizer and step decay learning strategy.
+The learning rate is dropped to $1e-4$ and $1e-5$ on the $15,000$-th and $30,000$-th steps, respectively.
+The training is terminated within $40,000$ steps with batch size of $32$.
+Instance normalization is involved to facilate training.
+Our model is trained end-to-end without piecewise pretraining of any component.
+The embedding size is $128$, target augmentation shape is $64$ for both row and column.
+The dataset is split as training set and test set with ratio of $75:25$.
+No pre-processing or post-processing are involved in CUTIE.
+
 \begin{figure*}
@@
 
+\subsection{Dataset}
+The dataset contains $6,980$ annotated scanned Spanish receipt documents, including taxi receipts, meals entertainment (ME) receipts, and hotel receipts, with $9$ different key information classes, as reported in Table \ref{tab:dataset}.
+We generate the texts and corresponding bounding boxes with Google's OCR API.
+Each text and their bounding box is manually labelled as one of the $9$ different classes: 'DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', and 'TaxRate'.
+We then employ the tokenizer introduced in Section \ref{pm} to segment texts into minimum token units, where text bounding boxes are also segmented accordingly.
+
+The dataset in this work is much more difficult than the neat scanned document images, since various layouts of receipts were captured in different scenarios using ordinary mobile phone camera.
+Examples of the scanned document images in our dataset are illustrated in Figure \ref{fig:receipts}, note that the colored rectangles is only for visual reference and the actual labelled data is in token-level rather than the line-level that is shown in the figure.
+
+\subsection{Overall Performance}
+We report results of our method in terms of AP and compare with other state of the art methods in Table \ref{tab:comparison}.
+We also provides softAP results for CUTIE-A and CUTIE-B in Table \ref{tab:comparison}, where both the softAP of CUTIE-A and CUTIE-B exceeds their AP by a large margin.
+Examples of inference results are illustrated in Figure \ref{fig:result}.
+Our big network CUTIE-A achieves $91.2\%$ AP and $98.1\%$ softAP on taxi receipts, $84.8\%$ AP and $93.5\%$ softAP on meals entertainment receipts, and $62.7\%$ AP and $88.0\%$ softAP on hotel receipts, outperforming other methods in almost all of the test cases.
+Compared to CloudScan, our big network CUTIE-A improves AP by $20.8\%$ AP on meals entertainment receipts, $9.2\%$ on taxi receipt, and $2.7\%$ on hotel receipts; our small network CUTIE-B improves AP by $13.2$ on taxi receipts, $20.3\%$ points on meals entertainment receipts, and $10.8\%$ on hotel receipts.
+Furthermore, compared to BERT, where model is pre-trained on a dataset with $3,300M$ words and transfer learned on our dataset, our big network CUTIE-B improves AP by $4.2\%$ and $4.5\%$ in taxi receipts and meals entertainment while using only $1/2$ parameters, our small network CUTIE-B improves AP by $8.2\%$ and $4.0\%$ in taxi receipts and meals entertainment but with much less complexity and smaller model size with only $1/9$ parameters without requiring a huge dataset for model pretraining.
+We will further prove in Section \ref{parameters} that CUTIE-B is also able to achieve state of the art performance with only $1/10$ of BERT's parameters.
+Although CUTIE-B is smaller in capacity, it outperforms CUTIE-A in several assessment criterias.
+This is because CUTIE-B enlarges field of view by employing the atrous convolution rather than the pooling or striding processes, the CUTIE-B model has larger field of view and better understanding of tokens' relative spatial relationship since no restrictions is applied on the feature maps shapes.
+
+It is worth noting that the difference of AP in the hotel receipt column actually leads to interesting findings.
+One of the finding is that if we neglect the 'VendorName' class in the evaluation criteria, the AP is increased to from $70.8\%$ to $76.9\%$ and the softAP drops to $83.8\%$, indicating that CUTIE is capable of extracting the interested 'VendorName' texts but sometimes involves texts that are not in the ground truth label.
+Another finding is that the hotel receipts are quite different from the meals entertainment receipts and the taxi receipts, where key information appears multi times in different areas of the receipt, whereas the human labelers tend to label only one of their appearances.
+We look deeper into this in the following part of this section by analyzing some inference result cases.
+
 Typical examples of receipts with low AP but high softAP score are shown in Figure \ref{fig:falsepositive}.
@@
 Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
-The false positives are results with the boundary-only rectangles being not overlapped with the filled rectangles.}
+The false positives are results with the boundary-only rectangles being not overlapped with the filled rectangles.
+We mask certain sensitive texts with filled gray rectangle only in this figure but not in }
 \label{fig:falsepositive}
@@
 
+\begin{table*}
+	\caption{Performance evaluation of CUTIE on ME with different embedding size.}
+\begin{center}
+\begin{tabular}{l | c | c | c | c | c | c | c | c | c | c}
+	Embedding Size & 1 & 2 & 4 & 8 & 16 & 32 & 64 & 128 & 256 & 512 \\
+	\hline
+	\#Params & 10.6M & 10.6M & 10.7M & 10.7M & 10.9M & 11.3M & 12.1M & 13.6M & 16.6M & 22.7M \\
+	AP & & & 84.3 & 82.8 & 84.9 & 84.8 & \textbf{85.0} & 84.3 & 84.6 & 84.4 \\
+	softAP & & & 94.1 & 92.0 & 91.4 & 91.2 & \textbf{92.9} & 92.4 & 91.9 & 91.9 \\
+\end{tabular}
+\end{center}
+	\label{tab:embedding}
+\end{table*}
+
+\begin{table*}
+	\caption{Performance evaluation of CUTIE-B on ME with different number of training samples.}
+\begin{center}
+\begin{tabular}{l | c | c | c | c | c | c | c | c | c}
+	Percentage(\%) & 3 & 12 & 21 & 30 & 39 & 48 & 57 & 66 & 75 \\
+	\hline
+	AP & 56.2 & 76.4 & 79.6 & 80.8 & 82.6 & 81.4 & 83.4 & \textbf{85.0} & 84.3 \\
+	softAP & 76.0 & 86.5 & 88.7 & 90.3 & 90.5 & 90.7 & 90.7 & 91.1 & \textbf{91.5} \\
+\end{tabular}
+\end{center}
+	\label{tab:samples}
+\end{table*}
+
 \subsection{Ablation Studies}
@@
 In this section, we perform ablation studies over a number of facets of CUTIE in order to better understand their relative importance.
+CUTIE-B is employed as the default model with grid augmentation, embedding size of $128$, and $75\%$ of dataset as training data.
 
@@
 The grid augmentation process further enhances this ability.
-To give evidence to this claim, we evaluate CUTIE with or without the grid augmentation process.
+To provide more evidence to this claim, we evaluate CUTIE with or without the grid augmentation process to test the model performance in terms of spatial diversity.
 Results are presented in Table \ref{tab:augmentation}.
-We can see that adding grid augment process in CUTIE can significantly improve the performance on all of these receipts.
+We can see that adding the grid augment process in CUTIE can significantly improve the performance on all of these receipts.
 These results demonstrate that CUTIE can greatly benefit from enhancing data diversity in spatial distribution.
@@
 \begin{table}
-	\caption{Performance evaluation of CUTIE with or without the grid augmentation process. (AP / softAP)}
+	\caption{Performance evaluation of CUTIE on ME with or without the grid augmentation process.}
 \begin{center}
-\begin{tabular}{l | c | c | c}
-	 & Taxi & ME & Hotel \\
+\begin{tabular}{l | c | c}
+	 & w/o augmentation & w augmentation \\
 	\hline
-	w augmentation & / & / & \\
-	w/o augmentation & / & / & \\
+	AP & 83.3 & 84.3 \\
+	softAP & 93.7 & 92.4 \\
 \end{tabular}
@@
 \subsubsection{Impact of Semantical Information Capacity}
-Next, we evaluate the impact of semantical information of CUTIE by comparing evaluation with different word embedding sizes, although it is intuitively clear that larger embedding size provides more semantic capacity.
-As reported in Table \ref{tab:embedding}, CUTIE performs worse with smaller embedding size.
-The result meets our expectation that $details$.
+\label{parameters}
+Next, we evaluate the impact of semantical information of CUTIE by comparing evaluation with different word embedding sizes.
+As reported in Table \ref{tab:embedding}, CUTIE performs in a bell shape curve as the embedding size increases.
+The best performance is achieved by CUTIE-B that achieves embedding size of $64$ with $85.0\%$ in AP and $94.3\%$ in softAP and CUTIE-B with embedding size of $64$ and $4$.
+One interesting finding is that the CUTIE model achieves satisfiable performance even with limited semantical information capacity.
+We infer the reason is that, for a SROIE problem in this paper with 9 key information classes, there are small amount of key tokens provide the majority of contribution to the model inference and the model can achieve good performance by paying special attention to these key tokens.
+It is also indicated in the result that too large embedding size also decreases the model performace.
 To further enhance the model performance, it might help to randomly mask out certain texts during the grid positional mapping process, such that the model learns inter-text relationship better with / without certain words present in the grid and further improves in generality.
-\begin{table}
-	\caption{Performance evaluation of CUTIE with different embedding size. (AP / softAP)}
-\begin{center}
-\begin{tabular}{l | c | c | c}
-	 & Taxi & ME & Hotel \\
-	\hline
-	64 & / & / & \\
-	128 & / & / & \\
-	256 & / & / & \\
-\end{tabular}
-\end{center}
-	\label{tab:embedding}
-\end{table}
 
 \subsubsection{Impact of Number of Training Samples}
-To evaluate the impact of different number of training samples on model performance, we train CUTIE with $30\%$, $39\%$, $48\%$, $57\%$, $66\%$, and $75\%$ of our dataset, and report the results in Table \ref{tab:samples}.
-\begin{table}
-	\caption{Performance evaluation of CUTIE with different number of training samples. (AP / softAP)}
-\begin{center}
-\begin{tabular}{l | c | c | c}
-	 & Taxi & ME & Hotel \\
-	\hline
-	30\% & / & / & \\
-	39\% & / & / & \\
-	48\% & / & / & \\
-	57\% & / & / & \\
-	66\% & / & / & \\
-	75\% & 84.3 / 91.5 & \textbf{92.8} / \textbf{98.0} & 70.8 / \textbf{83.8} \\
-\end{tabular}
-\end{center}
-	\label{tab:samples}
-\end{table}
+To evaluate the impact of different number of training samples on model performance, we train CUTIE with $3\%$, $12\%$, $21\%$, $30\%$, $39\%$, $48\%$, $57\%$, $66\%$, and $75\%$ of our dataset and report results in Table \ref{tab:samples}.
+It is not hard to find from the result that more training data leads to better performance either in terms of AP or softAP.
+CUTIE-B achieves the highest AP $85.0\%$ with $66\%$ of dataset as training samples and the highest softAP $91.5\%$ with $75\%$ of dataset as training samples.
+It is worth noting that CUTIE-B is already capable of achieving $79.6\%$ AP and $88.7\%$ softAP with only $21\%$ of dataset as training samples, which further proves the efficiency of the proposed method being capable of achieving good results with limited amount of training data.
 
@@
 Automatically extracting interested words / information from the scanned document images is of great interest to various services and applications.
-This paper proposes CUTIE to tackle this problem without requirement of any pre-training of post processing.
+This paper proposes CUTIE to tackle this problem without requirement of any pre-training or post processing.
 Experimental results verifies the effectiveness of the proposed method.
@@
 One interesting finding is that the trained CUTIE model correctly predicts certain key information that is neglected to be labelled by the human labeler, which further proves the effectiveness of the proposed method.
-It is also worth mention that incorporating better semantical feature processing module or involving image-level features may further boost the model performance and we leave it to future research.
+It is also worth mention that, as observed from experimental results, incorporating better semantical feature processing module or involving image-level features may further boost the model performance and we leave it to future research.
 
@@
 \subsection{Model Structure}
-We report the best performed CUTIE-B model in Table \ref{tab:cutie}.
+We report the CUTIE-B model in Table \ref{tab:cutie}.
 Tokens are firstly embedd into $128$ dimensional features.
@@
 Finally, inference result is achieved through a $1\times1$ convolution.
-\begin{table}
+\begin{table}[H]
 	\caption{Structure of the proposed CUTIE-B model. }

### 2019-03-27 main_evaluate_json.py

@@ -13,8 +13,8 @@ from data_loader_json import DataLoader
 from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--doc_path', type=str, default='data/hotel/') # modify this
-parser.add_argument('--save_prefix', type=str, default='hotel', help='prefix for load ckpt model') # modify this
+parser.add_argument('--doc_path', type=str, default='data/taxi_1108/') # modify this
+parser.add_argument('--save_prefix', type=str, default='taxi', help='prefix for load ckpt model') # modify this
 
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 

### 2019-03-27 model_cutie_aspp.py

@@ -45,8 +45,8 @@ class CUTIERes(CUTIE):
              .dilate_conv(3, 5, 256, 1, 1, 16, name='encoder1_8'))
         
         # Atrous Spatial Pyramid Pooling module
-        (self.feed('encoder1_8')
-             .conv(1, 1, 256, 1, 1, name='aspp_0'))
+        #(self.feed('encoder1_8')
+        #     .conv(1, 1, 256, 1, 1, name='aspp_0'))
         (self.feed('encoder1_8')
              .dilate_conv(3, 5, 256, 1, 1, 4, name='aspp_1'))
         (self.feed('encoder1_8')
@@ -55,7 +55,7 @@ class CUTIERes(CUTIE):
              .dilate_conv(3, 5, 256, 1, 1, 16, name='aspp_3'))
         (self.feed('encoder1_8')
              .global_pool(name='aspp_4'))
-        (self.feed('aspp_0', 'aspp_1', 'aspp_2', 'aspp_3', 'aspp_4')
+        (self.feed('aspp_1', 'aspp_2', 'aspp_3', 'aspp_4')
              .concat(3, name='aspp_concat')
              .conv(1, 1, 256, 1, 1, name='aspp_1x1'))
         

### 2019-03-29 Article/ms.tex
paper finished

@@
    Extracting key information from documents, such as receipts or invoices, and preserving the interested texts to structured data is crucial in the document-intensive streamline processes of office automation in areas that includes but not limited to accounting, financial, and taxation areas.
-Large proportion of published works attempt to tackle the problem by exploring the semantic context in text sequences based on the Named Entity Recognition (NER) method in the NLP field.
-In this paper, we propose to combine the effective information from both semantic meaning and spatial distribution of texts in documents.
-Specifically, our proposed model, Convolutional Universal Text Information Extractor (CUTIE), applies convolutional neural networks on the gridded texts where texts are embedded as features with semantical connotations.
+To avoid designing expert rules for each specific type of document, some published works attempt to tackle the problem by learning a model to explore the semantic context in text sequences based on the Named Entity Recognition (NER) method in the NLP field.
+In this paper, we propose to harness the effective information from both semantic meaning and spatial distribution of texts in documents.
+Specifically, our proposed model, Convolutional Universal Text Information Extractor (CUTIE), applies convolutional neural networks on gridded texts where texts are embedded as features with semantical connotations.
 We further explore the effect of employing different structures of convolutional neural network and propose a fast and portable structure.
@@
 
-\cite{cloudscan} proposed a learning based invoice analysis system named CloudScan, aiming to not rely on invoice layout templates, CloudScan trains a model that could be generalized to unseen invoice layouts, where a model is trained either using Long Short Term Memory (LSTM) or Logistic Regression (LR) with expert designed rules.
-This turns out to be extremely similar with a Named Entity Recognition (NER) model or a slot filling model.
-The Bi-directional Encoder Representations from Transformers (BERT) model proposed in \cite{bert} is a recently proposed state of the art method and has achieved great success in a wide of range of NLP tasks including NER.
-However, the methods based on the Named Entity Recognition (NER) research in the NLP field that is not originally designed to solve the key information extraction problem in SROIE, which align text words in the original document as a long paragraph in line-based rule.
-However, the real-world documents, such as receipts and invoices, present with various styles of layouts that were designed for different scenarios or from different enterprise entities.
-The order or word-to-word distance of the texts in the line-based aligned long paragraph tend to vary greatly due to layout variations, which is difficult to be handled with the natural language paragraph oriented methods, one typical example is illustrated in Fig.
+CloudScan is a learning based invoice analysis system \cite{cloudscan}.
+Aiming to not rely on invoice layout templates, CloudScan trains a model that could be generalized to unseen invoice layouts, where a model is trained either using Long Short Term Memory (LSTM) or Logistic Regression (LR) with expert designed rules as training features.
+This turns out to be extremely similar with solving a Named Entity Recognition (NER) or slot filling task.
+For that reason, several models can be employed, e.g., the Bi-directional Encoder Representations from Transformers (BERT) model is a recently proposed state of the art method and has achieved great success in a wide of range of NLP tasks including NER \cite{bert}.
+However, the NER models were not originally designed to solve the key information extraction problem in SROIE.
+To employ NER models, text words in the original document are aligned as a long paragraph in line-based rule.
+In fact, documents, such as receipts and invoices, present with various styles of layouts that were designed for different scenarios or from different enterprise entities.
+The order or word-to-word distance of the texts in the line-base-aligned long paragraph tend to vary greatly due to layout variations, which is difficult to be handled with the natural language oriented methods.
+Typical example of documents with different layouts are illustrated in Fig.
 \ref{fig:receipts}.
@@
 \begin{center}
-\includegraphics[width=0.99\linewidth]{Model.png}
+\includegraphics[width=0.99\linewidth]{Model.jpg}
 \end{center}
@@
 \end{figure*}
-In this work, attempting to involve the spatial information into the key information extraction process, we propose to tackle this problem by using the CNN based network structure and involve the semantic features in a properly designed fashion.
+In this work, attempting to involve the spatial information into the key information extraction process, we propose to tackle this problem by using the CNN based network structure and involve the semantic features in a carefully designed fashion.
 In particular, our proposed model, called Convolutional Universal Text Information Extractor (CUTIE), tackles the key information extraction problem by applying convolutional deep learning model on the gridded texts, as illustrated in Fig.
@@
 The rich semantic information is encoded from the gridded texts at the very beginning stage of the convolutional neural network with a word embedding layer.
-The CUTIE allows for simultaneously looking into both semantical information and spatial information of the texts in the scanned document image and can reach a new state of the art result for key information extraction, which outperforms BERT model but without demand pretraining on a huge text dataset \cite{bert,transformer}.
+The CUTIE allows for simultaneously looking into both semantical information and spatial information of the texts in the scanned document image and can reach a new state of the art result for key information extraction, which outperforms BERT model but without demanding of pretraining on a huge text dataset \cite{bert,transformer}.
 
-\section{Related Work}
+\section{Related Works}
 Several rule-based invoice analysis systems were proposed in \cite{3,5,7}.
@@
 
-CloudScan is a work attempting to extracting key information with learning based models \cite{cloudscan}.
+CloudScan is a work attempting to extract key information with learning based models \cite{cloudscan}.
 Firstly, N-grams features are formed by connecting expert designed rules calculated results on texts of each document line.
@@
 \begin{center}
-\includegraphics[width=0.99\linewidth]{Receipts.png}
+\includegraphics[width=0.99\linewidth]{Receipts.jpg}
 \end{center}
@@
 However, spatial resolution is reduced in the encoding process and the decoding process exploits only high resolution but low-level features to recover the spatial resolution, the consecutive striding encoding process decimates detail information \cite{hrnet}.
-Moreover, the encoding and decoding process applies shape restricts to the grid shape augment process as introduced in Section \ref{pm}.
+Moreover, the encoding and decoding process applies shape restricts to the grid shape augmentation process as introduced in Section \ref{pm}.
 
@@
 To capture long distance connection and avoid potential information loss in the encoding process, we propose two different network architectures and compare their performance in Section \ref{experiment}.
-We had experimented with various types of model structures and only detail two of them here to avoid being a tedious paper.
-Specifically, proposed CUTIE-A is a high capacity convolutional neural network that fuses multi-resolution features without losing high-resolution features, proposed CUTIE-B is a convolutional network with atrous convolution for enlarging field of view and Atrous Spatial Pyramid Pooling (ASPP) module to capture multi-scale contexts.
+In fact, we had experimented with various types of model structures and only detail two of them here to avoid being a tedious paper.
+Specifically, the proposed CUTIE-A is a high capacity convolutional neural network that fuses multi-resolution features without losing high-resolution features, the proposed CUTIE-B is a convolutional network with atrous convolution for enlarging field of view and Atrous Spatial Pyramid Pooling (ASPP) module to capture multi-scale contexts.
 
@@
 The training is terminated within $40,000$ steps with batch size of $32$.
+We train our model on Tesla V100 GPU where $11$ to $19$GB memories is used depending the configuration of the model framework and size of the dataset.
 Instance normalization is involved to facilate training.
 Our model is trained end-to-end without piecewise pretraining of any component.
-The embedding size is $128$, target augmentation shape is $64$ for both row and column.
+The default embedding size is $128$, target augmentation shape is $64$ for both row and column.
 The dataset is split as training set and test set with ratio of $75:25$.
@@
 \begin{center}
-\subfloat{\includegraphics[width=0.17\linewidth]{appendix/meals/Correct_0.png}} 
+\subfloat{\includegraphics[width=0.17\linewidth]{mCorrect_0.jpg}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.39\linewidth]{appendix/meals/Correct_1.png}}
+\subfloat{\includegraphics[width=0.39\linewidth]{mCorrect_1.jpg}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.17\linewidth]{appendix/meals/Correct_2.png}}
+\subfloat{\includegraphics[width=0.17\linewidth]{mCorrect_2.jpg}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.17\linewidth]{appendix/meals/Correct_3.png}} \\ 
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_4.png}}  
+\subfloat{\includegraphics[width=0.17\linewidth]{mCorrect_3.jpg}} \\ 
+\subfloat{\includegraphics[width=0.19\linewidth]{mCorrect_4.jpg}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_5.png}}  
+\subfloat{\includegraphics[width=0.19\linewidth]{mCorrect_5.jpg}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_9.png}}  
+\subfloat{\includegraphics[width=0.19\linewidth]{mCorrect_9.jpg}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_7.png}}  
+\subfloat{\includegraphics[width=0.19\linewidth]{mCorrect_7.jpg}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/meals/Correct_8.png}} \\
-\subfloat{\includegraphics[width=0.35\linewidth]{appendix/hotel/Correct_0.png}}  
+\subfloat{\includegraphics[width=0.19\linewidth]{mCorrect_8.jpg}} \\
+\subfloat{\includegraphics[width=0.35\linewidth]{hCorrect_0.jpg}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.19\linewidth]{appendix/hotel/Correct_1.png}}  
+\subfloat{\includegraphics[width=0.19\linewidth]{hCorrect_1.jpg}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.21\linewidth]{appendix/hotel/Correct_2.png}}  
+\subfloat{\includegraphics[width=0.21\linewidth]{hCorrect_2.jpg}}  
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.21\linewidth]{appendix/hotel/Correct_3.png}}  
+\subfloat{\includegraphics[width=0.21\linewidth]{hCorrect_3.jpg}}  
 \end{center}
@@
 Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
-The result is perfectly correct as if the filled rectangles overlap with the boundary-only rectangles.}
+The result is perfectly correct as if the filled rectangles overlap with the boundary-only rectangles.
+We mask out certain personal information with filled gray rectangle in the figure.}
 \label{fig:result}
@@
 Although the letter shows distinct appearance from the other digits in the scanned receipt image, it is mis-interpreted as one part of the 'BaseAmount' class due to its close spatial location to the digits and it-self being a digit.
-It is also can be seen in the first receipt in the second row that several spatial distant digits were wrongly predicted as in the 'BaseAmount' class.
+It also can be seen in the first receipt in the second row that several spatial distant digits were wrongly predicted as in the 'BaseAmount' class.
 Although these are rare cases in our test set, it still suggests that incorporating image-level information may further boost the inference accuracy inspite of the already involved semantical and spatial features.
@@
 \begin{center}
-\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalsePositive_0.png}} 
+\subfloat{\includegraphics[width=0.31\linewidth]{mFalsePositive_0.jpg}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalsePositive_1.png}}
+\subfloat{\includegraphics[width=0.31\linewidth]{mFalsePositive_1.jpg}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalsePositive_3.png}}\\
-\subfloat{\includegraphics[width=0.29\linewidth]{appendix/hotel/FalsePositive_0.png}}
+\subfloat{\includegraphics[width=0.31\linewidth]{mFalsePositive_3.jpg}}\\
+\subfloat{\includegraphics[width=0.29\linewidth]{hFalsePositive_0.jpg}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.35\linewidth]{appendix/taxi/FalsePositive_0.png}}
+\subfloat{\includegraphics[width=0.35\linewidth]{tFalsePositive_0.jpg}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.29\linewidth]{appendix/hotel/FalsePositive_1.png}}
-\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.29\linewidth]{hFalsePositive_1.jpg}}
 \end{center}
@@
 The false positives are results with the boundary-only rectangles being not overlapped with the filled rectangles.
-We mask certain sensitive texts with filled gray rectangle only in this figure but not in }
+We mask out certain personal information with filled gray rectangle in the figure.}
 \label{fig:falsepositive}
@@
 \begin{center}
-\subfloat{\includegraphics[width=0.28\linewidth]{appendix/meals/FalseLabel_0.png}} 
+\subfloat{\includegraphics[width=0.28\linewidth]{mFalseLabel_0.jpg}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.34\linewidth]{appendix/meals/FalseLabel_1.png}} 
+\subfloat{\includegraphics[width=0.34\linewidth]{mFalseLabel_1.jpg}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalseLabel_2.png}}\\
-\subfloat{\includegraphics[width=0.31\linewidth]{appendix/meals/FalseLabel_3.png}} 
+\subfloat{\includegraphics[width=0.31\linewidth]{mFalseLabel_2.jpg}}\\
+\subfloat{\includegraphics[width=0.31\linewidth]{mFalseLabel_3.jpg}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.31\linewidth]{appendix/hotel/FalseLabel_0.png}}
+\subfloat{\includegraphics[width=0.31\linewidth]{hFalseLabel_0.jpg}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.31\linewidth]{appendix/taxi/FalseLabel_4.png}}\\
-\subfloat{\includegraphics[width=0.36\linewidth]{appendix/taxi/FalseLabel_0.png}} 
+\subfloat{\includegraphics[width=0.31\linewidth]{tFalseLabel_4.jpg}}\\
+\subfloat{\includegraphics[width=0.36\linewidth]{tFalseLabel_0.jpg}} 
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.22\linewidth]{appendix/taxi/FalseLabel_5.png}}
+\subfloat{\includegraphics[width=0.22\linewidth]{tFalseLabel_5.jpg}}
 \subfloat{\fcolorbox{white}{white}{}}
-\subfloat{\includegraphics[width=0.36\linewidth]{appendix/hotel/FalseLabel_1.png}}\\
+\subfloat{\includegraphics[width=0.36\linewidth]{hFalseLabel_1.jpg}}\\
 \end{center}
@@
 Color legend in the top-left corner indicates the key information classes.
-Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.}
+Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
+We mask certain personal information with filled gray rectangle in the figure.}
 \label{fig:falselabel}
@@
 	\#Params & 10.6M & 10.6M & 10.7M & 10.7M & 10.9M & 11.3M & 12.1M & 13.6M & 16.6M & 22.7M \\
-	AP & & & 84.3 & 82.8 & 84.9 & 84.8 & \textbf{85.0} & 84.3 & 84.6 & 84.4 \\
-	softAP & & & 94.1 & 92.0 & 91.4 & 91.2 & \textbf{92.9} & 92.4 & 91.9 & 91.9 \\
+	AP & 79.1 & 82.8 & 83.1 & 82.8 & 84.9 & 84.8 & \textbf{85.0} & 84.3 & 84.6 & 84.4 \\
+	softAP & 87.3 & 90.3 & 90.4 & 92.0 & 91.4 & 91.2 & \textbf{92.9} & 92.4 & 91.9 & 91.9 \\
 \end{tabular}
@@
 Although we have demonstrated extremely strong empirical results, the results presented are achieved by combination of each aspect of the CUTIE framework.
-In this section, we perform ablation studies over a number of facets of CUTIE in order to better understand their relative importance.
+In this section, we perform ablation studies over a number of facets of CUTIE in order to have a better understanding of their relative importance.
 CUTIE-B is employed as the default model with grid augmentation, embedding size of $128$, and $75\%$ of dataset as training data.
@@
 Results are presented in Table \ref{tab:augmentation}.
-We can see that adding the grid augment process in CUTIE can significantly improve the performance on all of these receipts.
+We can see that adding the grid augment process in CUTIE significantly improves the performance.
 These results demonstrate that CUTIE can greatly benefit from enhancing data diversity in spatial distribution.
-For that reason, further analysis about grid augmentation techniques will surely further enhance CUTIE's performance, \eg, randomly moving certain texts upward, downward, leftward, or rightward by several pixels during the grid positional mapping process.
+For that reason, further analysis about grid augmentation techniques may enhance CUTIE's performance, \eg, randomly moving certain texts upward, downward, leftward, or rightward by several pixels during the grid positional mapping process.
 \begin{table}
@@
 As reported in Table \ref{tab:embedding}, CUTIE performs in a bell shape curve as the embedding size increases.
-The best performance is achieved by CUTIE-B that achieves embedding size of $64$ with $85.0\%$ in AP and $94.3\%$ in softAP and CUTIE-B with embedding size of $64$ and $4$.
-One interesting finding is that the CUTIE model achieves satisfiable performance even with limited semantical information capacity.
-We infer the reason is that, for a SROIE problem in this paper with 9 key information classes, there are small amount of key tokens provide the majority of contribution to the model inference and the model can achieve good performance by paying special attention to these key tokens.
+The best performance is achieved by CUTIE-B with $85.0\%$ in AP and $92.9\%$ in softAP using embedding size of $64$.
+One interesting finding is that the CUTIE model achieves good performance even with limited semantical information capacity.
+We infer the reason is that, for the SROIE problem with 9 key information classes, there are a small amount of key tokens provide the majority of contribution to the model inference and the model can achieve good performance by paying special attention to these key tokens.
 It is also indicated in the result that too large embedding size also decreases the model performace.
@@
 \bibliographystyle{ieee}
-\bibliography{biblio}
+\bibliography{ms}
 }
@@
 Tokens are firstly embedd into $128$ dimensional features.
-Then, $4$ consecutive convolution operations are conducted in the conv block and $4$ consecutive atrous convolution are conducted in the atrous conv block with stride $1$ and rate $2$.
-Following the atrous conv block, an ASPP module is employed to combine multi-resolution features.
+Then, $4$ consecutive convolution operations are conducted in the conv block with stride $1$ and $4$ consecutive atrous convolution are conducted in the atrous conv block with stride $1$ and rate $2$.
+Following the atrous conv block, an ASPP module is employed to fuse multi-resolution features.
 The low level but high resolution feature from the $1$st output of the convolution block is also added to the model in the shortcut layer with a concatenation operation and a $1\times1$ convolution.
-Finally, inference result is achieved through a $1\times1$ convolution.
+Finally, inference output is achieved through a $1\times1$ convolution.
 \begin{table}[H]

### 2019-03-29 main_evaluate_json.py

@@ -13,8 +13,8 @@ from data_loader_json import DataLoader
 from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--doc_path', type=str, default='data/taxi_1108/') # modify this
-parser.add_argument('--save_prefix', type=str, default='taxi', help='prefix for load ckpt model') # modify this
+parser.add_argument('--doc_path', type=str, default='data/hotel_1108/') # modify this
+parser.add_argument('--save_prefix', type=str, default='hotel', help='prefix for load ckpt model') # modify this
 
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 
@@ -42,7 +42,7 @@ params = parser.parse_args()
 if __name__ == '__main__':
     # data
     #data_loader = DataLoader(params, True, True) # True to use 25% training data
-    data_loader = DataLoader(params, update_dict=False, load_dictionary=True, data_split=0.75) # False to provide a path with only test data
+    data_loader = DataLoader(params, update_dict=False, load_dictionary=True, data_split=0) # False to provide a path with only test data
     num_words = max(20000, data_loader.num_words)
     num_classes = data_loader.num_classes
 
@@ -63,7 +63,7 @@ if __name__ == '__main__':
             print('{} restored'.format(ckpt_path))
         except:
             raise Exception('Check your pretrained {:s}'.format(ckpt_path))
-            
+        
         # calculate validation accuracy and display results   
         recalls, accs_strict, accs_soft = [], [], []
         num_test = len(data_loader.validation_docs)

### 2019-03-29 main_train_json.py

@@ -131,10 +131,10 @@ if __name__ == '__main__':
     data_loader = DataLoader(params, update_dict=params.update_dict, load_dictionary=params.load_dict, data_split=0.75)
     num_words = max(20000, data_loader.num_words)
     num_classes = data_loader.num_classes
-    for _ in range(2):
-        a = data_loader.next_batch()
-        b = data_loader.fetch_validation_data()
-        c = data_loader.fetch_test_data()
+    #for _ in range(2):
+    #    a = data_loader.next_batch()
+    #    b = data_loader.fetch_validation_data()
+    #    c = data_loader.fetch_test_data()
     
     # model
     network = CUTIERes(num_words, num_classes, params)
@@ -260,7 +260,7 @@ if __name__ == '__main__':
                       %(recall, acc_strict, acc_soft, max(training_recall), max(training_acc_strict), max(training_acc_soft)))
                 
             # calculate validation accuracy and display results
-            if iter%params.validation_step == 0:
+            if iter%params.validation_step == 0 and len(data_loader.validation_docs):
                 
                 recalls, accs_strict, accs_soft = [], [], []
                 for _ in range(len(data_loader.validation_docs)):
@@ -311,7 +311,7 @@ if __name__ == '__main__':
                     print('\nBest up-to-date performance validation checkpoint saved.\n')
                 
             # calculate validation accuracy and display results
-            if params.test_path!='' and iter%params.test_step == 0:
+            if params.test_path!='' and iter%params.test_step == 0 and len(data_loader.test_docs):
                 
                 recalls, accs_strict, accs_soft = [], [], []
                 while True:

### 2019-04-03 Article/ms.tex
CUTIEv1 finalized

@@
 where $c_{g_t}$ is the mean center of the target augment gird size, $r_{g_t}$ is the mean center of the target augment grid size, and $\sigma$ is the standard deviation.
+In case of two tokens occupy the same grid cell, tokens in the same row are shifted to place the tokens.
+This is acceptable since the model learns the relative spatial relationship among tokens and convolutional neural networks handle translations well.
 
@@
 	ME & 1109 & 475 & 9 \\
-	Taxi & 2514 & 1077 & 6 \\
-	Hotel & 1353 & 452 & 9 \\
+	Taxi & 1125 & 375 & 6 \\
+	Hotel & 1125 & 375 & 9 \\
 \end{tabular}
@@
 \begin{table*}
-	\caption{Performance comparison on different types of documents. Post-processing is abbreviated as pp.}
+	\caption{Performance comparison on different types of documents. (AP/softAP)}
 \begin{center}
@@
 	CloudScan\cite{cloudscan} & - & 82 / - & 64 / - & 60 / - \\
-	BERT\cite{bert}+pp & 110M & 87.0 / - & 80.3 / - & \textbf{79.4} / - \\
-	CUTIE-A & 67M & 91.2 / 98.1 & \textbf{84.8} / \textbf{93.5} & 62.7 / 88.9 \\
-	CUTIE-B & \textbf{14M} & \textbf{95.2} / \textbf{97.6} & 84.3 / 92.4 & 70.8 / \textbf{89.4} \\
+	BERT\cite{bert} & 110M & 88.1 / - & 80.1 / - & 71.7 / - \\
+	CUTIE-A & 67M & \\
+	CUTIE-B & 14M & 93.3 / 96.9 & 81.0 / 88.9 & 75.8 / 87.1 \\
+	%CUTIE-A split & 67M & 92.9 / 96.7 & 81.4 / 91.6 & 72.3 / 95.0 \\
+	%CUTIE-B split & 14M & 95.2 / 97.6 & 84.3 / 92.4 & 70.8 / 89.4 \\
 \end{tabular}
@@
 The BERT model for SROIE is transform learned with the Google released base model that is pre-trained on a huge dataset with $3,300$M words \cite{bert,bertgit}.
-Furthermore, post-processing is applied to the BERT results to eliminate certain errors and enhance accuracy.
 It is worth noting that the CloudScan based method and BERT based method were implemented by other teams.
@@
 	\#Params & 10.6M & 10.6M & 10.7M & 10.7M & 10.9M & 11.3M & 12.1M & 13.6M & 16.6M & 22.7M \\
-	AP & 79.1 & 82.8 & 83.1 & 82.8 & 84.9 & 84.8 & \textbf{85.0} & 84.3 & 84.6 & 84.4 \\
-	softAP & 87.3 & 90.3 & 90.4 & 92.0 & 91.4 & 91.2 & \textbf{92.9} & 92.4 & 91.9 & 91.9 \\
+	AP & 79.1 & 82.8 & 83.1 & 82.8 & 82.9 & 83.2 & 83.8 & 84.3 & \textbf{84.6} & 84.4 \\
+	softAP & 87.3 & 90.3 & 90.4 & 92.0 & 90.6 & 90.7 & 92.3 & \textbf{92.4} & 91.9 & 91.9 \\
 \end{tabular}

### 2019-04-03 data_loader_json.py

@@ -10,6 +10,7 @@ from collections import defaultdict
 import numpy as np
 import tensorflow as tf
 import tokenization
+import cv2
 
 DEBUG = False # True to show grid as image 
 
@@ -34,8 +35,13 @@ class DataLoader():
     """
     def __init__(self, params, update_dict=True, load_dictionary=False, data_split=0.75):
         self.random = False
+        self.data_laundry = False
         self.encoding_factor = 1 # ensures the size (rows/cols) of grid table compat with the network
+        self.classes = ['DontCare', 'Table']
+        #self.classes = ['DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', 'TaxRate']
+        
         self.doc_path = params.doc_path
+        self.use_cutie2 = params.use_cutie2 
         self.text_case = params.text_case 
         self.tokenize = params.tokenize
         if self.tokenize:
@@ -52,7 +58,7 @@ class DataLoader():
         self.cols_target = params.cols_target if hasattr(params, 'cols_target') else 64 
         self.rows_ulimit = params.rows_ulimit if hasattr(params, 'rows_ulimit') else 80 # handle OOM, must be multiple of self.encoding_factor
         self.cols_ulimit = params.cols_ulimit if hasattr(params, 'cols_ulimit') else 80 # handle OOM, must be multiple of self.encoding_factor
-        
+                
         self.fill_bbox = params.fill_bbox if hasattr(params, 'fill_bbox') else False # fill bbox with labels or use one single lable for the entire bbox
         
         self.data_augmentation_dropout = params.data_augmentation_dropout if hasattr(params, 'data_augmentation_dropout') else False # TBD: randomly dropout rows/cols
@@ -71,7 +77,6 @@ class DataLoader():
             self.dictionary = {'[PAD]':0, '[UNK]':0} # word/counts. to be updated in self.load_data() and self._update_docs_dictionary()
             self.word_to_index = {}
             self.index_to_word = {}
-        self.classes = ['DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', 'TaxRate']
 
         self.data_split = data_split # split data to training/validation, 0 for all for validation
         self.data_mode = 2 # 0 to consider key and value as two different class, 1 the same class, 2 only value considered
@@ -165,26 +170,29 @@ class DataLoader():
 
[…]

### 2019-04-03 deprecated/model_cutie_dilate.py

@@ -1,0 +1,52 @@
+# written by Xiaohui Zhao
+# 2019-03 
+# xiaohui.zhao@accenture.com
+import tensorflow as tf
+from model_cutie import CUTIE    
+    
+class CUTIERes(CUTIE):
+    def __init__(self, num_vocabs, num_classes, params, trainable=True):
+        self.name = "CUTIE_dilate" # 
+        
+        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
+        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
+        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
+        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
+
+        self.num_vocabs = num_vocabs
+        self.num_classes = num_classes     
+        self.trainable = trainable
+        
+        self.embedding_size = params.embedding_size
+        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
+        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
+        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
+        
+        self.layer_inputs = []        
+        self.setup()
+        
+    
+    def setup(self):        
+        # input
+        (self.feed('data')
+             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
+        
+        # encoder
+        (self.feed('embedding')
+             .conv(3, 5, 128, 1, 1, name='encoder1_1')
+             .conv(3, 5, 128, 1, 1, name='encoder1_2')
+             .dilate_conv(3, 5, 256, 1, 1, 2, name='encoder1_3')
+             .dilate_conv(3, 5, 256, 1, 1, 2, name='encoder1_4')
+             .dilate_conv(3, 5, 512, 1, 1, 2, name='encoder1_5')
[…]

### 2019-04-03 deprecated/model_cutie_res16.py

@@ -1,0 +1,75 @@
+# written by Xiaohui Zhao
+# 2018-12 
+# xiaohui.zhao@accenture.com
+import tensorflow as tf
+from model_cutie import CUTIE    
+    
+class CUTIERes(CUTIE):
+    def __init__(self, num_vocabs, num_classes, params, trainable=True):
+        self.name = "CUTIE_residual_16x" # 16x down sampling
+        
+        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes})  
+        self.num_vocabs = num_vocabs
+        self.num_classes = num_classes     
+        self.trainable = trainable
+        
+        self.embedding_size = params.embedding_size
+        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
+        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
+        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
+        
+        self.layer_inputs = []        
+        self.setup()
+        
+    
+    def setup(self):        
+        # input
+        (self.feed('data')
+             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
+        
+        # encoder
+        (self.feed('embedding')
+             .conv(3, 5, 64, 1, 1, name='encoder1_1')
+             .conv(3, 5, 128, 1, 1, name='encoder1_2')
+             .max_pool(2, 2, 2, 2, name='pool1')
+             .conv(3, 5, 128, 1, 1, name='encoder2_1')
+             .conv(3, 5, 256, 1, 1, name='encoder2_2')
+             .max_pool(2, 2, 2, 2, name='pool2')
+             .conv(3, 5, 256, 1, 1, name='encoder3_1')
+             .conv(3, 5, 512, 1, 1, name='encoder3_2')
+             .max_pool(2, 2, 2, 2, name='pool3')
+             .conv(3, 5, 512, 1, 1, name='encoder4_1')
+             .conv(3, 5, 512, 1, 1, name='encoder4_2')
+             .max_pool(2, 2, 2, 2, name='pool4')
[…]

### 2019-04-03 deprecated/model_cutie_res_att.py

@@ -1,0 +1,71 @@
+# written by Xiaohui Zhao
+# 2018-12 
+# xiaohui.zhao@accenture.com
+import tensorflow as tf
+from model_cutie import CUTIE    
+    
+class CUTIERes(CUTIE):
+    def __init__(self, num_vocabs, num_classes, params, trainable=True):
+        self.name = "CUTIE_residual_attention_8x" # 8x down sampling
+        
+        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
+        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
+        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
+        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
+
+        self.num_vocabs = num_vocabs
+        self.num_classes = num_classes     
+        self.trainable = trainable
+        
+        self.embedding_size = params.embedding_size
+        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
+        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
+        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
+        
+        self.layer_inputs = []        
+        self.setup()
+        
+    
+    def setup(self):        
+        # input
+        (self.feed('data')
+             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
+        
+        # encoder
+        (self.feed('embedding')
+             .conv(3, 5, 64, 1, 1, name='encoder1_1')
+             .conv(3, 5, 128, 1, 1, name='encoder1_2')
+             .max_pool(2, 2, 2, 2, name='pool1')
+             .conv(3, 5, 128, 1, 1, name='encoder2_1')
+             .conv(3, 5, 256, 1, 1, name='encoder2_2')
+             .max_pool(2, 2, 2, 2, name='pool2')
[…]

### 2019-04-03 main_evaluate_json.py

@@ -13,16 +13,16 @@ from data_loader_json import DataLoader
 from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--doc_path', type=str, default='data/hotel_1108/') # modify this
+parser.add_argument('--doc_path', type=str, default='data/hotel_small') # modify this
 parser.add_argument('--save_prefix', type=str, default='hotel', help='prefix for load ckpt model') # modify this
 
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 
 parser.add_argument('--e_ckpt_path', type=str, default='../graph/CUTIE/graph/') # modify this
 parser.add_argument('--ckpt_file', type=str, default='CUTIE_atrousSPP_d20000c9(r80c80)_iter_40000.ckpt')
-parser.add_argument('--positional_mapping_strategy', type=int, default=1)
-parser.add_argument('--rows_target', type=int, default=72) 
-parser.add_argument('--cols_target', type=int, default=72) 
+parser.add_argument('--positional_mapping_strategy', type=int, default=2)
+parser.add_argument('--rows_target', type=int, default=80)  
+parser.add_argument('--cols_target', type=int, default=80) 
 parser.add_argument('--rows_ulimit', type=int, default=80) 
 parser.add_argument('--cols_ulimit', type=int, default=80) 
 
@@ -42,7 +42,7 @@ params = parser.parse_args()
 if __name__ == '__main__':
     # data
     #data_loader = DataLoader(params, True, True) # True to use 25% training data
-    data_loader = DataLoader(params, update_dict=False, load_dictionary=True, data_split=0) # False to provide a path with only test data
+    data_loader = DataLoader(params, update_dict=False, load_dictionary=True, data_split=0.75) # False to provide a path with only test data
     num_words = max(20000, data_loader.num_words)
     num_classes = data_loader.num_classes
 
@@ -79,9 +79,14 @@ if __name__ == '__main__':
             fetches = [model_output]
             
             [model_output_val] = sess.run(fetches=fetches, feed_dict=feed_dict)
-            recall, acc_strict, acc_soft, res = cal_accuracy(data_loader, np.array(data['grid_table']), 
-                                                   np.array(data['gt_classes']), model_output_val, 
-                                                   np.array(data['label_mapids']), data['bbox_mapids'])                  
+#             recall, acc_strict, acc_soft, res = cal_accuracy(data_loader, np.array(data['grid_table']), 
[…]

### 2019-04-03 main_train_json.py

@@ -8,14 +8,17 @@ import timeit
 from pprint import pprint
 os.environ["CUDA_VISIBLE_DEVICES"] = "1"
 
-from model_cutie_aspp import CUTIERes
 from data_loader_json import DataLoader
 from utils import *
 
+from model_cutie_aspp import CUTIERes as CUTIEv1
+from model_cutie2_aspp import CUTIE2 as CUTIEv2
+
 parser = argparse.ArgumentParser(description='CUTIE parameters')
 # data
-parser.add_argument('--doc_path', type=str, default='data/taxi')
-parser.add_argument('--save_prefix', type=str, default='taxi', help='prefix for ckpt') # TBD: save log/models with prefix
+parser.add_argument('--use_cutie2', type=bool, default=False) # True to read image from doc_path 
+parser.add_argument('--doc_path', type=str, default='data/table')
+parser.add_argument('--save_prefix', type=str, default='table', help='prefix for ckpt') # TBD: save log/models with prefix
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
 # ckpt
@@ -34,26 +37,26 @@ parser.add_argument('--update_dict', type=bool, default=False)
 parser.add_argument('--dict_path', type=str, default='dict/---') # not used if load_dict is True
 
 # data manipulation
-parser.add_argument('--segment_grid', type=bool, default=True) # segment grid into two parts if grid is larger than cols_target
+parser.add_argument('--segment_grid', type=bool, default=False) # segment grid into two parts if grid is larger than cols_target
 parser.add_argument('--rows_segment', type=int, default=72) 
 parser.add_argument('--cols_segment', type=int, default=72) 
 parser.add_argument('--augment_strategy', type=int, default=1) # 1 for increasing grid shape size, 2 for gaussian around target shape
 parser.add_argument('--positional_mapping_strategy', type=int, default=2)
 parser.add_argument('--rows_target', type=int, default=64) 
 parser.add_argument('--cols_target', type=int, default=64) 
-parser.add_argument('--rows_ulimit', type=int, default=80) 
+parser.add_argument('--rows_ulimit', type=int, default=80) # used when data augmentation is true
 parser.add_argument('--cols_ulimit', type=int, default=80) 
 parser.add_argument('--fill_bbox', type=bool, default=False) # fill bbox with dict_id / label_id
 
 parser.add_argument('--data_augmentation_extra', type=bool, default=True) # randomly expand rows/cols
[…]

### 2019-04-03 model_cutie2.py

@@ -1,0 +1,147 @@
+# written by Xiaohui Zhao
+# 2019-04 
+# xiaohui.zhao@accenture.com
+import tensorflow as tf
+from model_framework import Model
+        
+class CUTIE2(Model):
+    def __init__(self, num_vocabs, num_classes, params, trainable=True):
+        self.name = "CUTTIE_benchmark" # 
+        
+        self.data_grid = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid')
+        self.data_image = tf.placeholder(tf.uint8, shape=[None, None, None, 3], name='image')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        
+        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
+        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
+        self.dropout = params.data_augmentation_dropout if hasattr(params, 'data_augmentation_dropout') else 1
+        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
+        self.layers = dict({'data_grid': self.data_grid, 'data_image': self.data_image, 
+                            'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
+
+        self.num_vocabs = num_vocabs
+        self.num_classes = num_classes     
+        self.trainable = trainable
+        
+        self.embedding_size = params.embedding_size
+        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
+        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
+        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
+        
+        self.layer_inputs = []        
+        self.setup()
+        
+    
+    def setup(self):        
+        # input
+        #         (self.feed('data_grid')
+        #              .embed(self.num_vocabs, self.embedding_size, name='embedding', dropout=self.dropout))  
+        #         (self.feed('data_image')
+        #              .conv(3, 3, 64, 1, 1, name='image_encoder1_1')
+        #              .conv(3, 3, 128, 1, 1, name='image_encoder1_2'))
+        #         
+        #         # encoder
[…]

### 2019-04-03 model_cutie2_aspp.py

@@ -1,0 +1,107 @@
+# written by Xiaohui Zhao
+# 2019-04
+# xiaohui.zhao@accenture.com
+import tensorflow as tf
+from model_cutie2 import CUTIE2 as CUTIE
+    
+class CUTIE2(CUTIE):
+    def __init__(self, num_vocabs, num_classes, params, trainable=True):
+        self.name = "CUTIE2_atrousSPP" # 
+        
+        self.data_grid = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='data_grid')
+        self.data_image = tf.placeholder(tf.float32, shape=[None, None, None, 3], name='data_image')
+        self.ps_1d_indices = tf.placeholder(tf.int32, shape=[None, None], name='ps_1d_indices')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        
+        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
+        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
+        self.dropout = params.data_augmentation_dropout if hasattr(params, 'data_augmentation_dropout') else 1
+        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
+        self.layers = dict({'data_grid': self.data_grid, 'data_image': self.data_image, 'ps_1d_indices': self.ps_1d_indices,
+                            'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
+
+        self.num_vocabs = num_vocabs
+        self.num_classes = num_classes     
+        self.trainable = trainable
+        
+        self.embedding_size = params.embedding_size
+        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
+        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
+        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
+        
+        self.layer_inputs = []        
+        self.setup()
+        
+    
+    def setup(self):                
+        ## grid
+        (self.feed('data_grid')
[…]

### 2019-04-03 model_cutie_aspp.py

@@ -8,12 +8,14 @@ class CUTIERes(CUTIE):
     def __init__(self, num_vocabs, num_classes, params, trainable=True):
         self.name = "CUTIE_atrousSPP" # 
         
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        self.data_grid = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='data_grid')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes') 
+        
         self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
         self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
+        self.dropout = params.data_augmentation_dropout if hasattr(params, 'data_augmentation_dropout') else 1
         self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
+        self.layers = dict({'data_grid': self.data_grid, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
 
         self.num_vocabs = num_vocabs
         self.num_classes = num_classes     
@@ -30,8 +32,8 @@ class CUTIERes(CUTIE):
     
     def setup(self):        
         # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
+        (self.feed('data_grid')
+             .embed(self.num_vocabs, self.embedding_size, name='embedding', dropout=self.dropout))  
         
         # encoder
         (self.feed('embedding')

### 2019-04-03 model_cutie_att.py

@@ -1,59 +1,0 @@
-# written by Xiaohui Zhao
-# 2019-03
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-from model_cutie import CUTIE    
-    
-class CUTIERes(CUTIE):
-    def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_attention" # 
-        
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
-        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
-        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
-        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
-
-        self.num_vocabs = num_vocabs
-        self.num_classes = num_classes     
-        self.trainable = trainable
-        
-        self.embedding_size = params.embedding_size
-        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
-        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
-        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
-        
-        self.layer_inputs = []        
-        self.setup()
-        
-    
-    def setup(self):        
-        # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding')
-             .conv(3, 5, 128, 1, 1, name='encoder0_1'))  
-        
-        # encoder
-        (self.feed('encoder0_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_2')
-             .conv(3, 5, 128, 1, 1, name='encoder1_3')
-             .conv(3, 5, 128, 1, 1, name='encoder1_4'))
-        
-        (self.feed('encoder0_1', 'encoder1_4')
-             .attention(1, name='attention2')
[…]

### 2019-04-03 model_cutie_dilate.py

@@ -1,52 +1,0 @@
-# written by Xiaohui Zhao
-# 2019-03 
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-from model_cutie import CUTIE    
-    
-class CUTIERes(CUTIE):
-    def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_dilate" # 
-        
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
-        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
-        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
-        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
-
-        self.num_vocabs = num_vocabs
-        self.num_classes = num_classes     
-        self.trainable = trainable
-        
-        self.embedding_size = params.embedding_size
-        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
-        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
-        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
-        
-        self.layer_inputs = []        
-        self.setup()
-        
-    
-    def setup(self):        
-        # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
-        
-        # encoder
-        (self.feed('embedding')
-             .conv(3, 5, 128, 1, 1, name='encoder1_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_2')
-             .dilate_conv(3, 5, 256, 1, 1, 2, name='encoder1_3')
-             .dilate_conv(3, 5, 256, 1, 1, 2, name='encoder1_4')
-             .dilate_conv(3, 5, 512, 1, 1, 2, name='encoder1_5')
[…]

### 2019-04-03 model_cutie_fpn8.py

@@ -1,73 +1,0 @@
-# written by Xiaohui Zhao
-# 2018-12 
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-from model_cutie import CUTIE    
-    
-class CUTIEFPN(CUTIE):
-    def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_fpn_8x" # 8x down sampling
-        
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes})  
-        self.num_vocabs = num_vocabs
-        self.num_classes = num_classes     
-        self.trainable = trainable
-        
-        self.embedding_size = params.embedding_size
-        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
-        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
-        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
-        
-        self.layer_inputs = []        
-        self.setup()
-        
-    
-    def setup(self):        
-        # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
-        
-        # encoder
-        (self.feed('embedding')
-             .conv(3, 5, 64, 1, 1, name='encoder1_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_2')
-             .max_pool(2, 2, 2, 2, name='pool1')
-             .conv(3, 5, 128, 1, 1, name='encoder2_1')
-             .conv(3, 5, 256, 1, 1, name='encoder2_2')
-             .max_pool(2, 2, 2, 2, name='pool2')
-             .conv(3, 5, 256, 1, 1, name='encoder3_1')
-             .conv(3, 5, 512, 1, 1, name='encoder3_2')
-             .conv(3, 5, 512, 1, 1, name='encoder3_3')
-             .max_pool(2, 2, 2, 2, name='pool3')
-             .conv(3, 5, 512, 1, 1, name='encoder4_1')
-             .conv(3, 5, 512, 1, 1, name='encoder4_2')
[…]

### 2019-04-03 model_cutie_hr.py

@@ -8,12 +8,13 @@ class CUTIERes(CUTIE):
     def __init__(self, num_vocabs, num_classes, params, trainable=True):
         self.name = "CUTIE_highresolution_8x" # 8x down sampling
         
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
+        self.data_grid = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
         self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
         self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
         self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
+        self.dropout = params.data_augmentation_dropout if hasattr(params, 'data_augmentation_dropout') else 1
         self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
+        self.layers = dict({'data_grid': self.data_grid, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
 
         self.num_vocabs = num_vocabs
         self.num_classes = num_classes     
@@ -30,8 +31,8 @@ class CUTIERes(CUTIE):
     
     def setup(self):        
         # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
+        (self.feed('data_grid')
+             .embed(self.num_vocabs, self.embedding_size, name='embedding', dropout=self.dropout)) 
         
         # stage 1 block 1
         (self.feed('embedding')

### 2019-04-03 model_cutie_res.py

@@ -1,71 +1,0 @@
-# written by Xiaohui Zhao
-# 2018-12 
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-from model_cutie import CUTIE    
-    
-class CUTIERes(CUTIE):
-    def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_residual_8x" # 8x down sampling
-        
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
-        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
-        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
-        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
-
-        self.num_vocabs = num_vocabs
-        self.num_classes = num_classes     
-        self.trainable = trainable
-        
-        self.embedding_size = params.embedding_size
-        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
-        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
-        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
-        
-        self.layer_inputs = []        
-        self.setup()
-        
-    
-    def setup(self):        
-        # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
-        
-        # encoder
-        (self.feed('embedding')
-             .conv(3, 5, 64, 1, 1, name='encoder1_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_2')
-             .max_pool(2, 2, 2, 2, name='pool1')
-             .conv(3, 5, 128, 1, 1, name='encoder2_1')
-             .conv(3, 5, 256, 1, 1, name='encoder2_2')
-             .max_pool(2, 2, 2, 2, name='pool2')
[…]

### 2019-04-03 model_cutie_res16.py

@@ -1,75 +1,0 @@
-# written by Xiaohui Zhao
-# 2018-12 
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-from model_cutie import CUTIE    
-    
-class CUTIERes(CUTIE):
-    def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_residual_16x" # 16x down sampling
-        
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes})  
-        self.num_vocabs = num_vocabs
-        self.num_classes = num_classes     
-        self.trainable = trainable
-        
-        self.embedding_size = params.embedding_size
-        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
-        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
-        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
-        
-        self.layer_inputs = []        
-        self.setup()
-        
-    
-    def setup(self):        
-        # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
-        
-        # encoder
-        (self.feed('embedding')
-             .conv(3, 5, 64, 1, 1, name='encoder1_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_2')
-             .max_pool(2, 2, 2, 2, name='pool1')
-             .conv(3, 5, 128, 1, 1, name='encoder2_1')
-             .conv(3, 5, 256, 1, 1, name='encoder2_2')
-             .max_pool(2, 2, 2, 2, name='pool2')
-             .conv(3, 5, 256, 1, 1, name='encoder3_1')
-             .conv(3, 5, 512, 1, 1, name='encoder3_2')
-             .max_pool(2, 2, 2, 2, name='pool3')
-             .conv(3, 5, 512, 1, 1, name='encoder4_1')
-             .conv(3, 5, 512, 1, 1, name='encoder4_2')
-             .max_pool(2, 2, 2, 2, name='pool4')
[…]

### 2019-04-03 model_cutie_res_att.py

@@ -1,71 +1,0 @@
-# written by Xiaohui Zhao
-# 2018-12 
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-from model_cutie import CUTIE    
-    
-class CUTIERes(CUTIE):
-    def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_residual_attention_8x" # 8x down sampling
-        
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
-        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
-        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
-        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
-
-        self.num_vocabs = num_vocabs
-        self.num_classes = num_classes     
-        self.trainable = trainable
-        
-        self.embedding_size = params.embedding_size
-        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
-        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
-        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
-        
-        self.layer_inputs = []        
-        self.setup()
-        
-    
-    def setup(self):        
-        # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
-        
-        # encoder
-        (self.feed('embedding')
-             .conv(3, 5, 64, 1, 1, name='encoder1_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_2')
-             .max_pool(2, 2, 2, 2, name='pool1')
-             .conv(3, 5, 128, 1, 1, name='encoder2_1')
-             .conv(3, 5, 256, 1, 1, name='encoder2_2')
-             .max_pool(2, 2, 2, 2, name='pool2')
[…]

### 2019-04-03 model_cutie_res_att_bert.py

@@ -1,72 +1,0 @@
-# written by Xiaohui Zhao
-# 2018-12 
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-from model_cutie import CUTIE    
-    
-class CUTIERes(CUTIE):
-    def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_residual_attention_bert_8x" # 8x down sampling
-        
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
-        self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
-        self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
-        self.ghm_weights = tf.placeholder(tf.float32, shape=[None, None, None, num_classes], name='ghm_weights')        
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes, 'ghm_weights':self.ghm_weights})
-
-        self.num_vocabs = num_vocabs
-        self.num_classes = num_classes     
-        self.trainable = trainable
-        
-        self.embedding_size = params.embedding_size
-        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
-        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
-        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
-        
-        self.layer_inputs = []    
-        self.embedding_table = None      
-        self.setup()
-        
-    
-    def setup(self):        
-        # input
-        (self.feed('data')
-             .bert_embed(self.num_vocabs, 768, name='embeddings', trainable=False))  
-        
-        # encoder
-        (self.feed('embeddings')
-             .conv(3, 5, 64, 1, 1, name='encoder1_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_2')
-             .max_pool(2, 2, 2, 2, name='pool1')
-             .conv(3, 5, 128, 1, 1, name='encoder2_1')
-             .conv(3, 5, 256, 1, 1, name='encoder2_2')
[…]

### 2019-04-03 model_cutie_sep.py

@@ -1,67 +1,0 @@
-# written by Xiaohui Zhao
-# 2018-12 
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-from model_cutie import CUTIE    
-    
-class CUTIESep(CUTIE):
-    def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_seperatable_residual"
-        
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes})  
-        self.num_vocabs = num_vocabs
-        self.num_classes = num_classes     
-        self.trainable = trainable
-        
-        self.embedding_size = params.embedding_size
-        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0
-        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0
-        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
-        
-        self.layer_inputs = []        
-        self.setup()
-        
-    
-    def setup(self):        
-        # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
-        
-        # encoder
-        (self.feed('embedding')
-             .sepconv(3, 5, 4, 2, name='encoder1_1')
-             .sepconv(3, 5, 4, 2, name='encoder1_2')
-             .conv(3, 5, 128, 1, 1, name='bottleneck1')
-             .max_pool(2, 2, 2, 2, name='pool1')
-             .sepconv(3, 5, 4, 2, name='encoder2_1')
-             .sepconv(3, 5, 4, 2, name='encoder2_2')
-             .conv(3, 5, 256, 1, 1, name='bottleneck2')
-             .max_pool(2, 2, 2, 2, name='pool2')
-             .sepconv(3, 5, 4, 2, name='encoder3_1')
-             .sepconv(3, 5, 4, 2, name='encoder3_2')
-             .conv(3, 5, 512, 1, 1, name='bottleneck3')
-             .max_pool(2, 2, 2, 2, name='pool3')
[…]

### 2019-04-03 model_cutie_unet8.py

@@ -1,73 +1,0 @@
-# written by Xiaohui Zhao
-# 2018-12 
-# xiaohui.zhao@accenture.com
-import tensorflow as tf
-from model_cutie import CUTIE    
-    
-class CUTIEUNet(CUTIE):
-    def __init__(self, num_vocabs, num_classes, params, trainable=True):
-        self.name = "CUTIE_unet_8x" # 8x down sampling
-        
-        self.data = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
-        self.layers = dict({'data': self.data, 'gt_classes': self.gt_classes})  
-        self.num_vocabs = num_vocabs
-        self.num_classes = num_classes     
-        self.trainable = trainable
-        
-        self.embedding_size = params.embedding_size
-        self.weight_decay = params.weight_decay if hasattr(params, 'weight_decay') else 0.0
-        self.hard_negative_ratio = params.hard_negative_ratio if hasattr(params, 'hard_negative_ratio') else 0.0
-        self.batch_size = params.batch_size if hasattr(params, 'batch_size') else 0
-        
-        self.layer_inputs = []        
-        self.setup()
-        
-    
-    def setup(self):        
-        # input
-        (self.feed('data')
-             .embed(self.num_vocabs, self.embedding_size, name='embedding'))  
-        
-        # encoder
-        (self.feed('embedding')
-             .conv(3, 5, 64, 1, 1, name='encoder1_1')
-             .conv(3, 5, 128, 1, 1, name='encoder1_2')
-             .max_pool(2, 2, 2, 2, name='pool1')
-             .conv(3, 5, 128, 1, 1, name='encoder2_1')
-             .conv(3, 5, 256, 1, 1, name='encoder2_2')
-             .max_pool(2, 2, 2, 2, name='pool2')
-             .conv(3, 5, 256, 1, 1, name='encoder3_1')
-             .conv(3, 5, 512, 1, 1, name='encoder3_2')
-             .conv(3, 5, 512, 1, 1, name='encoder3_3')
-             .max_pool(2, 2, 2, 2, name='pool3')
-             .conv(3, 5, 512, 1, 1, name='encoder4_1')
-             .conv(3, 5, 512, 1, 1, name='encoder4_2')
[…]

### 2019-04-03 model_framework.py

@@ -41,7 +41,7 @@ class Model(object):
      
     
     @layer
-    def embed(self, layer_input, vocabulary_size, embedding_size, name, trainable=True):
+    def embed(self, layer_input, vocabulary_size, embedding_size, name, dropout=1, trainable=True):
         with tf.variable_scope(name) as scope:
             init_embedding = tf.random_uniform_initializer(-1.0, 1.0)
             embeddings = self.make_var('weights', [vocabulary_size, embedding_size], init_embedding, None, trainable)
@@ -49,6 +49,7 @@ class Model(object):
             
             reshaped_input = tf.reshape(layer_input, [-1])
             e = tf.nn.embedding_lookup(embeddings, reshaped_input)
+            e = tf.nn.dropout(e, dropout)
             reshaped_e = tf.reshape(e, [shape[0], shape[1], shape[2], embedding_size])
             return reshaped_e
     
@@ -67,8 +68,24 @@ class Model(object):
                 trainable=trainable)
             self.embedding_table = embedding_table # the inherited class need a self.embedding_table variable
             return embedding_output        
+        
     
-     
+    @layer
+    def positional_sampling(self, layer_input, feature_dimension, name='positional_sampling'):
+        featuremap = layer_input[0]
+        batch_indices = layer_input[1]
+        grid = layer_input[2]        
+        
+        shape_grid = tf.shape(grid)
+        
+        featuremap_flat = tf.reshape(featuremap, [shape_grid[0], -1])        
+        batch_indices_flat = tf.reshape(batch_indices, [shape_grid[0], -1])        
+        batch_ps_flat = tf.batch_gather(featuremap_flat, batch_indices_flat)
+        
+        b, h, w, c = shape_grid[0], shape_grid[1], shape_grid[2], feature_dimension
+        return tf.reshape(batch_ps_flat, [b,h,w,c])
+    
+    
     @layer
     def sepconv(self, layer_input, k_h, k_w, cardinality, compression, name, activation='relu', trainable=True):
         """ customized seperable convolution

### 2019-04-03 utils.py

@@ -2,6 +2,7 @@
 # 2018-01 
 # xiaohui.zhao@accenture.com
 import numpy as np
+import csv
 from os.path import join
 try:
     import cv2
@@ -35,7 +36,8 @@ def cal_accuracy(data_loader, grid_table, gt_classes, model_output_val, label_ma
         bbox_id_selected = bbox_id[indexes]
         
         # calculate accuracy
-        #test_classes = [1,2,3,4,5,6,7,8,9]
+        #test_classes = [1,2,3,4,5]
+        #for c in test_classes:
         for c in range(1, data_loader.num_classes):
             labels_indexes = np.where(labels_selected == c)[0]
             logits_indexes = np.where(logits_array_selected[:,c] > c_threshold)[0]
@@ -90,45 +92,61 @@ def cal_accuracy(data_loader, grid_table, gt_classes, model_output_val, label_ma
     return prevalence, accuracy_strict, accuracy_soft, res.encode("utf-8")
 
 
-def cal_save_results(data_loader, save_prefix, docs, grid_table, gt_classes, model_output_val):
+def cal_save_results(data_loader, grid_table, gt_classes, model_output_val, label_mapids, bbox_mapids, file_names, save_prefix):
     res = ''
     num_correct = 0
     num_correct_strict = 0
+    num_correct_soft = 0
     num_all = grid_table.shape[0] * (model_output_val.shape[-1]-1)
     for b in range(grid_table.shape[0]):
-        filename = docs[b][0][0]
+        filename = file_names[0]
         
         data_input_flat = grid_table[b,:,:,0].reshape([-1])
         labels = gt_classes[b,:,:].reshape([-1])
         logits = model_output_val[b,:,:,:].reshape([-1, data_loader.num_classes])
+        label_mapid = label_mapids[b]
+        bbox_mapid = bbox_mapids[b]
+        rows, cols = grid_table.shape[1:3]
+        bbox_id = np.array([row*cols+col for row in range(rows) for col in range(cols)])
         
         # ignore inputs that are not word
         indexes = np.where(data_input_flat != 0)[0]
         data_selected = data_input_flat[indexes]
         labels_selected = labels[indexes]
         logits_array_selected = logits[indexes]
+        bbox_id_selected = bbox_id[indexes]
         
         # calculate accuracy
         for c in range(1, data_loader.num_classes):
             labels_indexes = np.where(labels_selected == c)[0]
[…]

### 2019-04-03 data_loader_json.py
CUTIEv2 first version

@@ -12,7 +12,7 @@ import tensorflow as tf
 import tokenization
 import cv2
 
-DEBUG = False # True to show grid as image 
+DEBUG = True # True to show grid as image 
 
 import unicodedata
 def is_number(s):
@@ -749,9 +749,9 @@ class DataLoader():
             cls = line['field_name']
             if cls in self.classes:
                 label_dressed[file_id][cls] = {'key_id':[], 'value_id':[], 'key_text':'', 'value_text':''} 
-                label_dressed[file_id][cls]['key_id'] = line.get('key_id', [])
+                #label_dressed[file_id][cls]['key_id'] = line.get('key_id', [])
                 label_dressed[file_id][cls]['value_id'] = line['id'] # value_id
-                label_dressed[file_id][cls]['key_text'] = line.get('key_text', []) 
+                #label_dressed[file_id][cls]['key_text'] = line.get('key_text', []) 
                 label_dressed[file_id][cls]['value_text'] = line['text'] # value_text
                 
         # handle corrupted data

### 2019-04-03 main_build_dict.py

@@ -7,11 +7,12 @@ import argparse
 from data_loader_json import DataLoader
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--dict_path', type=str, default='dict/taxi') 
-parser.add_argument('--doc_path', type=str, default='data/taxi') 
+parser.add_argument('--dict_path', type=str, default='dict/table') 
+parser.add_argument('--doc_path', type=str, default='data/table') 
 parser.add_argument('--text_case', type=bool, default=True) # case sensitive
 parser.add_argument('--tokenize', type=bool, default=True) # tokenize input text
 parser.add_argument('--batch_size', type=int, default=32) 
+parser.add_argument('--use_cutie2', type=bool, default=False) 
 params = parser.parse_args()
 
 if __name__ == '__main__':

### 2019-04-03 main_train_json.py

@@ -16,8 +16,8 @@ from model_cutie2_aspp import CUTIE2 as CUTIEv2
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
 # data
-parser.add_argument('--use_cutie2', type=bool, default=False) # True to read image from doc_path 
-parser.add_argument('--doc_path', type=str, default='data/table')
+parser.add_argument('--use_cutie2', type=bool, default=True) # True to read image from doc_path 
+parser.add_argument('--doc_path', type=str, default='data/table_small')
 parser.add_argument('--save_prefix', type=str, default='table', help='prefix for ckpt') # TBD: save log/models with prefix
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
@@ -30,7 +30,7 @@ parser.add_argument('--ckpt_file', type=str, default='meals/CUTIE_highresolution
 
 # dict
 parser.add_argument('--load_dict', type=bool, default=True, help='True to work based on an existing dict') 
-parser.add_argument('--load_dict_from_path', type=str, default='dict/20000TC') # 40000 or 20000TC or 119547
+parser.add_argument('--load_dict_from_path', type=str, default='dict/table') # 40000 or 20000TC or table
 parser.add_argument('--tokenize', type=bool, default=True) # tokenize input text
 parser.add_argument('--text_case', type=bool, default=True) # case sensitive
 parser.add_argument('--update_dict', type=bool, default=False)
@@ -41,7 +41,7 @@ parser.add_argument('--segment_grid', type=bool, default=False) # segment grid i
 parser.add_argument('--rows_segment', type=int, default=72) 
 parser.add_argument('--cols_segment', type=int, default=72) 
 parser.add_argument('--augment_strategy', type=int, default=1) # 1 for increasing grid shape size, 2 for gaussian around target shape
-parser.add_argument('--positional_mapping_strategy', type=int, default=2)
+parser.add_argument('--positional_mapping_strategy', type=int, default=1)
 parser.add_argument('--rows_target', type=int, default=64) 
 parser.add_argument('--cols_target', type=int, default=64) 
 parser.add_argument('--rows_ulimit', type=int, default=80) # used when data augmentation is true
@@ -134,9 +134,9 @@ if __name__ == '__main__':
     data_loader = DataLoader(params, update_dict=params.update_dict, load_dictionary=params.load_dict, data_split=0.75)
     num_words = max(20000, data_loader.num_words)
     num_classes = data_loader.num_classes
-    #for _ in range(2):
[…]

### 2019-04-03 model_cutie2_aspp.py

@@ -62,7 +62,7 @@ class CUTIE2(CUTIE):
              .conv(3, 3, 32, 1, 1, name='image_featuremap'))
          
         # feature map positional mapping
-        (self.feed('image_featuremap', 'ps_1d_indices', 'embedding')
+        (self.feed('image_featuremap', 'ps_1d_indices', 'data_grid')
              .positional_sampling(32, name='positional_sampling'))
          
         ## concate image with grid

### 2019-04-03 model_cutie_aspp.py

@@ -10,6 +10,8 @@ class CUTIERes(CUTIE):
         
         self.data_grid = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='data_grid')
         self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes') 
+        self.data_image = tf.placeholder(tf.float32, shape=[None, None, None, 3], name='data_image') # not used in CUTIEv1
+        self.ps_1d_indices = tf.placeholder(tf.int32, shape=[None, None], name='ps_1d_indices') # not used in CUTIEv1
         
         self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
         self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'

### 2019-04-03 model_framework.py

@@ -78,10 +78,11 @@ class Model(object):
         
         shape_grid = tf.shape(grid)
         
-        featuremap_flat = tf.reshape(featuremap, [shape_grid[0], -1])        
+        featuremap_flat = tf.reshape(featuremap, [shape_grid[0], -1, feature_dimension])        
         batch_indices_flat = tf.reshape(batch_indices, [shape_grid[0], -1])        
         batch_ps_flat = tf.batch_gather(featuremap_flat, batch_indices_flat)
         
+        print(shape_grid)
         b, h, w, c = shape_grid[0], shape_grid[1], shape_grid[2], feature_dimension
         return tf.reshape(batch_ps_flat, [b,h,w,c])
     

### 2019-04-04 Article/ms.tex
CUTIE paper final version

@@
 We further explore the effect of employing different structures of convolutional neural network and propose a fast and portable structure.
-We demonstrate the effectiveness of the proposed method on a dataset with up to $6,980$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than BERT but with only $1/10$ parameters and without requiring the $3,300$M word dataset for pre-training.
+We demonstrate the effectiveness of the proposed method on a dataset with up to $4,484$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than BERT but with only $1/10$ parameters and without requiring the $3,300$M word dataset for pre-training.
 Experimental results also demonstrate that the CUTIE being able to achieve state of the art performance with much smaller amount of training data.
@@
 Both CUTIE-A and CUITE-B conducts semantical meaning encoding process with a word embedding layer in the very beginning stage.
+Dropout is applied on the embedding layer to enhance the CUTIE's generalization ability.
 The cross entropy loss function is applied to compare the predicted token class grid and the ground truth grid.
@@
 	\hline
-	ME & 1109 & 475 & 9 \\
+	ME & 1109 & 375 & 9 \\
 	Taxi & 1125 & 375 & 6 \\
@@
 	BERT\cite{bert} & 110M & 88.1 / - & 80.1 / - & 71.7 / - \\
-	CUTIE-A & 67M & \\
-	CUTIE-B & 14M & 93.3 / 96.9 & 81.0 / 88.9 & 75.8 / 87.1 \\
+	CUTIE-A & 67M & 90.8 / 97.2 & 77.7 / \textbf{91.4} & 69.5 / \textbf{87.8} \\
+	CUTIE-B & 14M & \textbf{94.0} / \textbf{97.3} & \textbf{81.5} / 89.7 & \textbf{74.6} / 87.0 \\
 	%CUTIE-A split & 67M & 92.9 / 96.7 & 81.4 / 91.6 & 72.3 / 95.0 \\
@@
 The BERT model for SROIE is transform learned with the Google released base model that is pre-trained on a huge dataset with $3,300$M words \cite{bert,bertgit}.
-It is worth noting that the CloudScan based method and BERT based method were implemented by other teams.
-For that reason, there is minor difference in numbers of training / test data.
-To provide a fair comparison, we also provide ablation study to evaluate the influence of number of training images in CUTIE.
-We will also provide results generated using the same dataset in the next version of this paper.
+To provide a fair comparison, $4,484$ samples with around $1,500$ each from Taxi, Meals Entertainment (ME), and Hotel, where $3,375$ samples are used for training and $1,125$ are used for testing, as reported in Table \ref{tab:dataset}.
+A single model is trained on the dataset for all these $3$ types of document receipts either for CloudScan, BERT, or CUTIE.
 
@@
 We train our model on Tesla V100 GPU where $11$ to $19$GB memories is used depending the configuration of the model framework and size of the dataset.
-Instance normalization is involved to facilate training.
+Instance normalization and hard negative mining are involved to facilate training.
+Dropout is applied with keep probability of $0.9$.
 Our model is trained end-to-end without piecewise pretraining of any component.
@@
 \subsection{Dataset}
-The dataset contains $6,980$ annotated scanned Spanish receipt documents, including taxi receipts, meals entertainment (ME) receipts, and hotel receipts, with $9$ different key information classes, as reported in Table \ref{tab:dataset}.
+The dataset contains $4,484$ annotated scanned Spanish receipt documents, including taxi receipts, meals entertainment (ME) receipts, and hotel receipts, with $9$ different key information classes.
 We generate the texts and corresponding bounding boxes with Google's OCR API.
@@
 Examples of inference results are illustrated in Figure \ref{fig:result}.
-Our big network CUTIE-A achieves $91.2\%$ AP and $98.1\%$ softAP on taxi receipts, $84.8\%$ AP and $93.5\%$ softAP on meals entertainment receipts, and $62.7\%$ AP and $88.0\%$ softAP on hotel receipts, outperforming other methods in almost all of the test cases.
-Compared to CloudScan, our big network CUTIE-A improves AP by $20.8\%$ AP on meals entertainment receipts, $9.2\%$ on taxi receipt, and $2.7\%$ on hotel receipts; our small network CUTIE-B improves AP by $13.2$ on taxi receipts, $20.3\%$ points on meals entertainment receipts, and $10.8\%$ on hotel receipts.
-Furthermore, compared to BERT, where model is pre-trained on a dataset with $3,300M$ words and transfer learned on our dataset, our big network CUTIE-B improves AP by $4.2\%$ and $4.5\%$ in taxi receipts and meals entertainment while using only $1/2$ parameters, our small network CUTIE-B improves AP by $8.2\%$ and $4.0\%$ in taxi receipts and meals entertainment but with much less complexity and smaller model size with only $1/9$ parameters without requiring a huge dataset for model pretraining.
+Our big network CUTIE-A achieves $90.8\%$ AP and $97.2\%$ softAP on taxi receipts, $77.7\%$ AP and $91.4\%$ softAP on meals entertainment receipts, and $69.5\%$ AP and $87.8\%$ softAP on hotel receipts.
+Compared to CloudScan, CUTIE-A and CUTIE-B outperforms in every single test case.
+Furthermore, compared to BERT, where model is pre-trained on a dataset with $3,300$M words and transfer learned on our dataset, our big network CUTIE-A improves AP by $2.7\%$ AP on taxi receipt but less accurate on other type of documents while using only $1/2$ parameters; our small network CUTIE-B improves AP by $5.9\%$ on taxi receipts, $1.4\%$ points on meals entertainment receipts, and $2.9\%$ on hotel receipts, outperforming other methods in all of the test cases but with much less complexity and smaller model size with only $1/9$ parameters and without requiring a huge dataset for model pretraining.
 We will further prove in Section \ref{parameters} that CUTIE-B is also able to achieve state of the art performance with only $1/10$ of BERT's parameters.
@@
 
-It is worth noting that the difference of AP in the hotel receipt column actually leads to interesting findings.
-One of the finding is that if we neglect the 'VendorName' class in the evaluation criteria, the AP is increased to from $70.8\%$ to $76.9\%$ and the softAP drops to $83.8\%$, indicating that CUTIE is capable of extracting the interested 'VendorName' texts but sometimes involves texts that are not in the ground truth label.
+It is worth noting that the difference of AP and softAP leads to interesting findings.
+One of the finding is that CUTIE is capable of extracting the interested texts but sometimes involves texts that are not in the ground truth.
 Another finding is that the hotel receipts are quite different from the meals entertainment receipts and the taxi receipts, where key information appears multi times in different areas of the receipt, whereas the human labelers tend to label only one of their appearances.
@@
 Typical examples of receipts with low AP but high softAP score are shown in Figure \ref{fig:falsepositive}.
-Most of the false positive cases occur in the 'VenderName' class, where names tend to greatly vary and leads to difficulty in model inference.
+Most of the false positive cases occur in the 'VenderName' class, where names tend to vary greatly and leads to difficulty in model inference.
 However, it is not hard to find that these false positives can be easily avoided by appending a dictionary based post processor to the key information extractor.
@@
 In this section, we perform ablation studies over a number of facets of CUTIE in order to have a better understanding of their relative importance.
-CUTIE-B is employed as the default model with grid augmentation, embedding size of $128$, and $75\%$ of dataset as training data.
+CUTIE-B is employed as the default model with grid augmentation, embedding size of $128$.
+In this section, we use all data of ME, where $75\%$ of them are used train the model and the rest $25\%$ for test.
 
@@
 It is also indicated in the result that too large embedding size also decreases the model performace.
-To further enhance the model performance, it might help to randomly mask out certain texts during the grid positional mapping process, such that the model learns inter-text relationship better with / without certain words present in the grid and further improves in generality.
 

### 2019-04-04 data_loader_json.py

@@ -12,7 +12,7 @@ import tensorflow as tf
 import tokenization
 import cv2
 
-DEBUG = True # True to show grid as image 
+DEBUG = False # True to show grid as image 
 
 import unicodedata
 def is_number(s):
@@ -471,14 +471,37 @@ class DataLoader():
     def _positional_sampling(self, file_names, ps_indices_x, ps_indices_y, updated_cols):
         images, ps_1d_indices = [], []
         
+        ## load image and generate corresponding @ps_1dindices
         max_h, max_w = 0, updated_cols
-        for i in range(len(file_names)): # load image and generate corresponding @ps_1dindices
+        for i in range(len(file_names)):
             file_name = file_names[i]
             file_path = join(self.doc_path, file_name) # TBD: ensure image is upright
             ps_1d_x = np.array(ps_indices_x[i], dtype=np.float32).reshape([-1])
             ps_1d_y = np.array(ps_indices_y[i], dtype=np.float32).reshape([-1])
             
-            image, ps_1d = self._read_image_n_gen_indices(file_path, updated_cols, ps_1d_x, ps_1d_y)   
+            image = cv2.imread(file_path)
+            if image is not None:
+                h, w, _ = image.shape # [h,w,c]
+                factor = max_w / w
+                
+                w *= factor
+                h *= factor
+                ps_1d_x *= factor # TBD: implement more accurate mapping method rather than nearest neighbor, since the .4 or .6 leads to two different sampling results
+                ps_1d_y *= factor                
+                
+                ps_1d = np.int32(np.floor(ps_1d_x) + np.floor(ps_1d_y) * max_w)
+                max_items = w*h - 1
+                for i in range(len(ps_1d)):
+                    if ps_1d[i] > max_items - 1:
+                        ps_1d[i] = max_items - 1
+                    
+                
+                image = cv2.resize(image, (max_w, int(h)))
+                image = (image-127.5) / 255
+            else:
+                print('Warning: {} image not found!'.format(file_path))
+                image, ps_1d = None, None            
+                
             if image is not None and ps_1d is not None: # ignore data with no images                 
                 ps_1d_indices.append(ps_1d)
                 images.append(image)
@@ -488,31 +511,13 @@ class DataLoader():
             else:
                 print('{} ignored due to image file not found.'.format(file_path))
                 
-        for i,image in enumerate(images): # pad image to the same shape
+        ## pad image to the same shape
+        for i,image in enumerate(images): 
[…]

### 2019-04-04 export_data.py

@@ -1,0 +1,201 @@
+import requests
+import argparse
+from requests.auth import HTTPBasicAuth
+import sys
+import json
+import os
+import time
+
+
+def init_args():
+    parser = argparse.ArgumentParser()
+    parser.add_argument('--user', type=str, help='login name', required=True)
+    parser.add_argument('--password', type=str, help='login password', required=True)
+    parser.add_argument('--server', type=str, help='Server path', required=True)
+    parser.add_argument('--project', type=str, help='Project name', required=True)
+    parser.add_argument('--task', type=int, help='Task id', required=True)
+    parser.add_argument('--label', dest='label', help='Download label information', action='store_true')
+    parser.add_argument('--postprocessing', dest='postprocessing', help='Download postprocessing information', action='store_true')
+    parser.add_argument('--source_file', dest='source_file', help='Download source file', action='store_true')
+    parser.add_argument('--quality_file', dest='quality_file', help='Download quality file', action='store_true')
+    parser.add_argument('--engine_raw_result', dest='engine_raw_result', help='Download engine raw result', action='store_true')
+    parser.add_argument('--engine_result', dest='engine_result', help='Download engine result', action='store_true')
+    parser.add_argument('--only_labelled_data', dest='only_labelled_data', action='store_true', default=None)
+    parser.add_argument('--only_unlabelled_data', dest='only_unlabelled_data', action='store_true', default=None)
+    parser.add_argument('--only_valid_data', dest='only_valid_data', action='store_true', default=None)
+    parser.add_argument('--only_invalid_data', dest='only_invalid_data', action='store_true', default=None)
+    return parser.parse_args()
+
+
+def get_engine(api):
+    r = requests.get(api, auth=auth, headers=headers)
+    if r.ok:
+        return json.loads(r.json().get('json_result', '{}')).get('text_boxes')
+    else:
+        print('Download ticket {id} engine info failed.'.format(id=ticket_id))
+        print('Call api: {url}'.format(url=api))
+        print('[Err Reason]:{err}'.format(err=r.reason))
+        print('[Err text]:{err}'.format(err=r.text))
+        return None
+
+
+def download_info(server, project, task_id):
+    params = dict()
+    if args.only_labelled_data is True:
+        params['only_label_info'] = True
+
+    if args.only_unlabelled_data is True:
+        params['only_label_info'] = False
+
+    if args.only_valid_data is True:
+        params['ticket_invalid'] = False
+
[…]

### 2019-04-04 main_evaluate_json.py

@@ -8,26 +8,28 @@ import argparse
 import os, csv
 os.environ["CUDA_VISIBLE_DEVICES"] = "1"
 
-from model_cutie_aspp import CUTIERes
+from model_cutie_aspp import CUTIERes as CUTIEv1
+from model_cutie2_aspp import CUTIE2 as CUTIEv2
 from data_loader_json import DataLoader
 from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--doc_path', type=str, default='data/hotel_small') # modify this
-parser.add_argument('--save_prefix', type=str, default='hotel', help='prefix for load ckpt model') # modify this
+parser.add_argument('--use_cutie2', type=bool, default=True) # True to read image from doc_path 
+parser.add_argument('--doc_path', type=str, default='data/table_small') # modify this
+parser.add_argument('--save_prefix', type=str, default='table', help='prefix for load ckpt model') # modify this
 
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 
 parser.add_argument('--e_ckpt_path', type=str, default='../graph/CUTIE/graph/') # modify this
-parser.add_argument('--ckpt_file', type=str, default='CUTIE_atrousSPP_d20000c9(r80c80)_iter_40000.ckpt')
-parser.add_argument('--positional_mapping_strategy', type=int, default=2)
+parser.add_argument('--ckpt_file', type=str, default='CUTIE2_atrousSPP_d20000c2(r80c80)_iter_1201.ckpt')
+parser.add_argument('--positional_mapping_strategy', type=int, default=1)
 parser.add_argument('--rows_target', type=int, default=80)  
 parser.add_argument('--cols_target', type=int, default=80) 
 parser.add_argument('--rows_ulimit', type=int, default=80) 
 parser.add_argument('--cols_ulimit', type=int, default=80) 
 
 parser.add_argument('--load_dict', type=bool, default=True, help='True to work based on an existing dict') 
-parser.add_argument('--load_dict_from_path', type=str, default='dict/20000TC') # 40000 or 119547 or 20000TC
+parser.add_argument('--load_dict_from_path', type=str, default='dict/table') # 40000 or table or 20000TC
 parser.add_argument('--tokenize', type=bool, default=True) # tokenize input text
 parser.add_argument('--text_case', type=bool, default=True) # case sensitive
[…]

### 2019-04-04 model_cutie_hr.py

@@ -8,8 +8,11 @@ class CUTIERes(CUTIE):
     def __init__(self, num_vocabs, num_classes, params, trainable=True):
         self.name = "CUTIE_highresolution_8x" # 8x down sampling
         
-        self.data_grid = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='grid_table')
-        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes')
+        self.data_grid = tf.placeholder(tf.int32, shape=[None, None, None, 1], name='data_grid')
+        self.gt_classes = tf.placeholder(tf.int32, shape=[None, None, None], name='gt_classes') 
+        self.data_image = tf.placeholder(tf.float32, shape=[None, None, None, 3], name='data_image') # not used in CUTIEv1
+        self.ps_1d_indices = tf.placeholder(tf.int32, shape=[None, None], name='ps_1d_indices') # not used in CUTIEv1
+        
         self.use_ghm = tf.equal(1, params.use_ghm) if hasattr(params, 'use_ghm') else tf.equal(1, 0) #params.use_ghm 
         self.activation = 'sigmoid' if (hasattr(params, 'use_ghm') and params.use_ghm) else 'relu'
         self.dropout = params.data_augmentation_dropout if hasattr(params, 'data_augmentation_dropout') else 1

### 2019-04-04 model_framework.py

@@ -82,7 +82,6 @@ class Model(object):
         batch_indices_flat = tf.reshape(batch_indices, [shape_grid[0], -1])        
         batch_ps_flat = tf.batch_gather(featuremap_flat, batch_indices_flat)
         
-        print(shape_grid)
         b, h, w, c = shape_grid[0], shape_grid[1], shape_grid[2], feature_dimension
         return tf.reshape(batch_ps_flat, [b,h,w,c])
     

### 2019-04-04 data_loader_json.py
CUTIEv2 gather bug fixed

@@ -484,19 +484,18 @@ class DataLoader():
                 h, w, _ = image.shape # [h,w,c]
                 factor = max_w / w
                 
-                w *= factor
-                h *= factor
+                h = int(h*factor)
                 ps_1d_x *= factor # TBD: implement more accurate mapping method rather than nearest neighbor, since the .4 or .6 leads to two different sampling results
                 ps_1d_y *= factor                
                 
                 ps_1d = np.int32(np.floor(ps_1d_x) + np.floor(ps_1d_y) * max_w)
-                max_items = w*h - 1
+                max_items = max_w * h - 1
                 for i in range(len(ps_1d)):
                     if ps_1d[i] > max_items - 1:
                         ps_1d[i] = max_items - 1
                     
                 
-                image = cv2.resize(image, (max_w, int(h)))
+                image = cv2.resize(image, (max_w, h))
                 image = (image-127.5) / 255
             else:
                 print('Warning: {} image not found!'.format(file_path))

### 2019-04-04 main_evaluate_json.py

@@ -14,14 +14,14 @@ from data_loader_json import DataLoader
 from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--use_cutie2', type=bool, default=True) # True to read image from doc_path 
+parser.add_argument('--use_cutie2', type=bool, default=False) # True to read image from doc_path 
 parser.add_argument('--doc_path', type=str, default='data/table_small') # modify this
 parser.add_argument('--save_prefix', type=str, default='table', help='prefix for load ckpt model') # modify this
 
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 
 parser.add_argument('--e_ckpt_path', type=str, default='../graph/CUTIE/graph/') # modify this
-parser.add_argument('--ckpt_file', type=str, default='CUTIE2_atrousSPP_d20000c2(r80c80)_iter_1201.ckpt')
+parser.add_argument('--ckpt_file', type=str, default='CUTIE_atrousSPP_d20000c2(r80c80)_iter_1801.ckpt')
 parser.add_argument('--positional_mapping_strategy', type=int, default=1)
 parser.add_argument('--rows_target', type=int, default=80)  
 parser.add_argument('--cols_target', type=int, default=80) 
@@ -89,7 +89,7 @@ if __name__ == '__main__':
                 }
             fetches = [model_output]
             
-            if data['file_name'][0] != '000009704366_CLMREC_2-1.png':
+            if data['file_name'][0] != '000009682304_CLMREC_9-5.png':
                 continue
             print(data['file_name'][0])
             print(data['grid_table'].shape, data['data_image'].shape, data['ps_1d_indices'].shape)
@@ -111,9 +111,9 @@ if __name__ == '__main__':
             shape = data['shape']
             file_name = data['file_name'][0] # use one single file_name
             bboxes = data['bboxes'][file_name]
-#             vis_bbox(data_loader, params.doc_path, np.array(data['grid_table'])[0], 
-#                      np.array(data['gt_classes'])[0], np.array(model_output_val)[0], file_name, 
-#                      np.array(bboxes), shape)
+            vis_bbox(data_loader, params.doc_path, np.array(data['grid_table'])[0], 
+                     np.array(data['gt_classes'])[0], np.array(model_output_val)[0], file_name, 
+                     np.array(bboxes), shape)
 
         recall = sum(recalls) / len(recalls)
         acc_strict = sum(accs_strict) / len(accs_strict)

### 2019-05-24 Article/ms.tex
article updated

@@
 \author{
-  Xiaohui Zhao, Zhuo Wu, and Xiaoguang Wang \\
+  Xiaohui Zhao, Zhuo Wu, Endi Niu, and Xiaoguang Wang \\
   New IT Accenture \\
-{\tt\small xh.zhao@outlook.com zhuo.wu@accenture.com danny.x.wang@accenture.com}
+{\tt\small xh.zhao@outlook.com zhuo.wu@accenture.com henryniu14@gmail.com danny.x.wang@accenture.com}
 % Additional authors and addresses can be added with ``\and'',
@@
 We further explore the effect of employing different structures of convolutional neural network and propose a fast and portable structure.
-We demonstrate the effectiveness of the proposed method on a dataset with up to $4,484$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than BERT but with only $1/10$ parameters and without requiring the $3,300$M word dataset for pre-training.
-Experimental results also demonstrate that the CUTIE being able to achieve state of the art performance with much smaller amount of training data.
+We demonstrate the effectiveness of the proposed method on a dataset with up to $4,484$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than the BERT for NER but with only $1/10$ parameters and without requiring the $3,300$M word dataset for pre-training.
+Experimental results also demonstrate that the proposed CUTIE model being able to achieve the state of the art performance with a much smaller amount of training data.
 \end{abstract}
@@
 
-Implementing Scanned receipts OCR and information extraction (SROIE) is of great benefit to services and applications such as efficient archiving, compliance check, and fast indexing in the document-intensive streamline processes of office automation in areas that includes but not limit to accounting, financial, and taxation areas.
+Implementing Scanned receipts OCR and information extraction (SROIE) is of great benefit to services and applications such as efficient archiving, compliance check, and fast indexing in the document-intensive streamline processes of office automation in areas that includes but not limited to accounting, financial, and taxation areas.
 There are two specific tasks involved in SROIE: receipt OCR and key information extraction.
 In this work, we focus on the second task that is rare in published research.
-In fact, key information extraction faces big challenges, where different types of document structures and vast number of potential interested key words introduces great difficulties.
-Although the commonly used rule-based method can be implemented with carefully designed expert rules, it can only work on specific type of documents and takes no lesser effort to adapt to new type of documents.
-Therefore, it is desirable to have a learning-based key information extraction method with limited requirement of human resources and solely employing the deep learning technique without designing expert rules for any specific type of documents.
+In fact, key information extraction faces big challenges, where different types of document structures and the vast number of potential interested key words introduces great difficulties.
+Although the commonly used rule-based method can be implemented with carefully designed expert rules, it can only work on certain specific type of documents and takes no lesser effort to adapt to new type of documents.
+Therefore, it is desirable to have a learning-based key information extraction method with limited requirement of human resources and solely employing the deep learning technique without designing an expert rule for any specific type of documents.
 
@@
 However, the NER models were not originally designed to solve the key information extraction problem in SROIE.
-To employ NER models, text words in the original document are aligned as a long paragraph in line-based rule.
+To employ NER models, text words in the original document are aligned as a long paragraph based on a line-based rule.
 In fact, documents, such as receipts and invoices, present with various styles of layouts that were designed for different scenarios or from different enterprise entities.
 The order or word-to-word distance of the texts in the line-base-aligned long paragraph tend to vary greatly due to layout variations, which is difficult to be handled with the natural language oriented methods.
-Typical example of documents with different layouts are illustrated in Fig.
+Typical Examples of documents with different layouts are illustrated in Fig.
 \ref{fig:receipts}.
@@
 \ref{fig:cutie}.
-The gridded texts is formed with the proposed grid positional mapping method, where the grid is generated with the principle that is preserving texts’ relative spatial relationship in the original scanned document image.
+The gridded texts are formed with the proposed grid positional mapping method, where the grid is generated with the principle that is preserving texts’ relative spatial relationship in the original scanned document image.
 The rich semantic information is encoded from the gridded texts at the very beginning stage of the convolutional neural network with a word embedding layer.
@@
 Several rule-based invoice analysis systems were proposed in \cite{3,5,7}.
-Intellix by DocuWare requires the a template being annotated with relevant fields \cite{3}.
+Intellix by DocuWare requires a template being annotated with relevant fields \cite{3}.
 For that reason, a collection of templates have to be constructed.
@@
 Firstly, N-grams features are formed by connecting expert designed rules calculated results on texts of each document line.
-Then, the features are feed to train a RNN-based or a logistic regression based classifier for key information extraction.
-Certain post-processing are added to further enhance extraction results.
-However, the line-based feature extraction method can not achieve its best performance if document texts are not perfectly aligned in line.
-Moreover, the RNN-based classifier, bi-directional LSTM model in CloudScan, has limited ability to learn relationship among distant words.
+Then, the features are fed to train a RNN-based or a logistic regression based classifier for key information extraction.
+Certain post-processings are added to further enhance the extraction results.
+However, the line-based feature extraction method can not achieve its best performance when document texts are not perfectly aligned.
+Moreover, the RNN-based classifier, bi-directional LSTM model in CloudScan, has limited ability to learn the relationship among distant words.
 
 Bidirectional Encoder Representations from Transformers (BERT) is a recently proposed model that is pre-trained on a huge dataset and can be fine-tuned for a specific task, including Named Entity Recognition (NER), which outperforms most of the state of the art results in several NLP tasks \cite{bert}.
-Since the previous learning based methods treats the key information extraction problem as a NER problem, applying BERT can achieve better result than bi-LSTM in CloudScan.
+Since the previous learning based methods treat the key information extraction problem as a NER problem, applying BERT can achieve a better result than the bi-LSTM in CloudScan.
 
@@
 \ref{cy}, separately.
-Furthermore, to enhance the capability of CUTIE to better handle documents with different layouts, we augment the grid data to shapes with different rows and columns by random sampling a Gaussian distribution for with probability
+Furthermore, to enhance the capability of CUTIE to better handle documents with different layouts, we augment the grid data to shapes with different rows and columns by random sampling a Gaussian distribution with probability
 
@@
 In fact, we had experimented with various types of model structures and only detail two of them here to avoid being a tedious paper.
-Specifically, the proposed CUTIE-A is a high capacity convolutional neural network that fuses multi-resolution features without losing high-resolution features, the proposed CUTIE-B is a convolutional network with atrous convolution for enlarging field of view and Atrous Spatial Pyramid Pooling (ASPP) module to capture multi-scale contexts.
+Specifically, the proposed CUTIE-A is a high capacity convolutional neural network that fuses multi-resolution features without losing high-resolution features, the proposed CUTIE-B is a convolutional network with atrous convolution for enlarging the field of view and Atrous Spatial Pyramid Pooling (ASPP) module to capture multi-scale contexts.
 
@@
 \end{equation}
-where $r$ is the atrous rate that indicates the sampling stride of the input signal, which is implemented as convolving the input feature with up sampled filters by inserting $r-1$ zeros between two consecutive filter values along each spatial dimension.
+where $r$ is the atrous rate that indicates the sampling stride of the input signal, which is implemented as convolving the input feature with upsampled filters by inserting $r-1$ zeros between two consecutive filter values along each spatial dimension.
 Standard convolution is a special case of atrous convolution with $r=1$ \cite{deeplabv1}.
@@
 SoftAP is important since it indicates model's capability of extracting correct key information with tolerance of incorporating certain false positives.
-In fact, post processing can be employed to eliminate the false positives.
+In fact, post processings can be employed to eliminate the false positives.
 Therefore, joint analysis of AP and softAP provides a better understanding of the model performance.
@@
 The training is terminated within $40,000$ steps with batch size of $32$.
-We train our model on Tesla V100 GPU where $11$ to $19$GB memories is used depending the configuration of the model framework and size of the dataset.
+We train our model on Tesla V100 GPU where $11$ to $19$GB memories is used depending on the configuration of the model framework and size of the dataset.
 Instance normalization and hard negative mining are involved to facilate training.
@@
 The dataset is split as training set and test set with ratio of $75:25$.
-No pre-processing or post-processing are involved in CUTIE.
+Neither pre-processing nor post-processing is involved in CUTIE.
 
@@
 The result is perfectly correct as if the filled rectangles overlap with the boundary-only rectangles.
-We mask out certain personal information with filled gray rectangle in the figure.}
+We mask out certain private information with filled gray rectangles in the figure.}
 \label{fig:result}
@@
 
-The dataset in this work is much more difficult than the neat scanned document images, since various layouts of receipts were captured in different scenarios using ordinary mobile phone camera.
-Examples of the scanned document images in our dataset are illustrated in Figure \ref{fig:receipts}, note that the colored rectangles is only for visual reference and the actual labelled data is in token-level rather than the line-level that is shown in the figure.
+The dataset in this work is much more difficult than the neat scanned document images, since various layouts of receipts were captured in different scenarios with mobile phones.
+Examples of the scanned document images in our dataset are illustrated in Figure \ref{fig:receipts}, note that the colored rectangles are only for visual reference and the actual labelled data are in token-level rather than the line-level as shown in the figure.
 
@@
 We report results of our method in terms of AP and compare with other state of the art methods in Table \ref{tab:comparison}.
-We also provides softAP results for CUTIE-A and CUTIE-B in Table \ref{tab:comparison}, where both the softAP of CUTIE-A and CUTIE-B exceeds their AP by a large margin.
+We also provide softAP results for CUTIE-A and CUTIE-B in Table \ref{tab:comparison}, where both the softAP of CUTIE-A and CUTIE-B exceeds their AP by a large margin.
 Examples of inference results are illustrated in Figure \ref{fig:result}.
@@
 Compared to CloudScan, CUTIE-A and CUTIE-B outperforms in every single test case.
-Furthermore, compared to BERT, where model is pre-trained on a dataset with $3,300$M words and transfer learned on our dataset, our big network CUTIE-A improves AP by $2.7\%$ AP on taxi receipt but less accurate on other type of documents while using only $1/2$ parameters; our small network CUTIE-B improves AP by $5.9\%$ on taxi receipts, $1.4\%$ points on meals entertainment receipts, and $2.9\%$ on hotel receipts, outperforming other methods in all of the test cases but with much less complexity and smaller model size with only $1/9$ parameters and without requiring a huge dataset for model pretraining.
+Furthermore, compared to BERT, which is pre-trained on a dataset with $3,300$M words and transfer learned on our dataset, our big network CUTIE-A improves AP by $2.7\%$ AP on taxi receipts but less accurate on other type of documents while using only $1/2$ parameters; our small network CUTIE-B improves AP by $5.9\%$ on taxi receipts, $1.4\%$ points on meals entertainment receipts, and $2.9\%$ on hotel receipts, outperforming other methods in all of the test cases but with much less complexity and smaller model size with only $1/9$ parameters and without requiring a huge dataset for model pretraining.
 We will further prove in Section \ref{parameters} that CUTIE-B is also able to achieve state of the art performance with only $1/10$ of BERT's parameters.
 Although CUTIE-B is smaller in capacity, it outperforms CUTIE-A in several assessment criterias.
-This is because CUTIE-B enlarges field of view by employing the atrous convolution rather than the pooling or striding processes, the CUTIE-B model has larger field of view and better understanding of tokens' relative spatial relationship since no restrictions is applied on the feature maps shapes.
+This is because CUTIE-B enlarges the field of view by employing the atrous convolution rather than the pooling or striding processes, the CUTIE-B model has a larger field of view and better understanding of tokens' relative spatial relationship since no restriction is applied on the feature maps shapes.
 
 It is worth noting that the difference of AP and softAP leads to interesting findings.
-One of the finding is that CUTIE is capable of extracting the interested texts but sometimes involves texts that are not in the ground truth.
+One of the findings is that CUTIE is capable of extracting the interested texts but sometimes involves texts that are not in the ground truth.
 Another finding is that the hotel receipts are quite different from the meals entertainment receipts and the taxi receipts, where key information appears multi times in different areas of the receipt, whereas the human labelers tend to label only one of their appearances.
@@
 The false positives are results with the boundary-only rectangles being not overlapped with the filled rectangles.
-We mask out certain personal information with filled gray rectangle in the figure.}
+We mask out certain private information with filled gray rectangles in the figure.}
 \label{fig:falsepositive}
@@
 
-Furthermore, we find that some wrong cases are actually correct since the ground truth were wrongly labelled by the human labelers.
+Furthermore, we find that some wrong cases are actually correct since the ground truths were wrongly labelled by the human labelers.
 As illustrated in Figure \ref{fig:falselabel}, the 'VendorName' appears twice in the scanned image but only being labelled once in both the first and second receipt in the first row, while the model correctly interprets both occurance as the 'VendorName' in the first receipt and correctly interprets the second occurance in the second receipt.
-Furthermore, 'TaxRate' is neglected to be labeled in the third receipt in the first row and 'VendorName' is wrongly labelled in the first receipt in the second row.
+Furthermore, 'TaxRate' is neglected to be labelled in the third receipt in the first row and 'VendorName' is wrongly labelled in the first receipt in the second row.
 The third receipt in the second row and the first and second receipt in the third row are all neglected with labelling 'TaxRate', and the third receipt in the third row is neglected with labelling 'BaseAmount' while the trained model correctly inferred the right class.
@@
 \end{center}
-   \caption{False positive examples of CUITE prediction results, where the error is actually caused by the wrong labelling of human labeler.
+   \caption{False labelling examples of CUITE prediction results, where the error is actually caused by the wrong labelling of human labeler.
 Color legend in the top-left corner indicates the key information classes.
 Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
-We mask certain personal information with filled gray rectangle in the figure.}
+We mask out certain private information with filled gray rectangles in the figure.}
 \label{fig:falselabel}
@@
 CUTIE-B is employed as the default model with grid augmentation, embedding size of $128$.
-In this section, we use all data of ME, where $75\%$ of them are used train the model and the rest $25\%$ for test.
+In this section, we use all data of ME, where $75\%$ of them are used to train the model and the rest $25\%$ for test.
 
 \subsubsection{Effect of Grid Augmentation on Understanding Spatial Information}
-One of our core claim is that the high performance CUTIE is achieved by jointly analysis of the semantical and spatial information with the proposed framework.
+One of our core claims is that the high performance CUTIE is achieved by jointly analysis of the semantical and spatial information with the proposed framework.
 The highly effective spatial analysis ability is enabled by the CUTIE framework in contrast with the previous NER based methods.
@@
 One interesting finding is that the CUTIE model achieves good performance even with limited semantical information capacity.
-We infer the reason is that, for the SROIE problem with 9 key information classes, there are a small amount of key tokens provide the majority of contribution to the model inference and the model can achieve good performance by paying special attention to these key tokens.
-It is also indicated in the result that too large embedding size also decreases the model performace.
+We infer the reason is that, for the SROIE problem with 9 key information classes, there is a small amount of key token providing the majority contribution to the model inference and the model can achieve good performance by paying special attention to these key tokens.
+It is also indicated in the result that too large embedding size also decreases the model performance.
 
 \subsubsection{Impact of Number of Training Samples}
-To evaluate the impact of different number of training samples on model performance, we train CUTIE with $3\%$, $12\%$, $21\%$, $30\%$, $39\%$, $48\%$, $57\%$, $66\%$, and $75\%$ of our dataset and report results in Table \ref{tab:samples}.
+To evaluate the impact of using different number of training samples on model performance, we train CUTIE with $3\%$, $12\%$, $21\%$, $30\%$, $39\%$, $48\%$, $57\%$, $66\%$, and $75\%$ of our dataset and report results in Table \ref{tab:samples}.
 It is not hard to find from the result that more training data leads to better performance either in terms of AP or softAP.
 CUTIE-B achieves the highest AP $85.0\%$ with $66\%$ of dataset as training samples and the highest softAP $91.5\%$ with $75\%$ of dataset as training samples.
-It is worth noting that CUTIE-B is already capable of achieving $79.6\%$ AP and $88.7\%$ softAP with only $21\%$ of dataset as training samples, which further proves the efficiency of the proposed method being capable of achieving good results with limited amount of training data.
+It is worth noting that CUTIE-B is already capable of achieving $79.6\%$ AP and $88.7\%$ softAP with only $21\%$ of dataset as training samples, which further proves the efficiency of the proposed method being capable of achieving good results with a limited amount of training data.
+
+\subsubsection{Other Experiments}
+Here, we introduce another dataset with $613$ image samples where a text token is labelled with whether it is contained in a table region or not and which table column it belongs to.
+To test the performance of the proposed method on different tasks, two CUTIE-B models are trained, one for locating the table region in document images and another one for identifying the specific column that the token belongs to.
+$463$ samples are used for training and $150$ samples for testing.
+For the table region locating test, experimental results shows that $86\%$ tables are perfectly located, where most of the error cases are due to incorrectly incorporting tokens that not belong to the true table region, as illustrated in Figure \ref{fig:table}.
+For the column identifying test, $94.8\%$ tokens are perfectly inferenced, as illustrated in Figure \ref{fig:column}.
+\begin{figure}
+\begin{center}
+\subfloat{\includegraphics[width=0.31\linewidth]{table_3.png}} 
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.31\linewidth]{table_2.png}} 
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.31\linewidth]{table_1.png}} 
+\end{center}
+   \caption{Locating the table region with CUTIE-B.
+Table tokens are indicated with yellow bounding boxes and table region is indicated with pink boxes, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
+We mask out certain private information with filled red rectangles in the figure.}
+\label{fig:table}
+\end{figure}
+\begin{figure}
+\begin{center}
+\subfloat{\includegraphics[width=0.31\linewidth]{column_0.png}} 
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.31\linewidth]{column_3.png}} 
+\subfloat{\fcolorbox{white}{white}{}}
+\subfloat{\includegraphics[width=0.31\linewidth]{column_4.png}} 
+\end{center}
+   \caption{Identifying column tokens with CUTIE-B.
+Color legend in the top-left corner indicates the column id, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
+We mask out certain private information with filled red rectangles in the figure.}
+\label{fig:column}
+\end{figure}
 
@@
 Finally, inference output is achieved through a $1\times1$ convolution.
-\begin{table}[H]
+\begin{table*}
 	\caption{Structure of the proposed CUTIE-B model. }
@@
 	\label{tab:cutie}
-\end{table}
+\end{table*}
 

### 2019-05-24 data_loader_json.py

@@ -37,7 +37,8 @@ class DataLoader():
         self.random = False
         self.data_laundry = False
         self.encoding_factor = 1 # ensures the size (rows/cols) of grid table compat with the network
-        self.classes = ['DontCare', 'Table']
+        #self.classes = ['DontCare', 'Table']
+        self.classes = ['DontCare', 'Column0', 'Column1', 'Column2', 'Column3', 'Column4', 'Column5']
         #self.classes = ['DontCare', 'Column']
         #self.classes = ['DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', 'TaxRate']
         
@@ -236,10 +237,29 @@ class DataLoader():
             else:
                 break
             
-        def build_gt_pyramid(self):
-            rate = self.encoding_factor
+        def build_gt_pyramid(self, gt_classes):
+            gt_classes = np.array(gt_classes)
+            
+            rate = 4 # self.pooling_factor
+            b, h, w = np.shape(gt_classes)
+            same_padding_left = (rate-w%rate)//2 if w%rate else 0
+            same_padding_right = rate-(rate-w%rate)//2 if w%rate else 0
+            same_padding_top = (rate-h%rate)//2 if h%rate else 0
+            same_padding_bottom = rate-(rate-h%rate)//2 if h%rate else 0
             for gt_class in gt_classes:
-                pass
+                pad_v =  np.pad(gt_class, ((same_padding_top, same_padding_bottom), (0,0)), 'constant', constant_values=((0,0),(0,0)))
+                pad_h =  np.pad(gt_class, ((0,0), (same_padding_left, same_padding_right)), 'constant', constant_values=((0,0),(0,0)))
+                
+                ## find mask range for each single entity
+                num_entities = np.max(gt_classes) / self.num_classes
+                entity_ranges = [[] for _ in range(0,num_entities)]
+                for i in range(1, num_entities):
+                    if i % self.num_classes: # only consider non <DontCare> classes
+                        range_y, range_x = np.where(gt_classes==i)
+                        # entity_ranges[i] = [top, left, bottom, right, height, width]
+                        entity_ranges[i] = [min(range_y), min(range_x), max(range_y), max(range_x), 
+                                            max(range_y) - min(range_y), max(range_x) - min(range_x)] 
+                           
                 
         
[…]

### 2019-05-24 helper.py

@@ -1,23 +1,44 @@
 import requests
 import argparse
 import sys
-import os, re
+import os, re, json
 import time
 
+# if __name__ == "__main__":
+#     src = '/Users/xiaohui.zhao/workspace/CUTIE/hotel_imgs/'
+#     dst = '/Users/xiaohui.zhao/workspace/data/CUTIE/mixed_true_even/train_hotel'
+#     json_files = {}
+#     for dirpath,dirnames,filenames in os.walk(dst):
+#         for filename in filenames:
+#             file = re.split(r'\.', filename)[0]
+#             file_path = os.path.join(dirpath,filename)
+#             json_files.update({file: file_path})    
+#     
+#     files = []
+#     for dirpath,dirnames,filenames in os.walk(src):
+#         for filename in filenames:
+#             #file = os.path.join(dirpath,filename)
+#             file = re.split(r'\.', filename)[0]
+#             if file in json_files:
+#                 os.system('cp '+ os.path.join(dirpath,filename) + ' ' + dst)
+
 if __name__ == "__main__":
-    src = '/Users/xiaohui.zhao/workspace/CUTIE/hotel_imgs/'
-    dst = '/Users/xiaohui.zhao/workspace/data/CUTIE/mixed_true_even/train_hotel'
+    src = '/Users/xiaohui.zhao/workspace/data/CUTIE/column_identity'
+    dst = '/Users/xiaohui.zhao/workspace/data/CUTIE/column'
     json_files = {}
-    for dirpath,dirnames,filenames in os.walk(dst):
-        for filename in filenames:
-            file = re.split(r'\.', filename)[0]
-            file_path = os.path.join(dirpath,filename)
-            json_files.update({file: file_path})    
-    
-    files = []
     for dirpath,dirnames,filenames in os.walk(src):
         for filename in filenames:
-            #file = os.path.join(dirpath,filename)
-            file = re.split(r'\.', filename)[0]
-            if file in json_files:
-                os.system('cp '+ os.path.join(dirpath,filename) + ' ' + dst)
+            file_path = os.path.join(dirpath,filename)      
+            if file_path[-3:] == 'png':
+                continue    
+            with open(file_path, encoding='utf-8') as f:
+                data = json.load(f)
+                print(len(data['fields']))
+                for i in range(len(data['fields'])):
+                    data['fields'][i]['field_name'] = 'Column{}'.format(i)
+                    
+            target_path = os.path.join(dst,filename)     
[…]

### 2019-05-24 main_evaluate_json.py

@@ -15,14 +15,15 @@ from utils import *
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
 parser.add_argument('--use_cutie2', type=bool, default=False) # True to read image from doc_path 
-parser.add_argument('--doc_path', type=str, default='data/table_small') # modify this
-parser.add_argument('--save_prefix', type=str, default='table', help='prefix for load ckpt model') # modify this
+parser.add_argument('--is_table', type=bool, default=False) # True to read image from doc_path 
+parser.add_argument('--doc_path', type=str, default='data/column_small') # modify this
+parser.add_argument('--save_prefix', type=str, default='column', help='prefix for load ckpt model') # modify this
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 
 parser.add_argument('--e_ckpt_path', type=str, default='../graph/CUTIE/graph/') # modify this
-parser.add_argument('--ckpt_file', type=str, default='CUTIE_atrousSPP_d20000c2(r80c80)_iter_40000.ckpt')
+parser.add_argument('--ckpt_file', type=str, default='CUTIE_atrousSPP_d20000c7(r80c80)_iter_40000.ckpt')
 parser.add_argument('--positional_mapping_strategy', type=int, default=1)
 parser.add_argument('--rows_target', type=int, default=80)  
 parser.add_argument('--cols_target', type=int, default=80) 
@@ -45,7 +46,7 @@ params = parser.parse_args()
 if __name__ == '__main__':
     # data
     #data_loader = DataLoader(params, True, True) # True to use 25% training data
-    data_loader = DataLoader(params, update_dict=False, load_dictionary=True, data_split=0) # False to provide a path with only test data
+    data_loader = DataLoader(params, update_dict=False, load_dictionary=True, data_split=0.75) # False to provide a path with only test data
     num_words = max(20000, data_loader.num_words)
     num_classes = data_loader.num_classes
 
@@ -98,9 +99,14 @@ if __name__ == '__main__':
             timer_stop = timeit.default_timer()
             print('\t >>time per step: %.2fs <<'%(timer_stop - timer_start))
                 
-            recall, acc_strict, acc_soft, res = cal_accuracy(data_loader, np.array(data['grid_table']), 
-                                                   np.array(data['gt_classes']), model_output_val, 
-                                                   np.array(data['label_mapids']), data['bbox_mapids'])                  
+            if not params.is_table:
[…]

### 2019-05-24 model_framework.py

@@ -302,7 +302,7 @@ class Model(object):
         
     
     @layer
-    def max_pool(self, layer_input, k_h, k_w, s_h, s_w, name, padding='VALID'):
+    def max_pool(self, layer_input, k_h, k_w, s_h, s_w, name, padding='SAME'):
         return tf.nn.max_pool(layer_input, [1,k_h,k_w,1], [1,s_h,s_w,1], name=name, padding=padding)
     
     

### 2019-05-24 utils.py

@@ -260,3 +260,130 @@ def vis_bbox(data_loader, file_prefix, grid_table, gt_classes, model_output_val,
         cv2.imwrite('results/' + file_name[:-4]+'.png', img)        
         cv2.imshow("test", img)
         cv2.waitKey(0)
+        
+
+def cal_accuracy_table(data_loader, grid_table, gt_classes, model_output_val, label_mapids, bbox_mapids):
+    #num_tp = 0
+    #num_fn = 0
+    res = ''
+    num_correct = 0
+    num_correct_strict = 0
+    num_correct_soft = 0
+    num_all = grid_table.shape[0] * (model_output_val.shape[-1]-1)
+    for b in range(grid_table.shape[0]):
+        data_input_flat = grid_table[b,:,:,0]
+        rows, cols = grid_table.shape[1:3]
+        labels = gt_classes[b,:,:]
+        logits = model_output_val[b,:,:,:].reshape([rows, cols, data_loader.num_classes])
+        label_mapid = label_mapids[b]
+        bbox_mapid = bbox_mapids[b]
+        bbox_id = np.array([row*cols+col for row in range(rows) for col in range(cols)])
+        
+        # calculate accuracy
+        #test_classes = [1,2,3,4,5]
+        #for c in test_classes:
+        for c in range(1, data_loader.num_classes):
+            label_rows, label_cols = np.where(labels == c)
+            logit_rows, logit_cols = np.where(logits[:,:,c] > c_threshold)
+            if min(label_rows) == min(logit_rows) and max(label_cols) == max(logit_cols):
+                num_correct_strict += 1
+                num_correct_soft += 1
+                num_correct += 1
+            if min(label_rows) > min(logit_rows) and max(label_cols) < max(logit_cols):
+                num_correct_soft += 1
+                num_correct += 1
+            
+    prevalence = num_correct / num_all
+    accuracy_strict = num_correct_strict / num_all
+    accuracy_soft = num_correct_soft / num_all
+    return prevalence, accuracy_strict, accuracy_soft, res.encode("utf-8")
+
+
+def vis_table(data_loader, file_prefix, grid_table, gt_classes, model_output_val, file_name, bboxes, shape):
+    data_input_flat = grid_table.reshape([-1])
+    labels = gt_classes.reshape([-1])
+    logits = model_output_val.reshape([-1, data_loader.num_classes])
[…]

### 2019-06-18 Article/ms.tex
final version

@@
 \author{
-  Xiaohui Zhao, Zhuo Wu, Endi Niu, and Xiaoguang Wang \\
+  Xiaohui Zhao, Endi Niu, Zhuo Wu, and Xiaoguang Wang \\
   New IT Accenture \\
-{\tt\small xh.zhao@outlook.com zhuo.wu@accenture.com henryniu14@gmail.com danny.x.wang@accenture.com}
+{\tt\small xh.zhao@outlook.com henryniu14@gmail.com zhuo.wu@accenture.com danny.x.wang@accenture.com}
 % Additional authors and addresses can be added with ``\and'',
@@
 We demonstrate the effectiveness of the proposed method on a dataset with up to $4,484$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than the BERT for NER but with only $1/10$ parameters and without requiring the $3,300$M word dataset for pre-training.
-Experimental results also demonstrate that the proposed CUTIE model being able to achieve the state of the art performance with a much smaller amount of training data.
+Experimental results also demonstrate that the proposed CUTIE model being able to achieve the state of the art performance in terms of either speed and accuracy with a much smaller amount of training data.
 \end{abstract}
@@
 We provide two colored rectangles to help readers find the key information about distance of travel and total amount with blue and red, respectively.
-Note the different types of spatial layouts and key information texts in these receipt images.}
+Note the different types of spatial layouts and key information texts in these receipt images.
+}
 \label{fig:receipts}
@@
 \label{experiment}
-The proposed method is evaluated on a dataset with $3$ types of scanned document images, which contain $8$ key information classes and $1$ don't care class.
+The proposed method is evaluated on ICDAR 2019 robust reading challenge on SROIE dataset and also on a self-built dataset with $3$ types of scanned document images, which contain $8$ key information classes and $1$ don't care class.
 For each specific key information class, multiple tokens can be included.
@@
 The result is perfectly correct as if the filled rectangles overlap with the boundary-only rectangles.
-We mask out certain private information with filled gray rectangles in the figure.}
+We mask out certain private information with filled gray rectangles in these figures.
+(zooming in to check the details)}
 \label{fig:result}
@@
 \subsection{Dataset}
-The dataset contains $4,484$ annotated scanned Spanish receipt documents, including taxi receipts, meals entertainment (ME) receipts, and hotel receipts, with $9$ different key information classes.
+The ICDAR 2019 SROIE data set (task 3) contains $1000$ whole scanned receipt images.
+Each receipt image contains around about four key text fields, such as goods name, unit price, date, and total cost.
+The text annotated in the dataset mainly consists of digits and English characters.
+The dataset is split into a training/validation set (“trainval”) and a test set (“test”).
+The “trainval” set consists of $627$ receipt images which is made available to the participants along with their annotations.
+Since the test annotation is not avaliable yet, we conduct laundry on the trainval set and selected $517$ samples, where the filtered $55$ samples were wrongly labeled.
+Then we split the trainval set in the ratio of $75:25$, where $75\%$ are used as training data and $25\%$ are used for validation.
+
+The self-built dataset contains $4,484$ annotated scanned Spanish receipt documents, including taxi receipts, meals entertainment (ME) receipts, and hotel receipts, with $9$ different key information classes.
 We generate the texts and corresponding bounding boxes with Google's OCR API.
@@
 The false positives are results with the boundary-only rectangles being not overlapped with the filled rectangles.
-We mask out certain private information with filled gray rectangles in the figure.}
+We mask out certain private information with filled gray rectangles in these figures.
+(zooming in to check the details)}
 \label{fig:falsepositive}
@@
 Each color indicates a key information class, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
-We mask out certain private information with filled gray rectangles in the figure.}
+We mask out certain private information with filled gray rectangles in these figures.
+(zooming in to check the details)}
 \label{fig:falselabel}
@@
 	\label{tab:samples}
+\end{table*}
+
+We also evaluate the CUTIE-B model on the ICDAR 2019 SROIE trainval set and list the results in Table \ref{tab:sroie}.
+The result in class level indicates that the inferenced result is perfectly the same with the ground truth, whereas the result in soft class level indicates that the inferenced result incorporates the ground truth but also included some unrelated text tokens.
+The result in token level indicates the token classification accuracy of each class in spite of the 'DontCare' class.
+\begin{table*}
+	\caption{Performance evaluation of CUTIE-B on ICDAR 2019 SROIE task 3.}
+\begin{center}
+\begin{tabular}{l | c | c | c}
+	 & class level & class level (soft) & token level \\
+	\hline
+	CUTIE-B & 86.7\% & 92.7\% & 94.2\% \\
+\end{tabular}
+\end{center}
+	\label{tab:sroie}
 \end{table*}
@@
    \caption{Locating the table region with CUTIE-B.
-Table tokens are indicated with yellow bounding boxes and table region is indicated with pink boxes, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
-We mask out certain private information with filled red rectangles in the figure.}
+Table tokens are indicated with yellow bounding boxes and table regions are indicated with pink boxes, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
+We mask out certain private information with filled red rectangles in these figures.
+(zooming in to check the details)}
 \label{fig:table}
@@
 Color legend in the top-left corner indicates the column id, where filled rectangles are the ground truths while the boundary-only rectangles are the inference results.
-We mask out certain private information with filled red rectangles in the figure.}
+We mask out certain private information with filled red rectangles in these figures.
+(zooming in to check the details)}
 \label{fig:column}
@@
 This paper proposes CUTIE to tackle this problem without requirement of any pre-training or post processing.
-Experimental results verifies the effectiveness of the proposed method.
-In contrast to the previous methods, the proposed method is easy to train and requires much smaller amount of training data while achieving state of the art performance.
+Experimental results verify the effectiveness of the proposed method.
+In contrast to the previous methods, the proposed method is easy to train and requires much smaller amount of training data while achieving state of the art performance with processing speed up to 50 samples per second.
 The performance gain is mainly achieved by exploring three key factors: the spatial relationship among texts, the semantic information of texts, and the grid positional mapping mechanism.
@@
 \begin{table*}
-	\caption{Structure of the proposed CUTIE-B model. }
+	\caption{Structure of the proposed CUTIE-B model.}
 \begin{center}

### 2019-06-18 data_loader_json.py

@@ -37,10 +37,11 @@ class DataLoader():
         self.random = False
         self.data_laundry = False
         self.encoding_factor = 1 # ensures the size (rows/cols) of grid table compat with the network
-        #self.classes = ['DontCare', 'Table']
-        self.classes = ['DontCare', 'Column0', 'Column1', 'Column2', 'Column3', 'Column4', 'Column5']
+        self.classes = ['DontCare', 'company', 'date', 'address', 'total'] # for ICDAR2019 SROIE
+        #self.classes = ['DontCare', 'Table'] # for table
+        #self.classes = ['DontCare', 'Column0', 'Column1', 'Column2', 'Column3', 'Column4', 'Column5'] # for column
         #self.classes = ['DontCare', 'Column']
-        #self.classes = ['DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', 'TaxRate']
+        #self.classes = ['DontCare', 'VendorName', 'VendorTaxID', 'InvoiceDate', 'InvoiceNumber', 'ExpenseAmount', 'BaseAmount', 'TaxAmount', 'TaxRate'] # for Spanish project
         
         self.doc_path = params.doc_path
         self.doc_test_path = params.test_path
@@ -929,7 +930,7 @@ class DataLoader():
         y_bottom = max(positions[1::2])
         w = x_right - x_left
         h = y_bottom - y_top
-        return x_left, y_top, x_right, y_bottom       
+        return int(x_left), int(y_top), int(x_right), int(y_bottom)       
     
     def _get_filenames(self, data_path):
         files = []

### 2019-06-18 main_build_dict.py

@@ -7,8 +7,8 @@ import argparse
 from data_loader_json import DataLoader
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
-parser.add_argument('--dict_path', type=str, default='dict/table') 
-parser.add_argument('--doc_path', type=str, default='data/table') 
+parser.add_argument('--dict_path', type=str, default='dict/SROIE') 
+parser.add_argument('--doc_path', type=str, default='data/SROIE') 
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 parser.add_argument('--text_case', type=bool, default=True) # case sensitive
 parser.add_argument('--tokenize', type=bool, default=True) # tokenize input text

### 2019-06-18 main_evaluate_json.py

@@ -16,14 +16,14 @@ from utils import *
 parser = argparse.ArgumentParser(description='CUTIE parameters')
 parser.add_argument('--use_cutie2', type=bool, default=False) # True to read image from doc_path 
 parser.add_argument('--is_table', type=bool, default=False) # True to read image from doc_path 
-parser.add_argument('--doc_path', type=str, default='data/column_small') # modify this
-parser.add_argument('--save_prefix', type=str, default='column', help='prefix for load ckpt model') # modify this
+parser.add_argument('--doc_path', type=str, default='data/SROIE') # modify this
+parser.add_argument('--save_prefix', type=str, default='SROIE', help='prefix for load ckpt model') # modify this
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
 parser.add_argument('--fill_bbox', type=bool, default=False) # augment data row/col in each batch
 
 parser.add_argument('--e_ckpt_path', type=str, default='../graph/CUTIE/graph/') # modify this
-parser.add_argument('--ckpt_file', type=str, default='CUTIE_atrousSPP_d20000c7(r80c80)_iter_40000.ckpt')
+parser.add_argument('--ckpt_file', type=str, default='CUTIE_atrousSPP_d20000c5(r80c80)_iter_29201.ckpt')
 parser.add_argument('--positional_mapping_strategy', type=int, default=1)
 parser.add_argument('--rows_target', type=int, default=80)  
 parser.add_argument('--cols_target', type=int, default=80) 
@@ -31,9 +31,9 @@ parser.add_argument('--rows_ulimit', type=int, default=80)
 parser.add_argument('--cols_ulimit', type=int, default=80) 
 
 parser.add_argument('--load_dict', type=bool, default=True, help='True to work based on an existing dict') 
-parser.add_argument('--load_dict_from_path', type=str, default='dict/table') # 40000 or table or 20000TC
+parser.add_argument('--load_dict_from_path', type=str, default='dict/SROIEnc') # 40000 or table or 20000TC
 parser.add_argument('--tokenize', type=bool, default=True) # tokenize input text
-parser.add_argument('--text_case', type=bool, default=True) # case sensitive
+parser.add_argument('--text_case', type=bool, default=False) # case sensitive
 parser.add_argument('--dict_path', type=str, default='dict/---') # not used if load_dict is True
 
 parser.add_argument('--restore_ckpt', type=bool, default=True) 
@@ -114,7 +114,8 @@ if __name__ == '__main__':
             recalls += [recall]
[…]

### 2019-06-18 main_train_json.py

@@ -16,9 +16,9 @@ from model_cutie2_aspp import CUTIE2 as CUTIEv2
 
 parser = argparse.ArgumentParser(description='CUTIE parameters')
 # data
-parser.add_argument('--use_cutie2', type=bool, default=True) # True to read image from doc_path 
-parser.add_argument('--doc_path', type=str, default='data/taxi_small')
-parser.add_argument('--save_prefix', type=str, default='taxi', help='prefix for ckpt') # TBD: save log/models with prefix
+parser.add_argument('--use_cutie2', type=bool, default=False) # True to read image from doc_path 
+parser.add_argument('--doc_path', type=str, default='data/SROIE')
+parser.add_argument('--save_prefix', type=str, default='SROIE', help='prefix for ckpt') # TBD: save log/models with prefix
 parser.add_argument('--test_path', type=str, default='') # leave empty if no test data provided
 
 # ckpt
@@ -30,7 +30,7 @@ parser.add_argument('--ckpt_file', type=str, default='meals/CUTIE_highresolution
 
 # dict
 parser.add_argument('--load_dict', type=bool, default=True, help='True to work based on an existing dict') 
-parser.add_argument('--load_dict_from_path', type=str, default='dict/table') # 40000 or 20000TC or table
+parser.add_argument('--load_dict_from_path', type=str, default='dict/SROIE') # 40000 or 20000TC or table
 parser.add_argument('--tokenize', type=bool, default=True) # tokenize input text
 parser.add_argument('--text_case', type=bool, default=True) # case sensitive
 parser.add_argument('--update_dict', type=bool, default=False)
@@ -134,7 +134,7 @@ if __name__ == '__main__':
     data_loader = DataLoader(params, update_dict=params.update_dict, load_dictionary=params.load_dict, data_split=0.75)
     num_words = max(20000, data_loader.num_words)
     num_classes = data_loader.num_classes
-    for _ in range(2):
+    for _ in range(2000):
         a = data_loader.next_batch()
         b = data_loader.fetch_validation_data()
     #    c = data_loader.fetch_test_data()

### 2019-06-20 Article/ms.tex
final

@@
 We further explore the effect of employing different structures of convolutional neural network and propose a fast and portable structure.
-We demonstrate the effectiveness of the proposed method on a dataset with up to $4,484$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much higher than the BERT for NER but with only $1/10$ parameters and without requiring the $3,300$M word dataset for pre-training.
-Experimental results also demonstrate that the proposed CUTIE model being able to achieve the state of the art performance in terms of either speed and accuracy with a much smaller amount of training data.
+We demonstrate the effectiveness of the proposed method on a dataset with up to $4,484$ labelled receipts, without any pre-training or post-processing, achieving state of the art performance that is much better than the NER based methods in terms of either speed and accuracy.
+Experimental results also demonstrate that the proposed CUTIE model being able to achieve good performance with a much smaller amount of training data.
 \end{abstract}
@@
 	CloudScan\cite{cloudscan} & - & 82 / - & 64 / - & 60 / - \\
-	BERT\cite{bert} & 110M & 88.1 / - & 80.1 / - & 71.7 / - \\
+	BERT for NER\cite{bert} & 110M & 88.1 / - & 80.1 / - & 71.7 / - \\
 	CUTIE-A & 67M & 90.8 / 97.2 & 77.7 / \textbf{91.4} & 69.5 / \textbf{87.8} \\
@@
 
-We compare the performance of the proposed method with two state of the art methods CloudScan \cite{cloudscan} and BERT \cite{bert}.
+We compare the performance of the proposed method with two state of the art methods CloudScan \cite{cloudscan} and BERT for NER \cite{bert}.
 For comparison, the Cloud Scan model for SROIE is trained from scratch but with several expert designed features as described in \cite{cloudscan}.
@@
 Compared to CloudScan, CUTIE-A and CUTIE-B outperforms in every single test case.
-Furthermore, compared to BERT, which is pre-trained on a dataset with $3,300$M words and transfer learned on our dataset, our big network CUTIE-A improves AP by $2.7\%$ AP on taxi receipts but less accurate on other type of documents while using only $1/2$ parameters; our small network CUTIE-B improves AP by $5.9\%$ on taxi receipts, $1.4\%$ points on meals entertainment receipts, and $2.9\%$ on hotel receipts, outperforming other methods in all of the test cases but with much less complexity and smaller model size with only $1/9$ parameters and without requiring a huge dataset for model pretraining.
+Furthermore, compared to BERT for NER, which is pre-trained on a dataset with $3,300$M words and transfer learned on our dataset, our big network CUTIE-A improves AP by $2.7\%$ AP on taxi receipts but less accurate on other type of documents while using only $1/2$ parameters; our small network CUTIE-B improves AP by $5.9\%$ on taxi receipts, $1.4\%$ points on meals entertainment receipts, and $2.9\%$ on hotel receipts, outperforming other methods in all of the test cases but with much less complexity and smaller model size with only $1/9$ parameters and without requiring a huge dataset for model pretraining.
 We will further prove in Section \ref{parameters} that CUTIE-B is also able to achieve state of the art performance with only $1/10$ of BERT's parameters.
